# Alternative Models {#sec-appendix-models}

The main specification used a combined modeling approach.  Here we separate the parts of our framework and test the effects of constituent demand, capacity, and the political environment on interbranch representation separately, without adjusting for effects of the other parts. This alternative specification may be informative if we believe that parts are causally related (for example, if people from large states are more likely to become committee chairs or if more moderate members are more likely to face competitive general elections), or if some variables may be co-linear.

#### Modeling Response to Constituency Demands

$$
\begin{aligned}
Y_{ijt}\mid X_{ijt},\gamma_{ij},\delta_{jt},m_{it},p_{it} &\sim \text{NegBin}(\mu_{ijt},\alpha), \\
\log(\mu_{ijt}) = 
  & \beta_1 \text{District Population}_{it}+\\
  & \beta_2 \text{Percent Goverment Workers}_{it}+\\
  & \beta_3 \text{Percent with College Degree}_{it}+\\
  & \beta_4 \text{Percent Receiving Public Assistance}_{it}+\\
  &...\\
  & \gamma_{ij} + \delta_{jt} 
\end{aligned}
$$ {#eq-demand}


#### Modeling Capacity Effects


$$
\begin{aligned}
Y_{ijt}\mid X_{ijt},\gamma_{ij},\delta_{jt},m_{it},p_{it} &\sim \text{NegBin}(\mu_{ijt},\alpha), \\
\log(\mu_{ijt}) = 
  & \beta_1 \text{Experience in Office}_{it}+\\
  & \beta_2 \text{Experience as State Legislator}_{it}+\\
  & \beta_3 \text{Staff Budget}_{it}+\\
  & \beta_4 \text{Oversight Committee Position}_{itj}+\\
  & \beta_5 \text{Committee Chair}_{it}+\\
  & \beta_6 \text{Subcommittee Chair}_{it}+\\
  & \beta_7 \text{Ranking Minority Committee Member}_{it}+\\
  & \beta_8 \text{Prestige Committee Member}_{it}+\\
  &...\\
  & \gamma_{ij} + \delta_{jt} 
\end{aligned}
$$ {#eq-capacity}


Additionally, each section includes a model where we exclude committee leadership positions that depend on majority status, in order to estimate the effect of majority status among all members (not just those without leadership positions, who are structurally more likely to be in the minority, or junior members of the majority). 



## Total Interbranch Representation {#sec-appendix-models-total}

```{r}
type = "total"
here::here("code", "formatting.R") |> source()

```



###  Total Interbranch Representation: Demand

```{r}
#| label: tbl-models-demand_tot
#| tbl-cap: "The effect of demand on requests to federal agencies"
#| out-width: "100%"

load(here::here("models", type,  "models_demand.Rdata"))

modelsummary(models_demand,
             notes = list("Robust standard errors in parentheses, clustered by legislator.",
                          "This table shows estimates the relationship between district demographics that may affect demand and levels of interbranch representation.")) 
```

\clearpage

### Total Interbranch Representation: Capacity

<!--
Columns 1, 3, and 5 show differences across legislators with different capacity advantages.
--> 

```{r}
#| label: tbl-models-capacity-tot
#| tbl-cap: "The effect of capacity on total requests to federal agencies"
#| out-width: "100%"

load(here::here("models", type,  "models_capacity.Rdata"))

modelsummary(models_capacity,
             notes = list("Robust standard errors in parentheses, clustered by legislator.",
                          "This table shows estimates of the effect of legislator capacity (committee chair, subcommittee chair, and ranking member positions and years in office) on levels of interbranch representation.")) 
```


\clearpage

### Total Interbranch Representation: Strategic Responses to the Political Environment

::: {.fake-xref-table-for-caption}

```{=latex}
\begingroup\fontsize{1pt}{1pt}\selectfont\setlength{\tabcolsep}{0pt}\setlength{\arrayrulewidth}{0pt}\setlength{\abovecaptionskip}{0pt}\setlength{\belowcaptionskip}{0pt}
```

|   |
|---|
|   |

: The effect of constituent demand, legislator capacity, and political environment (including majority status) on corporate policy-work with federal agencies {#tbl-models-full-majority-tot}

```{=latex}
\endgroup\vspace{-2\baselineskip}
```
:::

```{r}
load(here::here("models", type,  "models_full_majority.Rdata"))

modelsummary(models_full_majority,
             notes = list(
               "Robust standard errors in parentheses, clustered by legislator.",
               "This table shows estimates of the effect of constituent demand, legislator capacity and strategic choices on levels of interbranch representation.")) |>
  # get rid of formatting to get rid of the extra line 
  theme_empty() |> 
  # bold header, hline bottom, aligned center
  tinytable::style_tt(j = 1, align = "l") |>
  tinytable::style_tt(i = 0:1, bold = T, line = "b",  align = "c") |>
  tinytable::style_tt(j = 1, align = "l")  |>  
  # new stuff for this table 
  tinytable::theme_latex(multipage = TRUE) |> 
  group_tt(i = list(
    "Constituent Demand"= 2,
    "Strategic Choices Shaped by Political Environment" = 10,
    "Capacity" = 28
  )) |>
  style_tt(i = 39, line = "t", line_color = "black", line_width = 0.1) |>
  style_tt("groupi", background = "grey") |>
  style_tt("~groupi", j = 1, indent = 1)
```


#### Total Interbranch Representation: Interbranch representation as electoral strategy

```{r}
#| label: tbl-models-elect_tot
#| tbl-cap: "The effect of electoral security on total interbranch representation"
#| out-width: 60%

load(here::here("models", type,  "models_elect.Rdata"))

modelsummary(models_elect,
             notes = list("Robust standard errors in parentheses, clustered by legislator.",
                          "This table shows estimates of the effect of electoral competition on levels of interbranch representation. "))  

```


\clearpage 


## Constituency Service {#sec-appendix-models-1}

```{r}
type = "1"
```


### Demand

```{r}
#| label: tbl-models-demand-ind
#| tbl-cap: "The effect of demand on individual constituent service"
#| out-width: "100%"

load(here::here("models", type,  "models_demand.Rdata"))

modelsummary(models_demand,
             notes = list("Robust standard errors in parentheses, clustered by legislator.",
                          "This table shows estimates the relationship between district demographics that may affect demand and levels of interbranch representation.")) 
```

\clearpage

### Capacity

```{r}
#| label: tbl-models-capacity-ind
#| tbl-cap: "The effect of capacity on individual constituent services"
#| out-width: "100%"

load(here::here("models", type,  "models_capacity.Rdata"))

modelsummary(models_capacity,
             notes = list("Robust standard errors in parentheses, clustered by legislator.",
                          "This table shows estimates of the effect of legislator capacity (committee chair, subcommittee chair, and ranking member positions and years in office) on levels of interbranch representation.")) 
```





\clearpage

### Individual Constituent Service: Strategic Responses to the Political Environment

::: {.fake-xref-table-for-caption}

```{=latex}
\begingroup\fontsize{1pt}{1pt}\selectfont\setlength{\tabcolsep}{0pt}\setlength{\arrayrulewidth}{0pt}\setlength{\abovecaptionskip}{0pt}\setlength{\belowcaptionskip}{0pt}
```

|   |
|---|
|   |

: The effect of constituent demand, legislator capacity, and political environment (including majority status) on individual constituent service  {#tbl-models-full-majority-ind}

```{=latex}
\endgroup\vspace{-2\baselineskip}
```
:::

```{r}
load(here::here("models", type,  "models_full_majority.Rdata"))

modelsummary(models_full_majority,
             notes = list(
               "Robust standard errors in parentheses, clustered by legislator.",
               "This table shows estimates of the effect of constituent demand, legislator capacity and strategic choices on levels of interbranch representation.")) |>
  # get rid of formatting to get rid of the extra line 
  theme_empty() |> 
  # bold header, hline bottom, aligned center
  tinytable::style_tt(j = 1, align = "l") |>
  tinytable::style_tt(i = 0:1, bold = T, line = "b",  align = "c") |>
  tinytable::style_tt(j = 1, align = "l")  |>  
  # new stuff for this table 
  tinytable::theme_latex(multipage = TRUE) |> 
  group_tt(i = list(
    "Constituent Demand"= 2,
    "Strategic Choices Shaped by Political Environment" = 10,
    "Capacity" = 28
  )) |>
  style_tt(i = 39, line = "t", line_color = "black", line_width = 0.1) |>
  style_tt("groupi", background = "grey") |>
  style_tt("~groupi", j = 1, indent = 1)
```



#### Interbranch representation as electoral strategy

```{r}
#| label: tbl-models-elect-ind
#| tbl-cap: "The effect of electoral security on individual constituent service"
#| out-width: "60%"

load(here::here("models", type,  "models_elect.Rdata"))

modelsummary(models_elect,
             notes = list("Robust standard errors in parentheses, clustered by legislator.",
                          "This table shows estimates of the effect of electoral competition on levels of interbranch representation. "))  

```



\clearpage 



## Corporate Service (Helping Businesses) {#sec-appendix-models-2}

```{r}
type = "2"
```



### Corporate Service : Demand

```{r}
#| label: tbl-models-demand-corser
#| tbl-cap: "The effect of demand on corporate service"
#| out-width: "100%"

load(here::here("models", type,  "models_demand.Rdata"))

modelsummary(models_demand,
             notes = list("Robust standard errors in parentheses, clustered by legislator.",
                          "This table shows estimates the relationship between district demographics that may affect demand and levels of interbranch representation.")) 
```

\clearpage

### Corporate Service: Capacity


```{r}
#| label: tbl-models-capacity-corser
#| tbl-cap: "The effect of capacity on corporate service"
#| out-width: "100%"

load(here::here("models", type,  "models_capacity.Rdata"))

modelsummary(models_capacity,
             notes = list("Robust standard errors in parentheses, clustered by legislator.",
                          "This table shows estimates of the effect of legislator capacity (committee chair, subcommittee chair, and ranking member positions and years in office) on levels of interbranch representation.")) 
```




\clearpage


### Corporate Service: Strategic Responses to the Political Environment

::: {.fake-xref-table-for-caption}

```{=latex}
\begingroup\fontsize{1pt}{1pt}\selectfont\setlength{\tabcolsep}{0pt}\setlength{\arrayrulewidth}{0pt}\setlength{\abovecaptionskip}{0pt}\setlength{\belowcaptionskip}{0pt}
```

|   |
|---|
|   |

: The effect of constituent demand, legislator capacity, and political environment (including majority status) on corporate service with federal agencies {#tbl-models-full-majority-corser}

```{=latex}
\endgroup\vspace{-2\baselineskip}
```
:::

```{r}
load(here::here("models", type,  "models_full_majority.Rdata"))

modelsummary(models_full_majority,
             notes = list(
               "Robust standard errors in parentheses, clustered by legislator.",
               "This table shows estimates of the effect of constituent demand, legislator capacity and strategic choices on levels of interbranch representation.")) |>
  # get rid of formatting to get rid of the extra line 
  theme_empty() |> 
  # bold header, hline bottom, aligned center
  tinytable::style_tt(j = 1, align = "l") |>
  tinytable::style_tt(i = 0:1, bold = T, line = "b",  align = "c") |>
  tinytable::style_tt(j = 1, align = "l")  |>  
  # new stuff for this table 
  tinytable::theme_latex(multipage = TRUE) |> 
  group_tt(i = list(
    "Constituent Demand"= 2,
    "Strategic Choices Shaped by Political Environment" = 10,
    "Capacity" = 28
  )) |>
  style_tt(i = 39, line = "t", line_color = "black", line_width = 0.1) |>
  style_tt("groupi", background = "grey") |>
  style_tt("~groupi", j = 1, indent = 1)
```


#### Corporate Service as electoral strategy

```{r}
#| label: tbl-models-elect_cs
#| tbl-cap: "The effect of electoral security on corporate service"
#| out-width: 60%

load(here::here("models", type,  "models_elect.Rdata"))

modelsummary(models_elect,
             notes = list("Robust standard errors in parentheses, clustered by legislator.",
                          "This table shows estimates of the effect of electoral competition on levels of interbranch representation. "))  

```


\clearpage 


## Helping Nonprofit and Local Government Representation {#sec-appendix-models-3}

```{r}
type = "3"
```


::: {.fake-xref-table-for-caption}

```{=latex}
\begingroup\fontsize{1pt}{1pt}\selectfont\setlength{\tabcolsep}{0pt}\setlength{\arrayrulewidth}{0pt}\setlength{\abovecaptionskip}{0pt}\setlength{\belowcaptionskip}{0pt}
```

|   |
|---|
|   |

: The effect of constituent demand, legislator capacity, and political environment on requests to federal agencies {#tbl-models-full-nonprofit}

```{=latex}
\endgroup\vspace{-2\baselineskip}
```
:::

```{r}
load(here::here("models", type,  "models_full_nonprofit.Rdata"))

modelsummary(models_full,
             notes = list(
               "Robust standard errors in parentheses, clustered by legislator.",
               "This table shows estimates of the effect of constituent demand (population, employment, education, public assistance), legislator capacity (chamber, reporting committee, committee chair, subcommittee chair, and ranking member positions and years in office) and institutional positions that may affect strategic behavior (reporting committee membership, perceived ideological distance from teh agency, co-partisan president) on levels of interbranch representation.")) |>
  # get rid of formatting to get rid of the extra line 
  theme_empty() |> 
  # bold header, hline bottom, aligned center
  tinytable::style_tt(j = 1, align = "l") |>
  tinytable::style_tt(i = 0:1, bold = T, line = "b",  align = "c") |>
  tinytable::style_tt(j = 1, align = "l")  |>  
  # new stuff for this table 
  tinytable::theme_latex(multipage = TRUE) |> 
  group_tt(i = list(
    "Constituent Demand"= 2,
    "Strategic Choices Shaped by Political Environment" = 12,
    #"Political Environment + Capcacy" = 26,
    "Capacity" = 28
  )) |>
  style_tt(i = 45, line = "t", line_color = "black", line_width = 0.1) |>
  style_tt("groupi", background = "grey") |>
  style_tt("~groupi", j = 1, indent = 1)
```

\clearpage

### Helping Nonprofit and Local Government Representation: Demand

```{r}
#| label: tbl-models-demand-non
#| tbl-cap: "The effect of demand on non-profit/local government service"
#| out-width: "100%"

load(here::here("models", type,  "models_demand.Rdata"))

modelsummary(models_demand,
             notes = list("Robust standard errors in parentheses, clustered by legislator.",
                          "This table shows estimates the relationship between district demographics that may affect demand and levels of interbranch representation.")) 
```

\clearpage

### Capacity


```{r}
#| label: tbl-models-capacity-non
#| tbl-cap: "The effect of capacity on non-profit/local government service"
#| out-width: "100%"

load(here::here("models", type,  "models_capacity.Rdata"))

modelsummary(models_capacity,
             notes = list("Robust standard errors in parentheses, clustered by legislator.",
                          "This table shows estimates of the effect of legislator capacity (committee chair, subcommittee chair, and ranking member positions and years in office) on levels of interbranch representation.")) 
```




\clearpage

### Non-profit/Local Government Service: Strategic Responses to the Political Environment

::: {.fake-xref-table-for-caption}

```{=latex}
\begingroup\fontsize{1pt}{1pt}\selectfont\setlength{\tabcolsep}{0pt}\setlength{\arrayrulewidth}{0pt}\setlength{\abovecaptionskip}{0pt}\setlength{\belowcaptionskip}{0pt}
```

|   |
|---|
|   |

: The effect of constituent demand, legislator capacity, and political environment (including majority status) on non-profit/local government service {#tbl-models-full-majority-non}

```{=latex}
\endgroup\vspace{-2\baselineskip}
```
:::

```{r}
load(here::here("models", type,  "models_full_majority.Rdata"))

modelsummary(models_full_majority,
             notes = list(
               "Robust standard errors in parentheses, clustered by legislator.",
               "This table shows estimates of the effect of constituent demand, legislator capacity and strategic choices on levels of interbranch representation.")) |>
  # get rid of formatting to get rid of the extra line 
  theme_empty() |> 
  # bold header, hline bottom, aligned center
  tinytable::style_tt(j = 1, align = "l") |>
  tinytable::style_tt(i = 0:1, bold = T, line = "b",  align = "c") |>
  tinytable::style_tt(j = 1, align = "l")  |>  
  # new stuff for this table 
  tinytable::theme_latex(multipage = TRUE) |> 
  group_tt(i = list(
    "Constituent Demand"= 2,
    "Strategic Choices Shaped by Political Environment" = 10,
    "Capacity" = 28
  )) |>
  style_tt(i = 39, line = "t", line_color = "black", line_width = 0.1) |>
  style_tt("groupi", background = "grey") |>
  style_tt("~groupi", j = 1, indent = 1)
```

#### Interbranch representation as electoral strategy

```{r}
#| label: tbl-models-elect_non
#| tbl-cap: "The effect of electoral security on non-profit/local government service"
#| out-width: 60%

load(here::here("models", type,  "models_elect.Rdata"))

modelsummary(models_elect,
             notes = list("Robust standard errors in parentheses, clustered by legislator.",
                          "This table shows estimates of the effect of electoral competition on levels of interbranch representation. "))  

```


\clearpage 


## Policy Work {#sec-appendix-models-5}

```{r}
type = "5"
```



### Policy Work: Demand

```{r}
#| label: tbl-models-demand-pol
#| tbl-cap: "The effect of demand on general policy work with federal agencies"
#| out-width: "100%"

load(here::here("models", type,  "models_demand.Rdata"))

modelsummary(models_demand,
             notes = list("Robust standard errors in parentheses, clustered by legislator.",
                          "This table shows estimates the relationship between district demographics that may affect demand and levels of interbranch representation.")) 
```

\clearpage

### Policy Work: Capacity


```{r}
#| label: tbl-models-capacity-pol
#| tbl-cap: "The effect of capacity on general policy work with federal agencies"
#| out-width: "100%"

load(here::here("models", type,  "models_capacity.Rdata"))

modelsummary(models_capacity,
             notes = list("Robust standard errors in parentheses, clustered by legislator.",
                          "This table shows estimates of the effect of legislator capacity (committee chair, subcommittee chair, and ranking member positions and years in office) on levels of interbranch representation.")) 
```



\clearpage 





\clearpage

### General Policywork: Strategic Responses to the Political Environment

::: {.fake-xref-table-for-caption}

```{=latex}
\begingroup\fontsize{1pt}{1pt}\selectfont\setlength{\tabcolsep}{0pt}\setlength{\arrayrulewidth}{0pt}\setlength{\abovecaptionskip}{0pt}\setlength{\belowcaptionskip}{0pt}
```

|   |
|---|
|   |

: The effect of constituent demand, legislator capacity, and political environment (including majority status) on general policy-work with federal agencies {#tbl-models-full-majority-pol}

```{=latex}
\endgroup\vspace{-2\baselineskip}
```
:::

```{r}
load(here::here("models", type,  "models_full_majority.Rdata"))

modelsummary(models_full_majority,
             notes = list(
               "Robust standard errors in parentheses, clustered by legislator.",
               "This table shows estimates of the effect of constituent demand, legislator capacity and strategic choices on levels of interbranch representation.")) |>
  # get rid of formatting to get rid of the extra line 
  theme_empty() |> 
  # bold header, hline bottom, aligned center
  tinytable::style_tt(j = 1, align = "l") |>
  tinytable::style_tt(i = 0:1, bold = T, line = "b",  align = "c") |>
  tinytable::style_tt(j = 1, align = "l")  |>  
  # new stuff for this table 
  tinytable::theme_latex(multipage = TRUE) |> 
  group_tt(i = list(
    "Constituent Demand"= 2,
    "Strategic Choices Shaped by Political Environment" = 10,
    "Capacity" = 28
  )) |>
  style_tt(i = 46, line = "t", line_color = "black", line_width = 0.1) |>
  style_tt("groupi", background = "grey") |>
  style_tt("~groupi", j = 1, indent = 1)
```


#### General Policy work as electoral strategy

```{r}
#| label: tbl-models-elect-pol
#| tbl-cap: "The effect of electoral security on general policy work with federal agencies"
#| out-width: 60%

load(here::here("models", type,  "models_elect.Rdata"))

modelsummary(models_elect,
             notes = list("Robust standard errors in parentheses, clustered by legislator.",
                          "This table shows estimates of the effect of electoral competition on levels of interbranch representation. "))  

```

\clearpage 

## Policy Work on Behalf of Business {#sec-appendix-models-4}

```{r}
type = "4"
```



### Policy Work on Behalf of Business: Demand

```{r}
#| label: tbl-models-demand-corpol
#| tbl-cap: "The effect of demand on corporate policy work"
#| out-width: "100%"

load(here::here("models", type,  "models_demand.Rdata"))

modelsummary(models_demand,
             notes = list("Robust standard errors in parentheses, clustered by legislator.",
                          "This table shows estimates the relationship between district demographics that may affect demand and levels of interbranch representation.")) 
```

\clearpage


### Policy Work on Behalf of Business: Capacity

```{r}
#| label: tbl-models-capacity-corpol
#| tbl-cap: "The effect of capacity on corporate policywork"
#| out-width: "100%"

load(here::here("models", type,  "models_capacity.Rdata"))

modelsummary(models_capacity,
             notes = list("Robust standard errors in parentheses, clustered by legislator.",
                          "This table shows estimates of the effect of legislator capacity (committee chair, subcommittee chair, and ranking member positions and years in office) on levels of interbranch representation.")) 
```


\clearpage

### Policy Work on Behalf of Business : Strategic Responses to the Political Environment

::: {.fake-xref-table-for-caption}

```{=latex}
\begingroup\fontsize{1pt}{1pt}\selectfont\setlength{\tabcolsep}{0pt}\setlength{\arrayrulewidth}{0pt}\setlength{\abovecaptionskip}{0pt}\setlength{\belowcaptionskip}{0pt}
```

|   |
|---|
|   |

: The effect of constituent demand, legislator capacity, and political environment (including majority status) on corporate policy-work with federal agencies {#tbl-models-full-majority}

```{=latex}
\endgroup\vspace{-2\baselineskip}
```
:::

```{r}
load(here::here("models", type,  "models_full_majority.Rdata"))

modelsummary(models_full_majority,
             notes = list(
               "Robust standard errors in parentheses, clustered by legislator.",
               "This table shows estimates of the effect of constituent demand, legislator capacity and strategic choices on levels of interbranch representation.")) |>
  # get rid of formatting to get rid of the extra line 
  theme_empty() |> 
  # bold header, hline bottom, aligned center
  tinytable::style_tt(j = 1, align = "l") |>
  tinytable::style_tt(i = 0:1, bold = T, line = "b",  align = "c") |>
  tinytable::style_tt(j = 1, align = "l")  |>  
  # new stuff for this table 
  tinytable::theme_latex(multipage = TRUE) |> 
  group_tt(i = list(
    "Constituent Demand"= 2,
    "Strategic Choices Shaped by Political Environment" = 10,
    "Capacity" = 28
  )) |>
  style_tt(i = 39, line = "t", line_color = "black", line_width = 0.1) |>
  style_tt("groupi", background = "grey") |>
  style_tt("~groupi", j = 1, indent = 1)
```


#### Policy Work on Behalf of Business as Electoral Strategy

```{r}
#| label: tbl-models-elect_corpol
#| tbl-cap: "The effect of electoral security on corporate policywork"
#| out-width: 60%

load(here::here("models", type,  "models_elect.Rdata"))

modelsummary(models_elect,
             notes = list("Robust standard errors in parentheses, clustered by legislator.",
                          "This table shows estimates of the effect of electoral competition on levels of interbranch representation. "))  

```

