
#### Staff experience - cross

m_full_staff_experience_cross

```{r m_full_staff_experience_cross}
m_full_staff_experience_cross <- fenegbin (
  perYear ~ total_staff_experience_years +
    population_m +
     percent_workers_government +
     percent_education_bachelor_or_higher +
     percent_public_assistance_or_snap_households +
    # percent_workers_self_employed +
    # percent_workers_private_sector +
    # percent_workers_nonprofit +
    # electoral
    competitive +
    competitive_primary +
    #PACamount_m +
    # institution
    chair +
    subchr +
    ranking_minority +
    #prestige +
    oversight +
    # member level
    state_leg +
    experience +
     abs(nominate_dim1) +
     party +
    distance*presidents_party #+ majority
  | Year_x_Agency,
                    cluster = "Legislator",
           data = data_member )
if(testing){modelsummary::modelsummary(m_full_staff_experience_cross, stars = T)}
```

#### House staff count did

m_full_staff_experience_did

```{r m_full_staff_experience_did}
# controlling for expiernce
m_full_staff_experience_did <-fenegbin (
  perYear ~ total_staff_experience_years +
    # lots of this does not vary enough for the dif in diff
    #population_m +
      percent_workers_government + # model failing to converge dropping
      percent_education_bachelor_or_higher + # model failing to converge dropping
      percent_public_assistance_or_snap_households +  # model failing to converge dropping
    # percent_workers_self_employed +
    # percent_workers_private_sector +
    # percent_workers_nonprofit +
    # electoral
     competitive +
    competitive_primary +
    #PACamount_m +
    # institution
    chair +
    subchr +
    ranking_minority +
    # prestige +
    oversight +
    # member level
    # state_leg +
    experience +
    # abs(nominate_1)
    # party +
    # distance*presidents_party +
    presidents_party #+ majority
  | Year_x_Agency + Legislator_x_Agency,
                    cluster = "Legislator",
           data = data_member )
if(testing){modelsummary::modelsummary(m_full_staff_experience_did, stars = T)}
```

#### House staff  - cross

m_full_house_staff_experience_cross

```{r m_full_house_staff_experience_cross}
m_full_house_staff_experience_cross <- fenegbin (
  perYear ~ total_staff_experience_years +
    population_m +
     percent_workers_government +
     percent_education_bachelor_or_higher +
     percent_public_assistance_or_snap_households +
    # percent_workers_self_employed +
    # percent_workers_private_sector +
    # percent_workers_nonprofit +
    # electoral
    competitive +
    competitive_primary +
    #PACamount_m +
    # institution
    chair +
    subchr +
    ranking_minority +
    #prestige +
    oversight +
    # member level
    state_leg +
    experience +
     abs(nominate_dim1) +
     party +
    distance*presidents_party #+ majority
  | Year_x_Agency,
                    cluster = "Legislator",
           data = data_member |> filter(chamber == "House") )
if(testing){modelsummary::modelsummary(m_full_house_staff_experience_cross, stars = T)}
```

#### House staff count did

m_full_house_staff_experience_did
 
```{r m_full_house_staff_experience_did}
# controlling for expiernce
m_full_house_staff_experience_did <-fenegbin (
  perYear ~ total_staff_experience_years +
    # lots of this does not vary enough for the dif in diff
    #population_m +
      percent_workers_government + # model failing to converge dropping
      percent_education_bachelor_or_higher + # model failing to converge dropping
      percent_public_assistance_or_snap_households +  # model failing to converge dropping
    # percent_workers_self_employed +
    # percent_workers_private_sector +
    # percent_workers_nonprofit +
    # electoral
     competitive +
    competitive_primary +
    #PACamount_m +
    # institution
    chair +
    subchr +
    ranking_minority +
    # prestige +
    oversight +
    # member level
    # state_leg +
    experience +
    # abs(nominate_1)
    # party +
    # distance*presidents_party +
    presidents_party #+ majority
  | Year_x_Agency + Legislator_x_Agency,
                    cluster = "Legislator",
           data = data_member |> filter(chamber == "House") )
if(testing){modelsummary::modelsummary(m_full_house_staff_experience_did, stars = T)}
```

#### Senate staff  - cross

m_full_senate_staff_experience_cross

```{r m_full_senate_staff_experience_cross}
m_full_senate_staff_experience_cross <- fenegbin (
  perYear ~ total_staff_experience_years +
    population_m +
     percent_workers_government +
     percent_education_bachelor_or_higher +
     percent_public_assistance_or_snap_households +
    # percent_workers_self_employed +
    # percent_workers_private_sector +
    # percent_workers_nonprofit +
    # electoral
    competitive +
    #ompetitive_primary +
    #PACamount_m +
    # institution
    chair +
    subchr +
    ranking_minority +
    #prestige +
    oversight +
    # member level
    state_leg +
    experience +
     abs(nominate_dim1) +
     party +
    distance*presidents_party #+ majority
  | Year_x_Agency,
                    cluster = "Legislator",
           data = data_member |> filter(chamber == "Senate") )
if(testing){modelsummary::modelsummary(m_full_house_staff_experience_cross, stars = T)}
```
 
####Senate staff count did
 
m_full_senate_staff_experience_did

```{r m_full_senate_staff_experience_did}
# controlling for staff experience
m_full_senate_staff_experience_did <-fenegbin (
  perYear ~ total_staff_experience_years +
    # lots of this does not vary enough for the dif in diff
    #population_m +
      percent_workers_government + # model failing to converge dropping
      percent_education_bachelor_or_higher + # model failing to converge dropping
      percent_public_assistance_or_snap_households +  # model failing to converge dropping
    # percent_workers_self_employed +
    # percent_workers_private_sector +
    # percent_workers_nonprofit +
    # electoral
     competitive +
    #competitive_primary +
    #PACamount_m +
    # institution
    chair +
    subchr +
    ranking_minority +
    # prestige +
    oversight +
    # member level
    # state_leg +
    experience +
    # abs(nominate_1)
    # party +
    # distance*presidents_party +
    presidents_party #+ majority
  | Year_x_Agency + Legislator_x_Agency,
                    cluster = "Legislator",
           data = data_member |> filter(chamber == "Senate") )
if(testing){modelsummary::modelsummary(m_full_senate_staff_experience_did, stars = T)}
```

#### "models_full_staff_experience.Rdata"

```{r models_full_staff_experience}
models_full_staff_experience <- list(
      "(1)" =  m_full_staff_experience_cross,
  "(2)" = m_full_staff_experience_did,
    "(3)" =  m_full_house_staff_experience_cross,
  "(4)" = m_full_house_staff_experience_did,
  "(5)" =  m_full_senate_staff_experience_cross,
  "(6)" = m_full_senate_staff_experience_did
)
rows <- tibble(
  term = c("Dependent variable",
           "All legislators",
           "Only House",
           "Only Senate"),
 `(1)` = c("Count", "X", "", ""),
  `(2)` = c("Count", "X", "", ""),
    `(3)` = c("Count", "", "X", ""),
  `(4)` = c("Count", "", "X", ""),
  `(5)` = c("Count", "", "", "X"),
  `(6)` = c("Count", "", "", "X"),
  )
attr(rows, 'position') <- c(0)
# load(here::here("models", type, "models_full.Rdata")))
modelsummary(models_full_staff_experience) |>
  group_tt(i = list(
    "Demand"= 2,
    "Political Environment" = 10,
    "Political Environment & Capcacy" = 26,
    "Capacity" = 28
  )) |>
  style_tt(i = 44, line = "t", line_color = "black", line_width = 0.2) |>
  style_tt("groupi", background = "grey") |>
  style_tt("~groupi", j = 1, indent = 2)
beta_did <- betas(m_full_house_staff_experience_did)
se_did <- standard_errors(m_full_house_staff_experience_did)
beta_cross <- betas(m_full_house_staff_experience_cross)
se_cross <- standard_errors(m_full_house_staff_experience_cross)
save(models_full_staff_experience, rows, cm, gm,   beta_cross, beta_did, se_cross, se_did,
     file = here::here("models", type, "models_full_staff_experience.Rdata"))
```
