

## per District

The main results showing that replacing a more experienced legislator with a new legislator yields a substantial decrease in service to the district are robust to interacting all variables with the `same_party` variable. 
Cross-sectional effects get larger but more uncertain when data are subset to district years after turnover (as required for the `same_party` variable). Within-district effects become more uncertain, likely due to the much smaller number of observations where `same_party` can be observed. 


### District-level Coefficient Plots

Figures: `figs/[TYPE]/m-district-[1:4].png`

1. cross-sectional 
2. cross-sectional with same-party variable 
3. diff-in-diff
4. diff-in-diff with same party variable

```{r}
#| layout-ncol: 2
#| fig-height: 4.5
#| fig-cap: "figs/[TYPE]/m-district-[1:4].png"
#| fig-subcap: 
#|   - "1"
#|   - "2"
#|   - "3"
#|   - "4"
#| out-width: "100%"
#| label: "m-district"
#| fig-show: "hold"


m_district_cross <- fenegbin(perYear ~
  new_member #+ second + third + fourth + fifth + sixth 
  | Year_x_Agency,
cluster = "District",
data = data_district)

if(testing){modelsummary::modelsummary(m_district_cross)}

coefplot(m_district_cross, horiz = T, drop = "(Intercept)|.theta", sub = "Reference = A member serving >6 years") 


m_district_cross_party <- fenegbin(perYear ~
  new_member*same_party #+ second*same_party + third*same_party + fourth*same_party + fifth*same_party + sixth*same_party 
  | Year_x_Agency,
cluster = "District",
data = data_district)

if(testing){modelsummary::modelsummary(m_district_cross)}

coefplot(m_district_cross_party, horiz = T, drop = "(Intercept)|.theta", sub = "Reference = A member serving >6 years") 


# Diff in diff
m_district_did <- fenegbin(perYear ~
  new_member #+ same_party + second + third + fourth + fifth + sixth | 
  | District + Year_x_Agency,
cluster = "District",
data = data_district )

coefplot(m_district_did, horiz = T, drop = "(Intercept)|.theta", sub = "Reference = A member serving >6 years") 

# Diff in diff
m_district_did_party <- fenegbin(perYear ~
  new_member*same_party #+ second*same_party + third*same_party + fourth*same_party + fifth*same_party + sixth*same_party 
   | District + Year_x_Agency,
cluster = "District",
data = data_district )

coefplot(m_district_did_party, horiz = T, drop = "(Intercept)|.theta", sub = "Reference = A member serving >6 years") 



# Diff in diff
m_district_did_house <- fenegbin(perYear ~
  new_member #+ same_party + second + third + fourth + fifth + sixth 
    | District + Year_x_Agency,
cluster = "District",
data = data_district |> filter(chamber == "House"))


# Diff in diff + party change var 
m_district_did_house_party <- fenegbin(perYear ~
  new_member*same_party #+ second*same_party + third*same_party + fourth*same_party + fifth*same_party + sixth*
 | District + Year_x_Agency,
cluster = "District",
data = data_district |> filter(chamber == "House"))

# Diff in diff
m_district_did_senate <- fenegbin(perYear ~
  new_member #+ same_party + second + third + fourth + fifth + sixth 
    | District + Year_x_Agency,
cluster = "District",
data = data_district |> filter(chamber == "Senate"))


# Diff in diff + party change var 
m_district_did_senate_party <- fenegbin(perYear ~
  new_member*same_party # + second*same_party + third*same_party + fourth*same_party + fifth*same_party + sixth*same_party 
    | District + Year_x_Agency,
cluster = "District",
data = data_district |> filter(chamber == "Senate"))

```

### Per District Tables

- Models: `models/models_district_negbin.Rdata` 


```{r models_district}
models_district <- list(
  "(1)" = m_district_cross,
  "(2)" = m_district_did,
  "(3)" = m_district_did_house,
  "(4)" = m_district_did_senate
)


rows <- tibble(
  term = c("Dependent variable", 
           "All districts",
           "House only",
           "Senate only"),
  `(1)` = c("Per year", 
            "X", 
            "", 
            ""),
  `(2)` =c("Per year", 
           "X", 
            "", 
            ""),
    `(3)` = c("Per year", 
            "", 
            "X", 
            ""),
  `(4)` =c("Per year", 
           #"X", 
           "", 
            "", 
            "X")
)



# Check marks for controls 
attr(rows, 'position') <- c(0)



modelsummary(models_district)
```


## Same party
models_district_party

```{r models_district_party}
models_district_party <- list(
  "(1)" = m_district_cross_party,
  "(2)" = m_district_did_party,
  "(3)" = m_district_did_house_party,
  "(4)" = m_district_did_senate_party
)


rows <- tibble(
  term = c("Dependent variable", 
           "All districts",
           "House only",
           "Senate only"),
  `(1)` = c("Per year", 
            "X", 
            "", 
            ""),
  `(2)` =c("Per year", 
           "X", 
            "", 
            ""),
    `(3)` = c("Per year", 
            "", 
            "X", 
            ""),
  `(4)` =c("Per year", 
           #"X", 
           "", 
            "", 
            "X")
)



# Check marks for controls 
attr(rows, 'position') <- c(0)



modelsummary(models_district_party)
```


### Per District Predictions (House only)

- Figures: `figs/[TYPE]/m-district-predicted-house-[1:2].png`

```{r}
#| layout-ncol: 2
#| fig-height: 3
#| fig-cap: "figs/[TYPE]/m-district-predicted-house-[1:2].png"
#| fig-subcap: 
#|   - "1"
#|   - "2"
#|   - "3"
#|   - "4"
#| out-width: "100%"
#| label: "m-district-predicted-house"
#| fig-show: "hold"


# Values for HOUSE seats 
values <- tidyr::expand(data_district,
                        new_member = new_member,
                        oversight = 0,
                        distance = data_member$distance |> mean(na.rm = T),
                        second = second,
                        third = third,
                        fourth = fourth,
                        fifth = fifth, 
                        sixth = sixth,
                        Year = "2017",
                        District = "alabama_1_1",
                        Year_x_Agency = modal$Year_x_Agency[n],
                        same_party = same_party
                   ) %>% 
  drop_na(same_party)

# diff in diff plot

predicted <- predictions(m_district_did_house,
                         newdata = values) 


predicted %>%
ggdistrict() +
        geom_line(aes(x = as.numeric(year_in_congress %>% str_replace(" N", "1") %>% str_sub(1,1) ))) + 
  labs(title = "Letters per House district",        subtitle = "(difference-in-differences)",
       x = "Years serving in Congress",
       y = "    Predicted letters per year\nper House district\n(difference-in-differneces)",
       fill = "",
       color = "",
       shape = "")


```





### Per District Predictions (Senate only)

- Figures: `figs/[TYPE]/m-district-predicted-senate-[1:2].png`

```{r}
#| layout-ncol: 2
#| fig-height: 3
#| fig-cap: "figs/[TYPE]/m-district-predicted-senate-[1:2].png"
#| fig-subcap: 
#|   - "1"
#|   - "2"
#|   - "3"
#|   - "4"
#| out-width: "100%"
#| label: "m-district-predicted-senate"
#| fig-show: "hold"


# Values for Senate seats 
values <- tidyr::expand(data_district,
                        new_member = new_member,
                        oversight = 0,
                        distance = data_member$distance |> mean(na.rm = T),
                        second = second,
                        third = third,
                        fourth = fourth,
                        fifth = fifth, 
                        sixth = sixth,
                        Year = "2017",
                        Year_x_Agency = modal$Year_x_Agency[n],
                        District = "alabama_0",
                        same_party = same_party
                   ) %>% 
  drop_na(same_party)

# diff in diff plot

predicted <- predictions(m_district_did_senate,
                         newdata = values) 


predicted %>%
ggdistrict() +
        geom_line(aes(x = as.numeric(year_in_congress %>% str_replace(" N", "1") %>% str_sub(1,1) ))) + 
  labs(title = "Letters per senator",        subtitle = "(difference-in-differences)",
       x = "Years serving in Congress",
       y = "   Predicted letters per year\nper Senator\n(difference-in-differneces)",
       fill = "",
       color = "",
       shape = "")
```



### Modeled Effects - district

```{r}
#| label: "m-distirct-effect"
#| fig-cap: "figs/[TYPE]/m-district-effect"
#| layout-ncol: 2
#| fig-height: 3.5
#| fig-width: 3.5
#| fig-subcap: 
#|   - "1"
#|   - "2"
#|   - "3"
#|   - "4"
#| out-width: "100%"
#| fig-show: "hold"

model <-m_district_cross_party
data = data_district |> filter(year > 2007,  year < 2019)

plot_effect( 
  newdata = data |>  
    mutate(same_party = 0),
  effect = "Same party"
  )


model <-m_district_did_party
data = data_district |> filter(year > 2007,  year < 2019)

plot_effect( 
  newdata = data |>  
    mutate(same_party = 0),
  effect = "Same party (diff-in-diff)"
  )
```

\clearpage

# Model Results:  Spillover Effects Robustness Check

This is a robustness check for an observable implication of demand-driven behavior. If variation in constituent demand drives variation in legislator behavior (specifically a preference for more senior members), then we should observe spillover effects on the rest of a delegation when an experienced member is replaced with a new member. That is, if people demand more from experienced members, people should redirect demand to the next most experienced member who represents them.

```{r spillover-data}

# new IVs: new_senator, new_proportion, new_one

dcounts_spillover <- data_district %>% 
  # FIRST, identify districts with new members 
  group_by(state, Year) %>% 
  # size of the delegation 
  add_count(name = "n_delegation") %>% 
  mutate(
    # new IVs:
    new_senator = ifelse(chamber == "Senate" & new_member == 1, 1, NA), 
    new_proportion = sum(new_member)/n_delegation, 
    new_one = ifelse(new_member == 1, 1, NA)
  ) %>% 
  fill(new_senator, .direction = "updown") %>% 
  fill(new_one, .direction = "updown") %>% 
  mutate(new_senator =   replace_na(new_senator, 0),
         new_one = replace_na(new_one, 0) 
  ) %>% 
  group_by(state, Year, chamber) %>% 
  arrange(year, state) 

  # THEN WE DROP ALL OF THE NEW MEMBERS 
dcounts_spillover %<>%   filter(new_member == 0)  


# # inspect data 
# dcounts_spillover |> select(Year, state, chamber, new_member, new_one, new_senator, new_proportion, perYear) |> ungroup() |>
#   #filter(new_senator ==1) |>  
#   #count(new_senator, new_member) |> 
#   kablebox_long()
#     

```


<!-- NOT WORTH PLOTTING 
### Spillover Coefficient Plots

Figures: `figs/[TYPE]/m-spillover-[1:3].png`

1. diff-in-diff, at least one **new Senator** in the delegation effect
2. diff-in-diff, **proportion** of new legislators in the delegation effect **on Senators**
3. diff-in-diff, at least one **new legislator** in the delegation effect **on Senators**
--> 

### Spillover Effect:

```{r}
#| layout-ncol: 2
#| fig-height: 4.5
#| fig-cap: "figs/[TYPE]/m-spillover-[1:3].png"
#| fig-subcap: 
#|   - "1"
#|   - "2"
#|   - "3"
#| out-width: "100%"
#| label: "m-spillover"
#| fig-show: "hold"

m_spillover <- fenegbin(perYear ~
  new_senator  | Year_x_Agency + District,
cluster = "District",
data = dcounts_spillover)

# coefplot(m_spillover, horiz = T, drop = "(Intercept)|.theta", sub = "") 

m_spillover_proportion <- fenegbin(perYear ~
  new_proportion  | Year_x_Agency + District,
cluster = "District",
data = dcounts_spillover |> filter(chamber == "Senate"))

# coefplot(m_spillover_proportion, horiz = T, drop = "(Intercept)|.theta", sub = "") 

m_spillover_new_one <- fenegbin(perYear ~
  new_one  | Year_x_Agency + District,
cluster = "District",
data = dcounts_spillover |> filter(chamber == "Senate"))

# coefplot(m_spillover_new_one, horiz = T, drop = "(Intercept)|.theta", sub = "") 

```


- Models: `models/models_spillover_negbin.Rdata`

```{r models_spillover}
models_spillover <- list(
  "(1)" = m_spillover,
  "(2)" = m_spillover_proportion,
  "(3)" = m_spillover_new_one
)


rows <- tibble(
  term = c("Dependent variable", 
           "All districts",
           "Senate only"),
  `(1)` = c("Per year", 
            "X", 
            ""),
  `(2)` =c("Per year", 
            "", 
           "X"),
    `(3)` = c("Per year", 
            "", 
            "X")
)



# Check marks for controls 
attr(rows, 'position') <- c(0)


modelsummary(models_spillover ) 

save(models_spillover, rows, cm, gm,  # beta_cross, beta_did, se_cross, se_did,
     file = here::here("models", type, "models_spillover.Rdata"))
```


\clearpage
