---
title: "Replication Code and Robustness Checks"
subtitle: ""
author: Devin Judge-Lord
format: 
  #pdf: 
  html:
      self-contained: true
      toc: true
      code-fold: true
editor_options: 
  chunk_output_type: console
execute:
  message: false
  warning: false
---

Packages: 
  
  - `tidyverse` and `magrittr`, for data wrangling
- `scales` for plot scales 
- `ggrepel` for plot labels
- `here` for file paths 
- `knitr` for document formatting 
- `kableExtra` for table formatting 
- `modelsummary` for regression tables 
- `marginaleffects` for predictions 
- `fixest` --- statistical package for fixed effects estimation 
- `ineq` to calculate GINI coefficients


```{r global.options, include=FALSE, purl=FALSE}
testing = F
verification = T
here::here("code", "qmd_global_options.R") |> source() 

# plotting functions 
here::here("code", "ggcompetitive.R") |> source() 
here::here("code", "ggchair.R") |> source() 
here::here("code", "ggtenure.R") |> source() 

# coef map
here::here("code", "cm.R") |> source() 
here::here("code")

```




# Descriptive

## Data 
```{r}
d <- d %>% 
  ungroup() %>% 
  mutate(Type = case_when(
    TYPE %in% c(1,2,3) ~ "Constituency\nService", 
    TYPE %in% c(4,5) ~ "Policy"), 
         type = case_when(
            TYPE == 1 ~ "Constituent (individual)",
            TYPE == 2 ~ "Constituent (corporate)",
            TYPE == 3 ~ "Constituent (501c3 or local\n government)",
            TYPE == 4 ~ "Policy (corporate)",
            TYPE == 5 ~ "Policy (general)"
         )) 
```


```{r descriptive-helpers}
percent <- function(x){
  y <- x*100 
  y %<>% round() 
  return(y)}

type <- d %>% 
  group_by(Type) %>% 
  summarise(n = sum(per_icpsr_chamber_year_agency_type)) %>% 
  ungroup()
```


We hand-coded data on `r as.integer(sum(type$n))` instances of members of Congress contacting federal agencies.

## Types of Legislator Requests


`r percent(type$n[1]/(type$n[1]+type$n[2]) )`% of the average legislators' contacts with agencies are about constituency service.

`r percent(type$n[2]/(type$n[1]+type$n[2]))`% of the average legislators' contacts with agencies are about policy work.

---

### Percents by Type

We classify legislator requests into five overall types.


```{r}
#| label: data_by_type
#| fig-width: 5.5
#| fig-height: 3.5

# paper figure 
type_totals <- d %>% 
  tidyr::drop_na(Type) %>%  
  mutate(total = sum(per_icpsr_chamber_year_agency_type)) %>% 
  group_by(total, Type, type) %>% 
  summarise(nT =  sum(per_icpsr_chamber_year_agency_type)) %>% 
  mutate(percent = paste0(nT, " = ", 100*round(nT/total, 2), "%"),
         type = str_c(type, "\n    ", percent)) %>% 
  ungroup() %>% 
  group_by(Type) %>% 
  mutate(nt = sum(nT),
         percent_t = paste0(100*round(nt/total, 2), "%"))

type_totals %<>% mutate(type = type %>% 
                          # FOR AJPS - remove N and percent 
                          str_remove_all("\n    .*") %>% 
                        # END FOR AJPS 
                          str_replace_all("\\)", "") %>% 
                          str_replace_all(" \\(", ",\n") 
                          
                        ) %>% 
  ungroup()

N <- type_totals$total |> unique()


# horizontal
type_totals %>% 
  ungroup() %>% 
  ggplot() + 
  geom_col(alpha = .7,
           aes(x = type, fill = Type, y = nT) ) + 
  scale_y_continuous(breaks = seq.int(0,500000, by = 100000), 
                     limits = c(0,400000), 
                     labels = scales::label_comma() ) + 
  labs(x = "",
       fill = "",
       y = paste("Number of contacts"),
       title = "") +
  #geom_text(aes(label = Type, x = Type,y = nT) ) + 
  theme(panel.border = element_blank(),
        panel.grid.major.x = element_blank(),
        axis.ticks = element_blank(),
        #axis.text.x.top = element_text(),
        legend.position ="none") + 
  ggpubr::geom_bracket(label.size = 3, # FOR AJPS
    xmin = type_totals$type[1], 
    xmax = type_totals$type[3], 
    y.position = 380000,
    label = paste(type_totals$percent_t[1], "Constituency service" ),
    #hjust = 1,
    vjust = -1
  ) + 
  ggpubr::geom_bracket(label.size = 3, # FOR AJPS
    xmin = type_totals$type[4], xmax = type_totals$type[5], 
    y.position = 85000,
    label = paste(type_totals$percent_t[5], "Policy work"),
    #hjust = 1,
    vjust = -1
  )+ 
  scale_fill_viridis_d(option = "cividis", end = .8, direction = -1)
```

:::{.callout-important collapse="true"}
```{r echo=verification, eval=verification}
type_totals |> select(type, percent, percent_t)
```
:::

### Percents by chair status 

```{r}
#| label: data_by_type_chair
#| fig-width: 5.5
#| fig-height: 3.5

# extra figure 
type_totals <- d %>% 
  tidyr::drop_na(Type) %>%  
  left_join(member_data |> distinct(icpsr, congress, chair)) %>% 
  group_by(chair) %>% 
  mutate(total = sum(per_icpsr_chamber_year_agency_type)) %>% 
  group_by(total, Type, type, chair) %>% 
  summarise(nT =  sum(per_icpsr_chamber_year_agency_type)) %>% 
  mutate(percent = paste0(nT, " = ", 100*round(nT/total, 2), "%"),
         type = str_c(type, "\n    ", percent)) %>% 
  ungroup() %>% 
  group_by(Type, chair) %>% 
  mutate(nt = sum(nT),
         percent_t = paste0(100*round(nt/total, 2), "%"))

type_totals %<>% mutate(type = type %>% 
                          # FOR AJPS - remove N and percent 
                          str_remove_all("\n    .*") %>% 
                        # END FOR AJPS 
                          str_replace_all("\\)", "") %>% 
                          str_replace_all(" \\(", ",\n") 
                          
                        ) %>% 
  ungroup()


# chair
type_totals %>% 
  ungroup() %>% 
  filter(chair == 1) %>% 
  ggplot() + 
  geom_col(alpha = .7,
           aes(x = type, fill = Type, y = nT) ) + 
  scale_y_continuous(breaks = seq.int(0,500000, by = 100000), 
                     limits = c(0,400000), 
                     labels = scales::label_comma() ) + 
  labs(x = "",
       fill = "",
       y = paste("Number of contacts"),
       title = "Chairs only") +
  #geom_text(aes(label = Type, x = Type,y = nT) ) + 
  theme(panel.border = element_blank(),
        panel.grid.major.x = element_blank(),
        axis.ticks = element_blank(),
        #axis.text.x.top = element_text(),
        legend.position ="none") + 
  ggpubr::geom_bracket(label.size = 3, # FOR AJPS
    xmin = type_totals$type[1], 
    xmax = type_totals$type[3], 
    y.position = 380000,
    label = paste(type_totals$percent_t[1], "Constituency service" ),
    #hjust = 1,
    vjust = -1
  ) + 
  ggpubr::geom_bracket(label.size = 3, # FOR AJPS
    xmin = type_totals$type[4], xmax = type_totals$type[5], 
    y.position = 85000,
    label = paste(type_totals$percent_t[5], "Policy work"),
    #hjust = 1,
    vjust = -1
  )+ 
  scale_fill_viridis_d(option = "cividis", end = .8, direction = -1) 



# non-chair 
type_totals %>% 
  ungroup() %>% 
  filter(chair == 0) %>% 
  ggplot() + 
  geom_col(alpha = .7,
           aes(x = type, fill = Type, y = nT) ) + 
  scale_y_continuous(breaks = seq.int(0,500000, by = 100000), 
                     limits = c(0,400000), 
                     labels = scales::label_comma() ) + 
  labs(x = "",
       fill = "",
       y = paste("Number of contacts"),
       title = "Non-chairs only") +
  #geom_text(aes(label = Type, x = Type,y = nT) ) + 
  theme(panel.border = element_blank(),
        panel.grid.major.x = element_blank(),
        axis.ticks = element_blank(),
        #axis.text.x.top = element_text(),
        legend.position ="none") + 
  ggpubr::geom_bracket(label.size = 3, # FOR AJPS
    xmin = type_totals$type[1], 
    xmax = type_totals$type[3], 
    y.position = 380000,
    label = paste(type_totals$percent_t[6], "Constituency service" ),
    #hjust = 1,
    vjust = -1
  ) + 
  ggpubr::geom_bracket(label.size = 3, # FOR AJPS
    xmin = type_totals$type[4], xmax = type_totals$type[5], 
    y.position = 85000,
    label = paste(type_totals$percent_t[9], "Policy work"),
    #hjust = 1,
    vjust = -1
  )+ 
  scale_fill_viridis_d(option = "cividis", end = .8, direction = -1) 
```

:::{.callout-important collapse="true"}
```{r echo=verification, eval=verification}
type_totals |> distinct(chair, Type, percent_t)
```
:::

## Requests by Percentile

```{r}
#| label: percentiles
#| fig-height: 3.4
#| fig-width: 6
#| cache: false

percentiles <- dcounts %>% 
  dplyr::filter(year > 2006, year < 2021) %>% 
  dplyr::group_by(member_state, chamber, year) %>% 
  dplyr::summarise(n = sum(per_icpsr_chamber_year_agency_type)) %>%
  dplyr::group_by(member_state, chamber) %>% 
  dplyr::summarise(mean = mean(n)) %>% 
  dplyr::ungroup() %>% 
  dplyr::group_by(chamber) %>% 
  dplyr::mutate(Percentile = dplyr::ntile(mean, 100),
         rank = dplyr::dense_rank(-mean)) %>% 
  dplyr::arrange(-Percentile) %>% 
  dplyr::select(member_state, Percentile, mean, chamber, rank) %>% 
  dplyr::distinct() 


percentiles |>
  arrange(rank) |>
  kablebox()



# percentiles %>%
#     ggplot() +
#     geom_col(aes(x = Percentile, y = mean),
#              color = "grey",
#              width = .000001,
#              fill = "black",
#              position = "dodge") +
#   geom_point(aes(x = Percentile, y = mean), color = "light blue") +
#   geom_text(aes(x = Percentile, y = mean,
#                 label = ifelse(rank <24 | Percentile < 50,
#                                member_state, "")),
#             check_overlap = T,
#                   size = 3,
#                   hjust = "inward") +
#   labs(#title = "Average Legislator Requests per Year by Percentile",
#        x = "Percentile within chamber",
#        y = "Average requests per year") +
#   facet_grid(. ~ chamber , scales = "free_y")
```

:::{.callout-important collapse="true"}
```{r echo=verification, eval=verification}
percentiles |>
  group_by(chamber) |>
  summarise(chamber_average = mean(mean)) 
```
:::
  
:::{.callout-important collapse="true"}
```{r echo=verification, eval=verification}
percentiles |> arrange(rank) |> head()
```
:::


```{r}
#| label: percentiles-chamber
#| fig-height: 3.4
#| fig-width: 3
#| cache: false
#| 
percentiles %>% 
    filter(chamber == "Senate") %>% 
    ggplot() + 
    geom_col(aes(x = Percentile, y = mean), 
             color = "grey", 
             width = .000001,
             fill = "black",
             position = "dodge") + 
  geom_point(aes(x = Percentile, 
                 y = mean), 
             color = "light blue") + 
  geom_text(aes(x = Percentile, 
                y = mean, 
                label = ifelse(rank <24 | Percentile < 50,
                               member_state, ""
                               )
                ), 
            check_overlap = T, 
                  size = 3,
                  hjust = "inward") + 
  # theme_minimal() + 
  labs(#title = "Average Legislator Requests per Year by Percentile",
       x = "Percentile in the Senate",
       y = "Average requests per year") 

percentiles %>% 
  filter(chamber == "House") %>% 
    ggplot() + 
    geom_col(aes(x = Percentile, y = mean), 
             color = "grey", 
             width = .000001,
             fill = "black",
             position = "dodge") + 
  geom_point(aes(x = Percentile, y = mean), color = "light blue") + 
  geom_text(aes(x = Percentile, y = mean, 
                label = ifelse(rank <24 | Percentile < 50,
                               member_state, "")), 
            check_overlap = T, 
                  size = 3,
                  hjust = "inward") + 
  # theme_minimal() + 
  labs(#title = "Average Legislator Requests per Year by Percentile",
       x = "\nPercentile in the House",
       y = "Average requests per year") 
```

\clearpage 



## Requests by Year

```{r counts-per-year, fig.height=3, fig.width=5.7, cache=TRUE, eval=TRUE}
#counts-per-year

dcounts_per_legislator <- dcounts  %>% 
  group_by(bioname, year) %>% 
  mutate(per_bioname_year = sum(per_icpsr_chamber_year_agency_type)) %>%
  ungroup() 

schumer2013 <- dcounts_per_legislator %>% filter(bioname == "SCHUMER, Charles Ellis (Chuck)",
                   year == 2013) %>% .$per_bioname_year %>% unique()

cruz2013 <- dcounts_per_legislator %>% filter(bioname == "CRUZ, Rafael Edward (Ted)",
                   year == 2013) %>% .$per_bioname_year %>% unique()

mcconnell2013 <- dcounts_per_legislator %>% filter(bioname == "McCONNELL, Addison Mitchell (Mitch)",
                   year == 2013) %>% .$per_bioname_year %>% unique()

# plot a line for all legislator-year counts in the data (this is a lot of data points and thus takes a long time to render)
p <- dcounts_per_legislator %>% 
  filter(year > 2006, year <2018) %>%
  distinct(bioname, per_bioname_year, year, chamber) %>% 
  filter(per_bioname_year > 0) %>% 
  ggplot() + 
  geom_line(aes(x = year, 
                y = per_bioname_year, 
                group = bioname, 
                color = chamber), 
            alpha = .1) +
  geom_line(aes(x = year, 
                group = bioname, 
                color = chamber,
                y = ifelse(bioname == "SCHUMER, Charles Ellis (Chuck)", per_bioname_year, NA))) + 
  geom_label(x = 2013, 
             y = schumer2013, 
             label = "Chuck Schumer") +
  geom_line(aes(x = year, group = bioname, color = chamber,
                y = ifelse(bioname == "CRUZ, Rafael Edward (Ted)", per_bioname_year, NA))) + 
  geom_label(x = 2013, 
             y = cruz2013, 
             label = "Ted Cruz") +
  geom_line(aes(x = year, group = bioname, color = chamber,
                y = ifelse(bioname == "McCONNELL, Addison Mitchell (Mitch)", per_bioname_year, NA))) + 
  geom_label(x = 2013, 
             y = mcconnell2013, 
             label = "Mitch McConnell") +
  labs(x = "",
       color = " ",
       y = paste("Requests per legislator per year"),
       title = "") +
  scale_x_continuous(breaks = unique(dcounts$year)) + 
  scale_color_viridis_d(begin = 0, end = .6, option = "cividis", direction = -1) 

# Non-AJPS formatting 
# p + 
  # theme_minimal() + 
  # theme(axis.text.x = element_text(angle = 30, vjust = 0) ) 


# FOR AJPS 
p +
  theme(panel.background = element_blank(), 
        legend.position = "inside",
        #FIXME NOTE: legend justification requires ggplot2 v3.5 or higher https://stackoverflow.com/questions/78212838/error-when-running-code-examples-from-usmap-r-package
        legend.justification.inside = c(1, 1), 
        #legend.position.inside = c(1, 1),
        axis.ticks = element_blank()
        ) 
```   


\clearpage

##  Example

Rep. Barbara Comstock worked in Rep. Frank Wolf's congressional office for five years, described him as a "longtime mentor," and claimed that Wolf first urged her to run for office. He endorsed and campaigned with her. 

Notice several patterns
- dip in constituency service when Wolf is no longer running for re-election
- further dip with transition
- quick rebound as Comstock gets her office in order
- inheriting a highly effective office, Comstock is far above average House member

:::{.callout-important collapse="true"}

```{r comestock}
dcounts %>% 
  filter(bioname == "COMSTOCK, Barbara J.", year %in% c(2015, 2016)) |> 
  group_by(year) %>% 
  summarise(n = sum(per_icpsr_chamber_year_agency_type))
```
:::

```{r case-study-function}
case_study <- function(cq){

  CHAMBER <- filter(member_data, cqlabel == cq) %>% 
    .$chamber %>% .[1]

dcounts %>% 
  group_by(member_state, year, chamber, cqlabel) %>% summarise(n = sum(per_icpsr_chamber_year_agency_type)) %>% 
  ungroup() %>% 
  group_by(chamber) %>% 
  mutate(mean_per_chamber = mean(n) %>% round(0)) %>% 
  filter(cqlabel == cq, year > 2007, year <2017) %>% 
  ggplot() +
  aes(x = year, 
      y = n, 
      fill = member_state %>% str_replace("-.*", "\\)")) + 
  geom_col(alpha = .5, position = "dodge") +
  geom_hline(aes(yintercept = mean_per_chamber), linetype = 2) + 
  geom_text(aes(y = mean_per_chamber), 
            x = 2007.5, 
            label = "Chamber average", check_overlap = T,
            size = 3, vjust = 1.3, hjust = 0) + 
  scale_x_continuous(breaks = seq(2008, 2016, 1)) +
  labs(x = "",
       y = "Number of requests", 
       fill = "") +  # str_c(CHAMBER, "-", cq) %>% str_remove_all("\\(|\\)|NA") ) +
  theme(panel.grid.major.x =  element_blank(),         
        legend.position = "bottom",
        axis.title.x = element_text(margin = unit(c(-5, 0, 0, 0), "mm")),
        # # FOR AJPS
        # axis.text.x = element_text(angle = 45), 
        # # END AJPS 
        panel.grid.minor.x =  element_blank() )+
    scale_fill_viridis_d(begin = 0, end = .6, option = "cividis", direction = -1) 
  
} 
```



```{r cases}
#| fig-width: 5.7
#| fig-height: 2.5
#| out-width: "100%"


# plot for WI for paper
case_study("(WI)")

case_study("(WI-7)")

# Wolf --> Comstock example 
case_study("(VA-10)")


# 
# case_study("(NY-07)")
# 
# case_study("(NY-14)")

# plot all 
# cases <- unique(member_data$cqlabel) #%>% head()

# map(cases, case_study )

```



## Requests by State Population


```{r pop, fig.width=6, fig.height=4}
dcounts %>% 
  filter(chamber == "Senate") %>% 
    group_by(member_state, year, pop2010) %>% 
  summarise(n = sum(per_icpsr_chamber_year_agency_type)) %>% 
    group_by(member_state, pop2010) %>%
  summarise(mean = mean(n)) %>% ungroup() %>% 
    ggplot() + 
    geom_point(aes(x = pop2010, y = mean), color = "light blue") + 
    geom_smooth(aes(x = pop2010, y = mean)) + 
  geom_text_repel(
    aes(
    x = pop2010,
    y = mean, 
    label = ifelse(mean > 390 | log(pop2010) > 17.0 | mean < 100,# & (log(pop2010) > 27 | log(pop2010) < 14), 
                   member_state  ,
                   "")), 
            seed = 44,
            check_overlap = T, 
            min.segment.length = 0,
            size = 3) + 
  labs(#title = "",
       x = "State population (log scale)",
       y = "Average number of requests per year") +
  scale_x_log10(labels = scales::comma) + 
  scale_y_continuous(labels = scales::comma, limits = c(0,500) ) 
```   





## Defining Prestige Committees

All of these findings replicate with various interpretations of "prestige" committees. To measure committee prestige, we use a revealed preference
    approach--what do members think is most valuable--using party
    rules/norms that limit members to serving on only one of a small
    number of desirable committees. For House members, the "exclusive"
    committees are: Appropriations, Energy & Commerce, Financial
    Services, Rules, and Ways & Means (CRS 2022). For Senators, the
    exclusive (also called "Super A") Committees are: Appropriations,
    Armed Services, Finance, and Foreign Relations (CRS 2024).



## Count Means

```{r count-means}
# check N
dcounts_tenure %>% tally(perYear, name = "Member-Level Observations") |> kable()
# dcounts_ratio %>% tally(perCon) |> kable()
# dcounts_ratio %>% tally(perPol) |> kable()
dcounts_per_district %>% ungroup %>%  tally(perYear, name = "District-Level Observations") |> kable()

# check n per year 
dcounts_tenure %>% filter(year > 2006) %>%  group_by(year) %>% tally(perYear) |> kablebox_long()

# average per member
dcounts_tenure %>% left_join(member_data %>% distinct(bioname, icpsr)) %>%
  group_by(bioname, year) %>% 
  summarise(perYear = sum(perYear)) %>% 
  group_by(bioname) %>% 
  summarise(average_per_year = mean(perYear), average_per_year) |> 
  arrange(-average_per_year) |> 
  kablebox()

# average per member per agency 
dcounts_tenure %>% left_join(member_data %>% select(bioname, icpsr)) %>%
  group_by(bioname) %>% 
  summarise(average_per_year_per_agency = mean(perYear)) |> arrange(-average_per_year_per_agency) |> 
  kablebox()


# per member per agency 
dcounts_tenure %>% left_join(member_data %>% distinct(bioname, icpsr)) %>%
  group_by(bioname, agency) %>% 
  summarise(per_year_per_agency = perYear) |> arrange(-per_year_per_agency) |> 
  kablebox()



# mean 
perYear_mean1 <- dcounts_tenure$perYear |> mean()
perYear_mean_total <- dcounts_tenure |> 
  group_by(icpsr, year) |> 
  transmute(perYearTotal = sum(perYear))
perYear_mean_total <- mean(perYear_mean_total$perYearTotal) |> round()

perYear_mean_policy <- dcounts_tenure |> 
  group_by(icpsr, year) |> 
  transmute(perYear = sum(perYear_policy))
perYear_mean_policy <- mean(perYear_mean_policy$perYear) |> round()

perYear_mean_con <- dcounts_tenure |> 
  group_by(icpsr, year) |> 
  transmute(perYear = sum(perYear_con))
perYear_mean_con <- mean(perYear_mean_con$perYear) |> round()

# Better variable names for tables
dcounts_tenure %<>% 
  mutate(Legislator = icpsr,
         Legislator_x_Agency = icpsr_agency,
         Year_x_Agency = agency_year)

# total per agency
dcounts_tenure %>% group_by(agency) %>% summarise(n = perYear %>% sum()) %>% arrange(-n) %>% kablebox()

# total per legislator-agency pair 
dcounts_tenure %>% group_by(Legislator_x_Agency) %>% summarise(n = perYear %>% sum()) %>% arrange(-n) %>% kablebox()
```





### Gini coefficients 

```{r gini}
gini <- dcounts_tenure |> 
  ungroup() |> 
  group_by(year, icpsr) |> 
  summarize(perYear = sum(perYear)) |> 
  ungroup() |> 
group_by(year) |> 
  summarise(gini = round(ineq::Gini(perYear),2)) |>
  arrange(- year) |> 
  filter(year > 2006) 

gini|> 
  kablebox()

gini |> 
  ggplot() +
  aes( x = year, y = gini) + 
  geom_point() + 
  geom_smooth(method = "lm")

gini_min <- min(gini$gini)
gini_max <- max(gini$gini)


gini2 <- dcounts_tenure |> 
  ungroup() |> 
  group_by(year, chamber, icpsr) |> 
  summarize(perYear = sum(perYear)) |> 
  ungroup() |> 
group_by(year, chamber) |> 
  summarise(gini = round(ineq::Gini(perYear),2)) |>
  arrange(- year) |> 
  filter(year > 2006) 

gini2|> 
  kablebox()

gini2 |> 
  ggplot() +
  aes( x = year, y = gini, color = chamber) + 
  geom_point() + 
  geom_smooth(method = "lm")


```


:::{.callout-important collapse="true"}
```{r echo=verification, eval=verification}
gini %<>% filter(year > 2017)

min(gini$gini)
max(gini$gini)
```
:::



In 2023, Colombia had the highest income inequality Gini coefficient at .54. 

https://ourworldindata.org/what-is-the-gini-coefficient

Top 10 Gini Coefficients in 2023

1. Colombia	0.54
1. Brazil	0.52	
1. Zambia	0.51
1. Angola	0.51				
1. Mozambique	0.50	
1. Zimbabwe	0.50
1. Kosovo	0.49
1. Panama	0.49
1. Honduras	0.47	
1. Costa Rica	0.47

<!--(The Gini coefficient for House campaign spending in 2016 was .29).  --> 


---

\clearpage
