---
title: "Replication Code and Robustness Checks"
subtitle: ""
author: Devin Judge-Lord
format: 
  #pdf: 
  html:
      self-contained: true
      toc: true
      code-fold: true
editor_options: 
  chunk_output_type: console
execute:
  message: false
  warning: false
---

Packages: 
  
  - `tidyverse` and `magrittr`, for data wrangling
- `scales` for plot scales 
- `ggrepel` for plot labels
- `here` for file paths 
- `knitr` for document formatting 
- `kableExtra` for table formatting 
- `modelsummary` for regression tables 
- `marginaleffects` for predictions 
- `fixest` --- statistical package for fixed effects estimation 
- `ineq` to calculate GINI coefficients


```{r global.options, include=FALSE, purl=FALSE, cache=FALSE}
testing = F
verification = F
here::here("code", "qmd_global_options.R") |> source() 

# plotting functions 
here::here("code", "ggcompetitive.R") |> source() 
here::here("code", "ggchair.R") |> source() 
here::here("code", "ggtenure.R") |> source() 

# coef map
here::here("code", "cm.R") |> source() 
here::here("code", "modelsummary_formatting.R") |> source() 


# functions 
here::here("code", "post_merge_transformations.r") |> source()
```


# Replication Data

```{r member-data, cache=FALSE}
# New member data 
load(here::here("data", "member_data.Rdata"))

# INSPECT
member_data |> drop_na(prestige) |> count(prestige) |> kable()
```

## Counts
```{r count-data, cache=FALSE}
# COUNT DATA 
load(here::here("data", "corr_counts.Rdata"))

## just in case it was saved as grouped data 
corr_counts %<>% ungroup()

# subset to 2007-2020
corr_counts  %<>% filter(year > 2006, year < 2021)


####################
# TRANSFORMATIONS #  
###################
# two-way fixed effects 
d <- corr_counts |> 
  ungroup() |> 
  mutate(
    icpsr_agency = paste(agency, icpsr, sep='_'),
    agency_year = paste(agency, year, sep='_')
  )


# CONGRESS VAR 
year_congress<- function(year){
  return(floor((year - 1787)/2))
}

d %<>% mutate(congress = year_congress(year))
```





## Drop chamber switchers 

```{r drop-chamber-switchers, cache=FALSE}
#FIXME THIS SHOULD BE AT TOP 
# make icpsr year variable 
d %<>% mutate( icpsr_year = paste(icpsr, year, sep='_') )

## chamber switchers  in original data (party switchers are not an issue because they net new ICPSR ids)
chamber_switchers  <- d |> 
  distinct(icpsr_year, agency, chamber) |>
  add_count(icpsr_year, agency,  #party, 
            name = "n") |>
  filter(n > 1) |> 
  distinct(icpsr_year, chamber) |> 
  arrange(icpsr_year)

# DROP CHAMBER SWITCHERS
d %<>% filter(!icpsr_year %in% chamber_switchers$icpsr_year)
```

## Total counts 

```{r data-transformations, cache=FALSE}
# This chunk takes the minimal count data and creates legislator-level and district-level yearly count and ratio data
# These are then used to estimate the models
# the key DVs are
# - perYear = counts per year (member level and district level)
# - ratio = ratio of policy work to constituency service

##creating the member-level aggregate count variables

# TOTAL counts 
dcounts_total <- d |>
  group_by(agency, icpsr, chamber, year, congress) |>
  summarise(perYear = sum(per_icpsr_chamber_year_agency_type)) |> 
  ungroup() |> 
  left_join(member_data) |>
  post_merge_transformations() |> 
  ungroup() |> 
  distinct() 

# DISTRICT counts 
dcounts_district <- dcounts_total   |>
  ungroup() |> 
  group_by(agency, state_dist, chamber, year, congress) |>
  summarise(perYear = sum(perYear) ) |>
            #perYear_con = sum(perYear_con),
            #perYear_policy = sum(perYear_policy),
  ungroup() |> 
  left_join(member_data) |>
  post_merge_transformations() |> 
  ungroup() |> 
  distinct()

# rename first year as "new_member" 
dcounts_total$new_member <- dcounts_total$first

save(dcounts_total, file =  here::here("data", "dcounts_total.rda"))
save(dcounts_district, file =  here::here("data", "dcounts_district.rda"))

if(testing){
# CHECK MISSINGNESS
sum_na <- function(x){is.na(x) |> sum() }

dcounts_total  |>  summarise_all(sum_na) |> pivot_longer(everything()) |> arrange(-value) |> filter(value>0 ) |> kable()
} 

## Means for paper
mean_total <- mean(dcounts_total$perYear)

# mean per year 
perYear_mean_total <- dcounts_total |> 
  group_by(icpsr, year) |> 
  transmute(perYearTotal = sum(perYear))
perYear_mean_total <- mean(perYear_mean_total$perYearTotal) |> round()

## Ns
n2007_2020 <- dcounts_total$perYear |> sum()
n_agency <- dcounts_total$agency |> unique() |> length()

save(mean_total,# mean_con, mean_pol, 
     perYear_mean_total,
     n_agency, n2007_2020, # n2007_2020coded, 
     modelsummary_AJPS,
     file = here::here("data", "means.Rdata"))
```

:::{.callout-important collapse="true"}
```{r echo=verification, eval=verification, cache=FALSE}
n_agency
n2007_2020
n2007_2020coded
```
:::


```{r testing, cache=FALSE}

############################
if(testing){
# inspect duplicates 
d <- d |> 
  ungroup() |>
  distinct() |>
  add_count(icpsr, year, agency,  #party, 
            name = "n") 


d |>filter(n > 1) |> distinct(icpsr, year) 
} 
```
