---
title: "Replication Code and Robustness Checks"
subtitle: "to replace fenegbin with fenegbin"
author: Devin Judge-Lord
format: 
  #pdf: 
  html:
      self-contained: true
      toc: true
      code-fold: true
editor_options: 
  chunk_output_type: console
execute:
  message: false
  warning: false
---

Packages: 
  
  - `tidyverse` and `magrittr`, for data wrangling
- `scales` for plot scales 
- `ggrepel` for plot labels
- `here` for file paths 
- `knitr` for document formatting 
- `kableExtra` for table formatting 
- `modelsummary` for regression tables 
- `marginaleffects` for predictions 
- `fixest` --- statistical package for fixed effects estimation 
- `ineq` to calculate GINI coefficients


```{r global.options, include=FALSE, purl=FALSE, cache=FALSE}
testing = F
verification = T
here::here("code", "qmd_global_options.R") |> source() 

# plotting functions 
here::here("code", "ggcompetitive.R") |> source() 
here::here("code", "ggchair.R") |> source() 
here::here("code", "ggtenure.R") |> source() 
here::here("code", "ggdistrict.R") |> source() 
source(here::here("code", "plot_effect.R"))



# coef map
here::here("code", "cm.R") |> source() 
here::here("code", "modelsummary_formatting.R") |> source()
```

# Data

```{r data, cache=FALSE}
load(here::here("data", "dcounts_total.rda"))
names(dcounts_total)
load(here::here("data", "dcounts_district.rda"))
load(here::here("data", "member_data.Rdata"))
load(here::here("data", "means.Rdata"))

# CHECK MISSINGNESS
sum_na <- function(x){is.na(x) |> sum() }

dcounts_total  |>  summarise_all(sum_na) |> pivot_longer(everything()) |> arrange(-value) |> filter(value>0 ) |> kable()

dcounts_total <- dcounts_total |> 
  mutate(same_party = as.numeric(same_party),
         pop2010m = pop2010/1000000,
         Legislator = icpsr,
         District = state_dist,
         Year = year,
         first_two = first + second, 
         experience = ifelse(first_two == 1, 0, 1),
         distance = abs(nominate_dim1 - agency_ideo),
    # fixed effects 
    icpsr_agency = paste(agency, icpsr, sep='_'),
    agency_year = paste(agency, year, sep='_'),
    Year_x_Agency = agency_year,
    Legislator_x_Agency = icpsr_agency)


dcounts_district <- dcounts_district |>
  mutate(same_party = as.numeric(same_party),
         Legislator = icpsr,
         District = state_dist,
         Year = year,
         first_two = first + second, 
         experience = ifelse(first_two == 1, 0, 1),
         distance = abs(nominate_dim1 - agency_ideo),
    # fixed effects 
    icpsr_agency = paste(agency, icpsr, sep='_'),
    agency_year = paste(agency, year, sep='_'),
    Year_x_Agency = agency_year,
    Legislator_x_Agency = icpsr_agency)

if(testing){
# CHECK MISSINGNESS
sum_na <- function(x){is.na(x) |> sum() }

dcounts_total  |>  summarise_all(sum_na) |> pivot_longer(everything()) |> arrange(-value) |> filter(value>0 ) |> kable()
} 



```

```{r}
#| label: "percentile"
#| fig-cap: "code/figs/percentile-[1:2].png"
#| layout-ncol: 2
#| fig-height: 3.5
#| fig-width: 3.5
#| fig-subcap: 
#|   - "1"
#|   - "2"
#| out-width: "100%"
#| fig-show: "hold"
#| 
source(here::here("code", "percentile_plot.R"))

plot_data(d = dcounts_total |> filter(chamber == "Senate"))
plot_data(d = dcounts_total |> filter(chamber == "House"))
```


### Gini coefficients 

```{r gini}
gini <- dcounts_total |> 
  ungroup() |> 
  group_by(year, icpsr) |> 
  summarize(perYear = sum(perYear)) |> 
  ungroup() |> 
group_by(year) |> 
  summarise(gini = round(ineq::Gini(perYear),2)) |>
  arrange(- year) |> 
  filter(year > 2006) 

gini|> 
  kablebox()

gini |> 
  ggplot() +
  aes( x = year, y = gini) + 
  geom_point() + 
  geom_smooth(method = "lm")

gini_min <- min(gini$gini)
gini_max <- max(gini$gini)


gini2 <- dcounts_total |> 
  ungroup() |> 
  group_by(year, chamber, icpsr) |> 
  summarize(perYear = sum(perYear)) |> 
  ungroup() |> 
group_by(year, chamber) |> 
  summarise(gini = round(ineq::Gini(perYear),2)) |>
  arrange(- year) |> 
  filter(year > 2006) 

gini2|> 
  kablebox()

gini2 |> 
  ggplot() +
  aes( x = year,
       y = gini, 
       color = chamber) + 
  geom_point() 
  #geom_smooth(method = "lm")
  

gini %<>% filter(year > 2017)

min(gini$gini)
max(gini$gini)
```




In 2023, Colombia had the highest income inequality Gini coefficient at .54. 

https://ourworldindata.org/what-is-the-gini-coefficient

Top 10 Gini Coefficients in 2023

1. Colombia	0.54
1. Brazil	0.52	
1. Zambia	0.51
1. Angola	0.51				
1. Mozambique	0.50	
1. Zimbabwe	0.50
1. Kosovo	0.49
1. Panama	0.49
1. Honduras	0.47	
1. Costa Rica	0.47

<!--(The Gini coefficient for House campaign spending in 2016 was .29).  --> 


## Values for Predictions

The most frequent legislator agency pair: McCain x VA with 2159 letters!

The average is  `r perYear_mean_total` letters per legislator per year, `r mean_total` letters per agency per year.
For predictions, we need an average member-year-agency triad. The first table below shows the members who averaged  `r perYear_mean_total`, entered Congress between 2007 and 2011, were observed in our data for at least seven years, and most often submitted exactly one letter to an agency (the closest integer  `r perYear_mean_total` ). For realism, this person would ideally become a chair at some point in our data. 

:::{.callout-warning}
In the figures below, uncertainty intervals around predictions do not include uncertainty in the estimates of the fixed effects. This is because the standard errors returned by marginaleffects::predictions() do not reflect uncertainty in the fixed effect estimation. Since we are just using predictions to illustrate the effects of interest, not make any claims about particular years, legislators, or agencies (the fixed effects), the uncertainty in the fixed effect estimates is not relevant for our use case (illustrating main effects, for which we do have estimates of uncertainty). However, we wish to alert users of these code that they should not use the predictions to make such claims. 

For further discussion, see [this discussion](https://github.com/vincentarelbundock/marginaleffects/issues/1487) that led the authors of the marginaleffects package to [stop](https://marginaleffects.com/bonus/NEWS_r.html#section) allowing users to calculate predictions for fixed effects models (due to their potential misuses and possible differences from uncertianty bounds that do include uncertianty related to the estimation of fixed effects).
:::

<!--
Of the modal legislators, 
John Barrasso and
Phil Roe 
meet this last criterion. However, whereas Barrasso's seat was always held by a Republican, Roe's seat flipped, adding realism to our predictions from models that include whether a legislator is replacing a co-partisan or not. 
Roe entered in 2009 and became a chair in 2017.
The IRS is a fairly modal agency, so predictions are Phil Roe X Treasury IRS X 2015. 
Other legislators, years, and agencies are simply intercept shifts. 
--> 

### Modal agencies

```{r modal-agencies}
 dcounts_total %>% 
 group_by(agency, year) %>% 
  summarise(perAgency = sum(perYear),
            agency_ideo = mean(agency_ideo)) %>% 
  ungroup() %>% 
  mutate(median = median(perAgency),
         diff = abs(perAgency - median)) %>% 
  arrange(diff) %>% 
  drop_na(agency_ideo) %>% 
  kablebox()
```


### Modal legislators

```{r modal-legislators}
modal <- dcounts_total %>% 
  group_by(icpsr) %>% 
  filter(first_year > 2006, first_year < 2013,  max_year > 6) %>% 
  mutate(Chair = sum(chair, na.rm = T) >1) %>% 
  group_by(icpsr, year) %>%
  mutate(perLeg = sum(perYear)) %>% 
  filter(perYear == 1, perLeg == perYear_mean_total  ) %>% 
  select(perAgency = perYear, 
         congress,
         perLeg, 
         agency, bioname, 
           Legislator_x_Agency,
                        Year_x_Agency,
                        Legislator,
                        Year, first_year, max_year, Chair) %>% 
  distinct() %>% 
  ungroup() %>% left_join(member_data %>% select(bioname, icpsr, congress))


modal %>%
  mutate(average = perLeg) %>% 
  count(average, bioname, first_year, max_year, Chair, sort = T, name = "agency_year_count == 1") %>% 
  distinct() %>%
  arrange(-Chair) %>%
  kablebox()
```

### Modal legislator-agency pairs

```{r values, fig.width=5, fig.height=3}

modal %<>% filter(Chair) %>% distinct()

modal %>%
  kablebox()

dcounts_total %>% 
  group_by(icpsr, year) %>% 
  mutate(perYearTotal = sum(perYear)) %>%
  #mutate (perLegislator = sum(perYear)) %>% 
  ungroup() %>% 
  mutate(meanLeg = mean(perYearTotal),
         meanYear = mean(perYear)) %>%
  filter( abs(perYearTotal - perYear_mean_total) < 10,   
          perYear < 10 )  %>% 
  drop_na(agency_ideo) %>% 
  ggplot() +
  aes(x = perYear, 
      y = perYearTotal) + 
  geom_jitter(alpha = .5) + 
  geom_vline(aes(xintercept = meanYear), color = "blue") + 
  geom_hline(aes(yintercept = meanLeg), color = "blue") + 
  geom_text_repel(
    aes( label = ifelse(icpsr_agency %in% modal$Legislator_x_Agency & agency_year %in% modal$Year_x_Agency , 
                     icpsr_agency, 
                     NA)  ),
    color = "red", 
    box.padding = 0.5, 
    max.overlaps = Inf
    ) + 
  labs(x = "Contacts per Legislator per Agency per year",
       y = "Contacts per Legislator per year") + 
  scale_x_continuous(breaks = seq.int(0, 9, length.out =  10))

modal %>%
  ungroup() %>% 
  distinct(agency, perAgency, bioname, 
           Legislator_x_Agency,
                        Year_x_Agency,
                        Legislator,
                        Year) %>% 
  kablebox()


# modal pair  
n <- 1 

# by chair and President's party
values <- tidyr::expand(dcounts_total,
                        chair = chair, 
                        oversight = 0,
                        distance = dcounts_total$distance |> mean(na.rm = T),
                        ranking_minority	= FALSE, 
                        prestige = TRUE, 
                        competitive = FALSE,
                        competitive_primary = FALSE,
                        experience = 1, 
                        first = FALSE,
                        second = FALSE,
                        third = FALSE,
                        fourth = FALSE,
                        fifth = FALSE, 
                        sixth = FALSE,
                        agency =  modal$agency[n],
                        Legislator_x_Agency = modal$Legislator_x_Agency[n],
                        Year_x_Agency = modal$Year_x_Agency[n],
                        Legislator =  modal$Legislator[n],
                        Year =  modal$year[n],
                        majority = TRUE,
                        presidents_party = presidents_party
                   ) %>% 
  drop_na(majority, chair)

# by year 
values_tenure <- tidyr::expand(dcounts_total,
                        chair = chair, 
                        oversight = 0,
                                                distance = dcounts_total$distance |> mean(na.rm = T),
                        ranking_minority	= FALSE, 
                        prestige = TRUE, 
                        competitive = FALSE,
                        competitive_primary = FALSE,
                        experience = experience, 
                        # first = first,
                        # second = second,
                        # third = third,
                        # fourth = fourth,
                        # fifth = fifth, 
                        # sixth = sixth,
                        agency =  modal$agency[n],
                        Legislator_x_Agency = modal$Legislator_x_Agency[n],
                        Year_x_Agency = modal$Year_x_Agency[n],
                        Legislator =  modal$Legislator[n],
                        Year =  modal$year[n],
                        majority = TRUE,
                        presidents_party = TRUE
                   ) %>% 
  drop_na(chair)
```


# Model Results: Counts per member per year

Clustering standard errors at the legislator level:

["Clustering on the panel variable produces an estimator of the VCE that is robust to cross-sectional heteroskedasticity and within-panel (serial) correlation that is asymptotically equivalent to that proposed by Arellano (1987)"](https://www.stata.com/manuals13/xtxtreg.pdf)

We use `fixest::fenegbin` here and replicated the main models using `xtreg` in Replication.do.
See more about how robust (clustered) standard errors with fixed effects are calculated by `fixest` [here](https://lrberge.github.io/fixest/articles/standard_errors.html) and by  `xtreg` [here](https://www.stata.com/manuals13/xtxtreg.pdf).


---

## Total Letters 

### Member-level Coefficient Plots

- Figures: `code/figs/negbin-m-total-[1:4].png`

```{r}
#| label: "negbin-m-total"
#| fig-cap: "code/figs/negbin-m-total-[1:4].png"
#| layout-ncol: 2
#| fig-height: 4.5
#| fig-subcap: 
#|   - "1"
#|   - "2"
#|   - "3"
#|   - "4"
#| out-width: "100%"
#| fig-show: "hold"


# cross-sectional 
m_total_cross <-fenegbin (perYear ~ 
                         chair + ranking_minority + prestige + oversight +
                    experience + 
                    majority + presidents_party | Year_x_Agency,
                    cluster = "Legislator", 
           data = dcounts_total)


if(testing){modelsummary::modelsummary(m_total_cross)}

coefplot(m_total_cross, horiz = T, drop = "(Intercept)|.theta") 



# 2
m_total_did <-fenegbin (perYear ~ 
                       chair + ranking_minority + prestige + oversight +  
                    experience + 
                    majority + presidents_party | Year_x_Agency + Legislator_x_Agency, 
                    cluster = "Legislator",
                    # ALT vcov = hetero ~ ssc(cluster.adj = TRUE),
           data = dcounts_total)

if(testing){modelsummary::modelsummary(m_total_did)}

coefplot(m_total_did, horiz = T, drop = ".theta") 


# 3
m_total_2nd <-fenegbin (perYear ~ 
                       chair + ranking_minority + prestige + oversight +  
                    experience + 
                    majority + presidents_party | Year_x_Agency, 
                    cluster = "Legislator", 
           data = dcounts_total %>% filter(survive == 1))

if(testing){modelsummary::modelsummary(m_total_2nd)}
coefplot(m_total_2nd, horiz = T, drop = ".theta") 


# # 4
# m_logtotal_did <-fenegbin (log(perYear + 1) ~ 
#                           chair + ranking_minority + prestige + oversight +  
#                     experience + 
#                     majority + presidents_party | Year_x_Agency + Legislator_x_Agency, 
#                     cluster = "Legislator", 
#            data = dcounts_total)
# 
# if(testing){modelsummary::modelsummary(m_logtotal_did)}
# 
# coefplot(m_logtotal_did, horiz = T, drop = ".theta") 


```

### Total Letters Table 

- Models: `models/models_total_negbin.Rdata` 


```{r models_total}
models_total <- list(
  "(1)" = m_total_cross,
  "(2)" = m_total_did,
  "(3)" =  m_total_2nd#,
  #"(4)" = m_logtotal_did
)

rows <- tibble(
  term = c("Dependent variable", 
           "Majority",
           "President's party",
           "All legislators", 
           "Served at least 2nd term"),
  `(1)` = c("Count", "X", "X", "X", ""),
  `(2)` =c("Count", "X", "X", "X", ""),
  `(3)` = c("Count", "X","X","", "X")#,
  #`(4)` = c("Log(Count+1)","X","X", "X", "") 
)

rows <- tibble(
  term = c("Dependent variable", 
           #"Majority",
           #"President's party",
           "All legislators", 
           "Served at least 2nd term"),
  `(1)` = c("Count", "X", ""),
  `(2)` =c("Count", "X", ""),
  `(3)` = c("Count","", "X")#,
 # `(4)` = c("Log(Count+1)", "X", "") 
)

attr(rows, 'position') <- c(0, 20,21,22,23)

attr(rows, 'position') <- c(0)


# HTML
modelsummary(models_total)


if(testing){
rows <- tibble(
  term = c("Dependent variable"),
  `(1)` = c("Count"),
  `(2)` =c("Count"),
  `(3)` = c("Count")#,
  #`(4)` = c("Log(Count+1)") 
)

attr(rows, 'position') <- c(0)


modelsummary::modelsummary(models_total,  
             add_rows = rows,     
             notes = "") 
}
```


### Total Letters Predictions 

- Figures: `code/figs/negbin-m-total-predicted-[1:4].png`


```{r}
#| label: "negbin-m-total-predicted"
#| fig-cap: "code/figs/negbin-m-total-predicted"
#| layout-ncol: 2
#| fig-height: 3
#| fig-subcap: 
#|   - "1"
#|   - "2"
#|   - "3"
#|   - "4"
#| out-width: "100%"
#| fig-show: "hold"

predicted <- predictions(m_total_cross,
                         newdata = values)

# Cross-sectional predictions
predicted %>%
    mutate(estimate = estimate*n_agency, 
         conf.high = conf.high*n_agency, conf.low = conf.low*n_agency) %>%  
  ggchair() + 
  labs(title =  "", # "Predicted total letters per year",        subtitle = "(cross-sectional)",
       x = "",
       y = "Predicted total letters per year",
       fill = "",
       color = "",
       shape = "") 

# by tenure
predicted <- predictions(m_total_cross,
                         newdata = values_tenure)

predicted %>%
    mutate(estimate = estimate*n_agency, 
         conf.high = conf.high*n_agency, conf.low = conf.low*n_agency) %>% 
ggtenure() +
  labs(title =  "", # "Predicted total letters per year",        subtitle = "(cross-sectional)",
       x = "Years serving in Congress",
       y = "      Predicted letters per year",
       fill = "",
       color = "",
       shape = "") 


# diff in diff 
predicted <- predictions(m_total_did,
                         newdata = values)


# Predictions by Chair and President's Party
predicted %>%
    mutate(estimate = estimate*n_agency, #predicted*n_agency,
         conf.high = conf.high*n_agency, conf.low = conf.low*n_agency) %>% # std.error = std.error*n_agency)) %>%
  ggchair() + 
  labs(title =  "", # "Predicted total letters per year\nDifference in Differences (Within-Legislator)",
       x = "",
       y = "  Predicted letters per year",
       fill = "",
       color = "",
       shape = "") 

# by tenure
predicted2 <- predictions(m_total_did,
                         newdata = values_tenure)

predicted2 %>%
    mutate(estimate = estimate*n_agency, #predicted*n_agency,
         conf.high = conf.high*n_agency, conf.low = conf.low*n_agency) %>%  # std.error = std.error*n_agency) %>%
ggtenure() +
    #geom_line(aes(x = as.numeric(year_in_congress %>% str_sub(1,1) %>% str_replace("N", "1")))) + 
  labs(title =  "", # "Predicted total letters per year\nDifference in Differences (Within-Legislator)",
       x = "Years serving in Congress",
       y = "  Predicted letters per year",
       fill = "",
       color = "",
       shape = "") 
```

### Modeled Effects 

```{r}
#| label: "negbin-m-total-effect"
#| fig-cap: "code/figs/negbin-m-total-effect"
#| layout-ncol: 2
#| fig-height: 3.5
#| fig-width: 3.5
#| fig-subcap: 
#|   - "1"
#|   - "2"
#|   - "3"
#|   - "4"
#| out-width: "100%"
#| fig-show: "hold"

model <- m_total_cross
data = dcounts_total |> filter(year > 2007,  year < 2019)

plot_effect(
  newdata = data |>  mutate(chair = 0),
  effect = "Chair"
  )

plot_effect(
  newdata = data |>  mutate(ranking_minority = 0),
  effect = "Ranking Minority"
  )

plot_effect(
  newdata = data |>  mutate(prestige = 0),
  effect = "Prestige Committee"
  )

plot_effect(
  newdata = data |>  mutate(oversight = 0),
  effect = "Oversight Committee"
  )

plot_effect(
  newdata = data |>  mutate(experience = 0),
  effect = "3+ years in office"
  )

plot_effect(
  newdata = data |>  mutate(majority = 0),
  effect = "Majority"
  )

plot_effect(
  newdata = data |>  mutate(presidents_party = 0),
  effect = "President's party"
  )

plot_effect(
  newdata = data |>  mutate(chair = 0,
                            ranking_minority = 0,
                            # oversight = 0,
                            # prestige = 0,
                            experience = 0),
  effect = "Total capacity"
  )
```


### Modeled Effects - diff in diff

```{r}
#| label: "negbin-m-total-did-effect"
#| fig-cap: "code/figs/negbin-m-total-did-effect"
#| layout-ncol: 2
#| fig-height: 3.5
#| fig-width: 3.5
#| fig-subcap: 
#|   - "1"
#|   - "2"
#|   - "3"
#|   - "4"
#| out-width: "100%"
#| fig-show: "hold"

model <- m_total_did
data = dcounts_total |> filter(year > 2007,  year < 2019)

plot_effect(
  newdata = data |>  mutate(chair = 0),
  effect = "Chair (diff in diff)"
  )

plot_effect(
  newdata = data |>  mutate(ranking_minority = 0),
  effect = "Ranking minority (diff in diff)"
  )

plot_effect(
  newdata = data |>  mutate(prestige = 0),
  effect = "Prestige committee (diff in diff)"
  )

plot_effect(
  newdata = data |>  mutate(oversight = 0),
  effect = "Oversight committee (diff in diff)"
  )

plot_effect(
  newdata = data |>  mutate(experience = 0),
  effect = "3+ years in office (diff in diff)"
  )

plot_effect(
  newdata = data |>  mutate(majority = 0),
  effect = "Majority (diff in diff)"
  )

plot_effect(
  newdata = data |>  mutate(presidents_party = 0),
  effect = "President's party (diff in diff)"
  )

plot_effect(
  newdata = data |>  mutate(chair = 0,
                            ranking_minority = 0,
                            # oversight = 0,
                            # prestige = 0,
                            experience = 0),
  effect = "Total capacity (diff in diff)"
  )
```


---

## Total Letters - House

### Member-level Coefficient Plots - House

- Figures: `code/figs/negbin-m-total-house-[1:4].png`

```{r}
#| label: "negbin-m-total-house"
#| fig-cap: "code/figs/negbin-m-total-house-[1:4].png"
#| layout-ncol: 2
#| fig-height: 4.5
#| fig-subcap: 
#|   - "1"
#|   - "2"
#|   - "3"
#|   - "4"
#| out-width: "100%"
#| fig-show: "hold"

# cross-sectional 
m_total_cross_house <-fenegbin (perYear ~ 
                         chair + ranking_minority + prestige + oversight +  
                    experience + # first + second + third + fourth + fifth + sixth  + 
                    majority + presidents_party | Year_x_Agency,
                    cluster = "Legislator", 
           data = dcounts_total |> filter(chamber=="House"))

if(testing){modelsummary::modelsummary(m_total_cross_house)}

coefplot(m_total_cross_house, horiz = T, drop = "(Intercept)|.theta") 



# Model 2
m_total_did_house <-fenegbin (perYear ~ 
                       chair + ranking_minority + prestige + oversight +  
                    experience + 
                    majority + presidents_party | Year_x_Agency + Legislator_x_Agency, 
                    cluster = "Legislator",
                    # ALT vcov = hetero ~ ssc(cluster.adj = TRUE),
           data = dcounts_total |> filter(chamber=="House"))

if(testing){modelsummary::modelsummary(m_total_did_house)}

coefplot(m_total_did_house, horiz = T, drop = ".theta") 


# 3
m_total_2nd_house <-fenegbin (perYear ~ 
                       chair + ranking_minority + prestige + oversight +  
                    experience + 
                    majority + presidents_party | Year_x_Agency , 
                    cluster = "Legislator", 
           data = dcounts_total |> filter(survive == 1)  |> filter(chamber=="House"))

if(testing){modelsummary::modelsummary(m_total_2nd_house)}
coefplot(m_total_2nd_house, horiz = T, drop = ".theta") 


# # 4
# m_logtotal_did_house <-fenegbin (log(perYear + 1) ~ 
#                           chair + ranking_minority + prestige + oversight +  
#                     experience + 
#                     majority + presidents_party | Year_x_Agency + Legislator_x_Agency, 
#                     cluster = "Legislator", 
#            data = dcounts_total |> filter(chamber=="House"))
# 
# if(testing){modelsummary::modelsummary(m_logtotal_did_house)}
# 
# coefplot(m_logtotal_did_house, horiz = T, drop = ".theta") 


```


### Modeled Effects - House

```{r}
#| label: "negbin-m-total-house-effect"
#| fig-cap: "code/figs/negbin-m-total-house-effect"
#| layout-ncol: 2
#| fig-height: 3.5
#| fig-width: 3.5
#| fig-subcap: 
#|   - "1"
#|   - "2"
#|   - "3"
#|   - "4"
#| out-width: "100%"
#| fig-show: "hold"

model <- m_total_cross_house
data = dcounts_total |> filter(year > 2007,  year < 2019)

plot_effect(
  newdata = data |>  mutate(chair = 0),
  effect = "Chair"
  )

plot_effect(
  newdata = data |>  mutate(ranking_minority = 0),
  effect = "Ranking Minority"
  )

plot_effect(
  newdata = data |>  mutate(prestige = 0),
  effect = "Prestige Committee"
  )

plot_effect(
  newdata = data |>  mutate(oversight = 0),
  effect = "Oversight Committee"
  )

plot_effect(
  newdata = data |>  mutate(experience = 0),
  effect = "3+ years in office"
  )

plot_effect(
  newdata = data |>  mutate(majority = 0),
  effect = "Majority"
  )

plot_effect(
  newdata = data |>  mutate(presidents_party = 0),
  effect = "President's party"
  )

plot_effect(
  newdata = data |>  mutate(chair = 0,
                            ranking_minority = 0,
                            # oversight = 0,
                            # prestige = 0,
                            experience = 0),
  effect = "Total capacity"
  )
```


## Total Letters - Senate

### Member-level Coefficient Plots - Senate

- Figures: `code/figs/negbin-m-total-senate-[1:4].png`

```{r cache=FALSE}
#| label: "negbin-m-total-senate"
#| fig-cap: "code/figs/negbin-m-total-senate-[1:4].png"
#| layout-ncol: 2
#| fig-height: 4.5
#| fig-subcap: 
#|   - "1"
#|   - "2"
#|   - "3"
#|   - "4"
#| out-width: "100%"
#| fig-show: "hold"

# cross-sectional 
m_total_cross_senate <-fenegbin (perYear ~ pop2010m + 
                         chair + ranking_minority + prestige + oversight +  
                    experience + # first + second + third + fourth + fifth + sixth  + 
                    majority + presidents_party | Year_x_Agency,
                    cluster = "Legislator", 
           data = dcounts_total |> filter(chamber=="Senate"))

if(testing){modelsummary::modelsummary(m_total_cross_senate)}

coefplot(m_total_cross_senate, horiz = T, drop = "(Intercept)|.theta") 



# Model 2
m_total_did_senate <-fenegbin (perYear ~ 
                       chair + ranking_minority + prestige + oversight +  
                    experience + 
                    majority + presidents_party | Year_x_Agency + Legislator_x_Agency, 
                    cluster = "Legislator",
                    # ALT vcov = hetero ~ ssc(cluster.adj = TRUE),
           data = dcounts_total |> filter(chamber=="Senate"))

if(testing){modelsummary::modelsummary(m_total_did_senate)}

coefplot(m_total_did_senate, horiz = T, drop = ".theta") 


# 3
m_total_2nd_senate <-fenegbin (perYear ~ pop2010m + 
                       chair + ranking_minority + prestige + oversight +  
                    experience + 
                    majority + presidents_party | Year_x_Agency , 
                    cluster = "Legislator", 
           data = dcounts_total |> filter(survive == 1)  |> filter(chamber=="Senate"))

if(testing){modelsummary::modelsummary(m_total_2nd_senate)}
coefplot(m_total_2nd_senate, horiz = T, drop = ".theta") 


# # 4
# m_logtotal_did_senate <-fenegbin (log(perYear + 1) ~ 
#                           chair + ranking_minority + prestige + oversight +  
#                     experience + 
#                     majority + presidents_party | Year_x_Agency + Legislator_x_Agency, 
#                     cluster = "Legislator", 
#            data = dcounts_total |> filter(chamber=="Senate"))
# 
# if(testing){modelsummary::modelsummary(m_logtotal_did_senate)}
# 
# coefplot(m_logtotal_did_senate, horiz = T, drop = ".theta") 


```

### Modeled Effects - Senate 

negbin-m-total-senate

```{r}
#| label: "negbin-m-total-senate-effect"
#| fig-cap: "code/figs/negbin-m-total-senate-effect"
#| layout-ncol: 2
#| fig-height: 3.5
#| fig-width: 3.5
#| fig-subcap: 
#|   - "1"
#|   - "2"
#|   - "3"
#|   - "4"
#| out-width: "100%"
#| fig-show: "hold"

model <- m_total_cross_senate
data = dcounts_total |> filter(chamber=="Senate") |> filter(year > 2007,  year < 2019)

plot_effect(
  newdata = data |>  mutate(pop2010m = min(dcounts_total$pop2010m) ),
  effect = "State population"
  )

plot_effect(
  newdata = data |>  mutate(chair = 0),
  effect = "Chair"
  )

plot_effect(
  newdata = data |>  mutate(ranking_minority = 0),
  effect = "Ranking minority"
  )

plot_effect(
  newdata = data |>  mutate(prestige = 0),
  effect = "Prestige committee"
  )

plot_effect(
  newdata = data |>  mutate(oversight = 0),
  effect = "Oversight committee"
  )

plot_effect(
  newdata = data |>  mutate(experience = 0),
  effect = "3+ years in office"
  )

plot_effect(
  newdata = data |>  mutate(majority = 0),
  effect = "Majority"
  )

plot_effect(
  newdata = data |>  mutate(presidents_party = 0),
  effect = "President's party"
  )

plot_effect(
  newdata = data |>  mutate(chair = 0,
                            ranking_minority = 0,
                            # oversight = 0,
                            # prestige = 0,
                            experience = 0),
  effect = "Total capacity"
  )
```



\clearpage


## Total Letters - Electoral Competitiveness

- Figures: `code/figs/m-elect-total-[1:4].png`

```{r m-elect-total,  fig.show="hold", out.width="50%", fig.height=4.5, fig.cap= "Total Letters Per Year",fig.subcap= c("Model 1: Cross Sectional","Model 2: Diff in Diff","Model 3: restricted Diff in Diff","Model 4: log Diff in Diff")}

# cross-sectional 
m_elect_total_cross <- fenegbin (perYear ~ 
                         competitive + competitive_primary +
                           chair + ranking_minority + prestige + oversight +  
                    experience + 
                    majority + presidents_party | Year_x_Agency,
                    cluster = "Legislator", 
           data = dcounts_total)

if(testing){modelsummary(m_elect_total_cross, gof_omit = "R.*", coef_omit = coef_omit)}

coefplot(m_elect_total_cross, horiz = T, drop = "(Intercept)") 



# 2
m_elect_total_did <-fenegbin (perYear ~ 
                       competitive + competitive_primary +
                         chair + ranking_minority + prestige + oversight +  oversight +
                    experience + 
                    majority  | Year_x_Agency + Legislator_x_Agency, 
                    cluster = "Legislator",
                    # ALT vcov = hetero ~ ssc(cluster.adj = TRUE),
           data = dcounts_total)

if(testing){modelsummary(m_elect_total_did, gof_omit = "R.*", coef_omit = coef_omit)}

coefplot(m_elect_total_did, horiz = T, drop = ".theta") 


# 3
m_elect_total_2nd_cross <-fenegbin (perYear ~ 
                       competitive + competitive_primary + 
                         chair + ranking_minority + prestige + oversight +  
                    experience + 
                    majority + presidents_party | Year_x_Agency, 
                    cluster = "Legislator", 
           data = dcounts_total %>% filter(survive == 1))

if(testing){modelsummary(m_elect_total_2nd_cross, gof_omit = "R.*", coef_omit = coef_omit)}
coefplot(m_elect_total_2nd_cross, horiz = T, drop = ".theta") 


# 4
m_elect_total_2nd_did <-fenegbin (log(perYear + 1) ~
                          competitive + competitive_primary + 
                            chair + ranking_minority + prestige + oversight +
                    experience +
                    majority + presidents_party | Year_x_Agency + Legislator_x_Agency,
                    cluster = "Legislator",
           data = dcounts_total %>% filter(survive == 1))

if(testing){modelsummary(m_elect_logtotal_did, gof_omit = "R.*", coef_omit = coef_omit)}

coefplot(m_elect_total_2nd_did, horiz = T, drop = ".theta")
```


### Total Letters Table - Electoral 

```{r m-elect-models_total}
models_elect_total <- list(
  "(1)" = m_elect_total_cross,
  "(2)" = m_elect_total_did,
  "(3)" =  m_elect_total_2nd_cross,
 "(4)" = m_elect_total_2nd_did
)

rows <- tibble(
  term = c("Dependent Variable", 
           #"Majority",
           #"President's Party",
           "All Legislators", 
           "Served At Least 2nd Term"),
  `(1)` = c("Count", "X", ""),
  `(2)` =c("Count", "X", ""),
  `(3)` = c("Count","", "X"),
  `(4)` = c("Count", "", "X") 
)

# subset
attr(rows, 'position') <- c(0, 20,21,22,23)

# call coefs
attr(rows, 'position') <- c(0)

options(modelsummary_factory_default = 'kableExtra')


# HTML
modelsummary(models_elect_total, 
             title = "The Effect of Experience and District Competitiveness on Legislator Contacts", 
             notes = list("Robust standard errors in parentheses, clustered by legislator."))

beta_cross <- betas(m_elect_total_cross)
se_cross <- standard_errors(m_elect_total_cross)
beta_did <- betas(m_elect_total_did)
se_did <- standard_errors(m_elect_total_did)
```


### Total Letters Narrative

To address potential confounding in across-legislator comparisons, the estimates from Model 2 (Column 2 of Table `\ref{tab:models_total}`) provide the estimated effects from the difference-in-differences specification in Equation `\ref{e:diff1}`.  Consider first the effect of being in a competitive district. We estimate that a district becoming competitive causes an increase of `r beta_did$competitive`  requests `\textit{per agency}` (95-percent confidence interval [`r beta_did$competitive - se_did$competitive*1.96`, `r beta_did$competitive + se_did$competitive*1.96`]). Across all `r n_agency` agencies, this represents an increase of approximately `r (beta_did$competitive*n_agency) %>% round(0)` additional requests per year, `r (beta_did$competitive / mean(dcounts_total$perYear) ) %>% round(3)*100 ``\%` of the average requests per year in our data. There is a smaller increase for individuals who become ranking members and those who join a Prestige Committee, though the increase is statistically significant for the prestige committee. Becoming a ranking member of a committee causes an increase of `r beta_did$ranking_minority` contacts per agency, while joining a prestige committee causes a `r beta_did$prestige` per agency increase in the number of contacts a member of Congress makes.



### Total Letters Predictions 

- Figures: `code/figs/m-total-predicted-[1:4].png`


```{r m-elect-total-predicted,  fig.show="hold", out.width="50%", fig.cap= "Total",  fig.subcap= c("Model 1: Cross Sectional","Model 1: Cross Sectional", "Model 2: Diff in Diff","Model 2: Diff in Diff")}
predicted <- predictions(m_elect_total_cross,
                         newdata = values)

# Cross-sectional predictions
predicted %>%
    mutate(estimate = estimate*n_agency, #predicted*n_agency,
         conf.high = conf.high*n_agency, conf.low = conf.low*n_agency) %>%  # std.error = std.error*n_agency) %>%
  ggcompetitive() + 
  labs(title = "Predicted Total Letters per Year",        subtitle = "(Cross-Sectional)",
       x = "",
       y = "Predicted Total Letters Per Year",
       fill = "",
       color = "",
       shape = "") 

# by tenure
predicted <- predictions(m_elect_total_cross,
                         newdata = values_tenure)

predicted %>%
    mutate(estimate = estimate*n_agency, #predicted*n_agency,
         conf.high = conf.high*n_agency, conf.low = conf.low*n_agency) %>%  # std.error = std.error*n_agency) %>%
ggtenure() +
  labs(title = "Predicted Total Letters Per Year",        subtitle = "(Cross-Sectional)",
       x = "Years Serving in Congress",
       y = "Predicted Letters Per Year",
       fill = "",
       color = "",
       shape = "") 


# diff in diff 
predicted <- predictions(m_elect_total_did,
                         newdata = values)


# predictions by competitive and presidents' party
predicted %>%
    mutate(estimate = estimate*n_agency, #predicted*n_agency,
         conf.high = conf.high*n_agency, conf.low = conf.low*n_agency) %>% # std.error = std.error*n_agency)) %>%
  ggcompetitive() + 
  labs(title = "Predicted Total Letters per Year\nDifference in Differences (Within-Legislator)",
       x = "",
       y = "Predicted Letters Per Year",
       fill = "",
       color = "",
       shape = "") 

# by tenure
predicted <- predictions(m_elect_total_did,
                         newdata = values_tenure)

predicted %>%
    mutate(estimate = estimate*n_agency, #predicted*n_agency,
         conf.high = conf.high*n_agency, conf.low = conf.low*n_agency) %>%  # std.error = std.error*n_agency) %>%
ggtenure() +
    #geom_line(aes(x = as.numeric(year_in_congress %>% str_sub(1,1)))) + 
  labs(title = "Predicted Total Letters Per Year",
       subtitle = "Difference in Differences (Within-Legislator)",
       x = "Years Serving in Congress",
       y = "Predicted Letters Per Year",
       fill = "",
       color = "",
       shape = "") 
```


### Modeled Effects - electoral - cross sectional 

```{r}
#| label: "negbin-m-elect-total-effect"
#| fig-cap: "code/figs/negbin-m-elect-total-effect"
#| layout-ncol: 2
#| fig-height: 3.5
#| fig-width: 3.5
#| fig-subcap: 
#|   - "1"
#|   - "2"
#|   - "3"
#|   - "4"
#| out-width: "100%"
#| fig-show: "hold"

model <- m_elect_total_cross
data = dcounts_total |> filter(year > 2007,  year < 2019)

plot_effect(
  newdata = data |>  mutate(competitive = 0),
  effect = "Competitive general election"
  )

plot_effect(
  newdata = data |>  mutate(competitive_primary = 0),
  effect = "Competitive primary election"
  )

plot_effect(
  newdata = data |>  mutate(competitive = 0,
                            # oversight = 0,
                            # prestige = 0,
                            competitive_primary = 0),
  effect = "Total electoral competition effect"
  )
```

### Modeled Effects - electoral - diff in diff

```{r}
#| label: "negbin-m-elect-total-did-effect"
#| fig-cap: "code/figs/negbin-m-elect-total-did-effect"
#| layout-ncol: 2
#| fig-height: 3.5
#| fig-width: 3.5
#| fig-subcap: 
#|   - "1"
#|   - "2"
#|   - "3"
#|   - "4"
#| out-width: "100%"
#| fig-show: "hold"

model <- m_elect_total_did
data = dcounts_total #|> filter(year > 2007,  year < 2019)

plot_effect(
  newdata = data |>  mutate(competitive = 0),
  effect = "Competitive general election\n(diff in diff)"
  )

plot_effect(
  newdata = data |>  mutate(competitive_primary = 0),
  effect = "Competitive primary election\n(diff in diff)"
  )

plot_effect(
  newdata = data |>  mutate(competitive = 0,
                            # oversight = 0,
                            # prestige = 0,
                            competitive_primary = 0),
  effect = "Total electoral competition\n(diff in diff)"
  )
```

## Total Letters - Ideology

- Figures: `code/figs/m-ideo-total-[1:4].png`

```{r m-ideo-total,  fig.show="hold", out.width="50%", fig.height=4.5, fig.cap= "Total Letters Per Year",fig.subcap= c("Model 1: Cross Sectional","Model 2: Diff in Diff","Model 3: restricted Diff in Diff","Model 4: log Diff in Diff")}


# cross-sectional 
m_ideo_total_cross <- fenegbin (perYear ~ 
                         chair + ranking_minority + prestige + oversight +  
                    experience + 
                    majority + distance*presidents_party | Year_x_Agency,
                    cluster = "Legislator", 
           data = dcounts_total)

if(testing){modelsummary(m_ideo_total_cross, gof_omit = "R.*", coef_omit = coef_omit)}

coefplot(m_ideo_total_cross, horiz = T, drop = "(Intercept)") 



# 2
m_ideo_total_did <-feglm (perYear ~ 
                        chair + ranking_minority + prestige + oversight + 
                    experience + 
                    majority  + distance*presidents_party | Year_x_Agency + Legislator_x_Agency, 
                    cluster = "Legislator",
                    # ALT vcov = hetero ~ ssc(cluster.adj = TRUE),
           data = dcounts_total)

a <- m_ideo_total_did |> predict()

if(testing){modelsummary(m_ideo_total_did, gof_omit = "R.*", coef_omit = coef_omit)}

coefplot(m_ideo_total_did, horiz = T, drop = ".theta") 


# 3
m_ideo_total_2nd_cross <-fenegbin (perYear ~ 
                        chair + ranking_minority + prestige + oversight +  
                    experience + 
                    majority + distance*presidents_party | Year_x_Agency, 
                    cluster = "Legislator", 
           data = dcounts_total %>% filter(survive == 1))

if(testing){modelsummary(m_ideo_total_2nd_cross, gof_omit = "R.*", coef_omit = coef_omit)}
coefplot(m_ideo_total_2nd_cross, horiz = T, drop = ".theta") 


# # 4
# m_ideo_logtotal_did <-fenegbin (log(perYear + 1) ~ 
#                           distance + chair + ranking_minority + prestige + oversight +  
#                     experience + 
#                       competitive+ 
#                     majority + presidents_party | Year_x_Agency + Legislator_x_Agency, 
#                     cluster = "Legislator", 
#            data = dcounts_total)
# 
# if(testing){modelsummary(m_ideo_logtotal_did, gof_omit = "R.*", coef_omit = coef_omit)}
# 
# coefplot(m_ideo_logtotal_did, horiz = T, drop = ".theta") 
```


### Total Letters Table - Ideology 

```{r m-ideo-models_total}
models_ideo_total <- list(
  "(1)" = m_ideo_total_cross,
  "(2)" = m_ideo_total_did,
  "(3)" =  m_ideo_total_2nd_cross#,
 # "(4)" = m_ideo_logtotal_did
)

rows <- tibble(
  term = c("Dependent Variable", 
           "Majority",
           "President's Party",
           "All Legislators", 
           "Served At Least 2nd Term"),
  `(1)` = c("Count", "X", "X", "X", ""),
  `(2)` =c("Count", "X", "X", "X", ""),
  `(3)` = c("Count", "X","X","", "X")#,
  #`(4)` = c("Log(Count+1)","X","X", "X", "") 
)

rows <- tibble(
  term = c("Dependent Variable", 
           #"Majority",
           #"President's Party",
           "All Legislators", 
           "Served At Least 2nd Term"),
  `(1)` = c("Count", "X", ""),
  `(2)` =c("Count", "X", ""),
  `(3)` = c("Count","", "X")#,
  #`(4)` = c("Log(Count+1)", "X", "") 
)

# subset
attr(rows, 'position') <- c(0, 20,21,22,23)

# call coefs
attr(rows, 'position') <- c(0)

options(modelsummary_factory_default = 'kableExtra')


# HTML
modelsummary(models_ideo_total,
             title = "The Effect of Experience and District Competitiveness on Legislator Contacts", 
             notes = list("Robust standard errors in parentheses, clustered by legislator."))

beta_cross <- betas(m_ideo_total_cross)
se_cross <- standard_errors(m_ideo_total_cross)
```


### Total Letters Narrative - Ideology

TODO 



### Total Letters Predictions - Ideology

- Figures: `code/figs/m-total-predicted-[1:4].png`


```{r m-ideo-total-predicted,  fig.show="hold", out.width="50%", fig.cap= "Total",  fig.subcap= c("Model 1: Cross Sectional","Model 1: Cross Sectional", "Model 2: Diff in Diff","Model 2: Diff in Diff")}
# predicted <- predictions(m_ideo_total_cross,
#                          newdata = values)
# 
# # Cross-sectional predictions
# predicted %>%
#     mutate(estimate = estimate*n_agency, #predicted*n_agency,
#          conf.high = conf.high*n_agency, conf.low = conf.low*n_agency) %>%  # std.error = std.error*n_agency) %>%
#   ggcompetitive() + 
#   labs(title = "Predicted Total Letters per Year",        subtitle = "(Cross-Sectional)",
#        x = "",
#        y = "Predicted Total Letters Per Year",
#        fill = "",
#        color = "",
#        shape = "") 
# 
# # by tenure
# predicted <- predictions(m_ideo_total_cross,
#                          newdata = values_tenure)
# 
# predicted %>%
#     mutate(estimate = estimate*n_agency, #predicted*n_agency,
#          conf.high = conf.high*n_agency, conf.low = conf.low*n_agency) %>%  # std.error = std.error*n_agency) %>%
# ggtenure() +
#   labs(title = "Predicted Total Letters Per Year",        subtitle = "(Cross-Sectional)",
#        x = "Years Serving in Congress",
#        y = "Predicted Letters Per Year",
#        fill = "",
#        color = "",
#        shape = "") 
```



### Modeled Effects - ideology

```{r}
#| label: "negbin-m-ideo-total-effect"
#| fig-cap: "code/figs/negbin-m-ideo-total-effect"
#| layout-ncol: 2
#| fig-height: 3.5
#| fig-width: 3.5
#| fig-subcap: 
#|   - "1"
#|   - "2"
#|   - "3"
#|   - "4"
#| out-width: "100%"
#| fig-show: "hold"

model <- m_ideo_total_cross
data = dcounts_total |> filter(year > 2007,  year < 2019)

plot_effect(
  newdata = data |>  
    mutate(nominate_dim1 = 0) |>
    mutate(distance = abs(nominate_dim1 - agency_ideo)),
    # mutate(distance == 0), 
  effect = "Legislator ideology"
  )

plot_effect(
  newdata = data |>  
    # mutate(distance == 0), 
    mutate(agency_ideo = 0) |>  
    mutate(distance = abs(nominate_dim1 - agency_ideo)),
  effect = "Perceived agency ideology"
  )
```

# Model Results: Per District

## Data

<!--
#TODO deal with chamber switchers ? or maybe we don't need to since everything is calculated grouped at chamber level?
# count(member_data, bioname, icpsr, congress, sort = T) |> filter(n >1)
-->

The main district-level models in the paper focus on estimating the effect of legislator experience by leveraging turnover within districts. We compare the service that a district receives before and after electing a new legislator and in the following years as legislators gain experience in office.


```{r add-crosswalk}

dcounts_district |> 
  count(same_party) |> 
  kablebox()
# 


# dcounts_district |> filter(chamber == "House") |>   select(icpsr, state_dist, year, state_dist_party, lag_p, same_party, new_member)   |> kablebox()

dcounts_district %<>% mutate(same_party = as.numeric(same_party))
```


## Total Letters per District

The main results showing that replacing a more experienced legislator with a new legislator yields a substantial decrease in service to the district are robust to interacting all variables with the `same_party` variable. 
Cross-sectional effects get larger but more uncertain when data are subset to district years after turnover (as required for the `same_party` variable). Within-district effects become more uncertain, likely due to the much smaller number of observations where `same_party` can be observed. 


### Total District-level Coefficient Plots

Figures: `code/figs/negbin-m-district-[1:4].png`

1. cross-sectional 
2. cross-sectional with same-party variable 
3. diff-in-diff
4. diff-in-diff with same party variable

```{r}
#| layout-ncol: 2
#| fig-height: 4.5
#| fig-cap: "code/figs/negbin-m-district-[1:4].png"
#| fig-subcap: 
#|   - "1"
#|   - "2"
#|   - "3"
#|   - "4"
#| out-width: "100%"
#| label: "negbin-m-district"
#| fig-show: "hold"


m_district_cross <- fenegbin(perYear ~
  new_member #+ second + third + fourth + fifth + sixth 
  | Year_x_Agency,
cluster = "District",
data = dcounts_district)

if(testing){modelsummary::modelsummary(m_district_cross)}

coefplot(m_district_cross, horiz = T, drop = "(Intercept)|.theta", sub = "Reference = A member serving >6 years") 


m_district_cross_party <- fenegbin(perYear ~
  new_member*same_party #+ second*same_party + third*same_party + fourth*same_party + fifth*same_party + sixth*same_party 
  | Year_x_Agency,
cluster = "District",
data = dcounts_district)

if(testing){modelsummary::modelsummary(m_district_cross)}

coefplot(m_district_cross_party, horiz = T, drop = "(Intercept)|.theta", sub = "Reference = A member serving >6 years") 


# Diff in diff
m_district_did <- fenegbin(perYear ~
  new_member #+ same_party + second + third + fourth + fifth + sixth | 
  | District + Year_x_Agency,
cluster = "District",
data = dcounts_district )

coefplot(m_district_did, horiz = T, drop = "(Intercept)|.theta", sub = "Reference = A member serving >6 years") 

# Diff in diff
m_district_did_party <- fenegbin(perYear ~
  new_member*same_party #+ second*same_party + third*same_party + fourth*same_party + fifth*same_party + sixth*same_party 
   | District + Year_x_Agency,
cluster = "District",
data = dcounts_district )

coefplot(m_district_did_party, horiz = T, drop = "(Intercept)|.theta", sub = "Reference = A member serving >6 years") 



# Diff in diff
m_district_did_house <- fenegbin(perYear ~
  new_member #+ same_party + second + third + fourth + fifth + sixth 
    | District + Year_x_Agency,
cluster = "District",
data = dcounts_district |> filter(chamber == "House"))


# Diff in diff + party change var 
m_district_did_house_party <- fenegbin(perYear ~
  new_member*same_party #+ second*same_party + third*same_party + fourth*same_party + fifth*same_party + sixth*
 | District + Year_x_Agency,
cluster = "District",
data = dcounts_district |> filter(chamber == "House"))

# Diff in diff
m_district_did_senate <- fenegbin(perYear ~
  new_member #+ same_party + second + third + fourth + fifth + sixth 
    | District + Year_x_Agency,
cluster = "District",
data = dcounts_district |> filter(chamber == "Senate"))


# Diff in diff + party change var 
m_district_did_senate_party <- fenegbin(perYear ~
  new_member*same_party # + second*same_party + third*same_party + fourth*same_party + fifth*same_party + sixth*same_party 
    | District + Year_x_Agency,
cluster = "District",
data = dcounts_district |> filter(chamber == "Senate"))

```

### Total Per District Tables

- Models: `models/models_district_negbin.Rdata` 


```{r models_district}
models_district <- list(
  "(1)" = m_district_cross,
  "(2)" = m_district_did,
  "(3)" = m_district_did_house,
  "(4)" = m_district_did_senate
)


rows <- tibble(
  term = c("Dependent variable", 
           "All districts",
           "House only",
           "Senate only"),
  `(1)` = c("Per year", 
            "X", 
            "", 
            ""),
  `(2)` =c("Per year", 
           "X", 
            "", 
            ""),
    `(3)` = c("Per year", 
            "", 
            "X", 
            ""),
  `(4)` =c("Per year", 
           #"X", 
           "", 
            "", 
            "X")
)



# Check marks for controls 
attr(rows, 'position') <- c(0)



modelsummary(models_district)
```


## Same party
models_district_party

```{r models_district_party}
models_district_party <- list(
  "(1)" = m_district_cross_party,
  "(2)" = m_district_did_party,
  "(3)" = m_district_did_house_party,
  "(4)" = m_district_did_senate_party
)


rows <- tibble(
  term = c("Dependent variable", 
           "All districts",
           "House only",
           "Senate only"),
  `(1)` = c("Per year", 
            "X", 
            "", 
            ""),
  `(2)` =c("Per year", 
           "X", 
            "", 
            ""),
    `(3)` = c("Per year", 
            "", 
            "X", 
            ""),
  `(4)` =c("Per year", 
           #"X", 
           "", 
            "", 
            "X")
)



# Check marks for controls 
attr(rows, 'position') <- c(0)



modelsummary(models_district_party)
```


### Total Per District Predictions (House only)

- Figures: `code/figs/negbin-m-district-predicted-house-[1:2].png`

```{r}
#| layout-ncol: 2
#| fig-height: 3
#| fig-cap: "code/figs/negbin-m-district-predicted-house-[1:2].png"
#| fig-subcap: 
#|   - "1"
#|   - "2"
#|   - "3"
#|   - "4"
#| out-width: "100%"
#| label: "negbin-m-district-predicted-house"
#| fig-show: "hold"


# Values for HOUSE seats 
values <- tidyr::expand(dcounts_district,
                        new_member = new_member,
                        oversight = 0,
                        distance = dcounts_total$distance |> mean(na.rm = T),
                        second = second,
                        third = third,
                        fourth = fourth,
                        fifth = fifth, 
                        sixth = sixth,
                        Year = "2017",
                        District = "alabama_1_1",
                        Year_x_Agency = modal$Year_x_Agency[n],
                        same_party = same_party
                   ) %>% 
  drop_na(same_party)

# diff in diff plot

predicted <- predictions(m_district_did_house,
                         newdata = values) 


predicted %>%
ggdistrict() +
        geom_line(aes(x = as.numeric(year_in_congress %>% str_replace(" N", "1") %>% str_sub(1,1) ))) + 
  labs(title = "Letters per House district",        subtitle = "(difference-in-differences)",
       x = "Years serving in Congress",
       y = "    Predicted letters per year\nper House district\n(difference-in-differneces)",
       fill = "",
       color = "",
       shape = "")


```





### Total Per District Predictions (Senate only)

- Figures: `code/figs/negbin-m-district-predicted-senate-[1:2].png`

```{r}
#| layout-ncol: 2
#| fig-height: 3
#| fig-cap: "code/figs/negbin-m-district-predicted-senate-[1:2].png"
#| fig-subcap: 
#|   - "1"
#|   - "2"
#|   - "3"
#|   - "4"
#| out-width: "100%"
#| label: "negbin-m-district-predicted-senate"
#| fig-show: "hold"


# Values for Senate seats 
values <- tidyr::expand(dcounts_district,
                        new_member = new_member,
                        oversight = 0,
                        distance = dcounts_total$distance |> mean(na.rm = T),
                        second = second,
                        third = third,
                        fourth = fourth,
                        fifth = fifth, 
                        sixth = sixth,
                        Year = "2017",
                        Year_x_Agency = modal$Year_x_Agency[n],
                        District = "alabama_0",
                        same_party = same_party
                   ) %>% 
  drop_na(same_party)

# diff in diff plot

predicted <- predictions(m_district_did_senate,
                         newdata = values) 


predicted %>%
ggdistrict() +
        geom_line(aes(x = as.numeric(year_in_congress %>% str_replace(" N", "1") %>% str_sub(1,1) ))) + 
  labs(title = "Letters per senator",        subtitle = "(difference-in-differences)",
       x = "Years serving in Congress",
       y = "   Predicted letters per year\nper Senator\n(difference-in-differneces)",
       fill = "",
       color = "",
       shape = "")
```



### Modeled Effects - district

```{r}
#| label: "negbin-m-distirct-total-effect"
#| fig-cap: "code/figs/negbin-m-district-total-effect"
#| layout-ncol: 2
#| fig-height: 3.5
#| fig-width: 3.5
#| fig-subcap: 
#|   - "1"
#|   - "2"
#|   - "3"
#|   - "4"
#| out-width: "100%"
#| fig-show: "hold"

model <-m_district_cross_party
data = dcounts_district |> filter(year > 2007,  year < 2019)

plot_effect(
  newdata = data |>  
    mutate(same_party = 0),
  effect = "Same party"
  )


model <-m_district_did_party
data = dcounts_district |> filter(year > 2007,  year < 2019)

plot_effect(
  newdata = data |>  
    mutate(same_party = 0),
  effect = "Same party (diff-in-diff)"
  )
```

\clearpage

# Model Results:  Spillover Effects Robustness Check

This is a robustness check for an observable implication of demand-driven behavior. If variation in constituent demand drives variation in legislator behavior (specifically a preference for more senior members), then we should observe spillover effects on the rest of a delegation when an experienced member is replaced with a new member. That is, if people demand more from experienced members, people should redirect demand to the next most experienced member who represents them.

```{r spillover-data}

# new IVs: new_senator, new_proportion, new_one

dcounts_spillover <- dcounts_district %>% 
  # FIRST, identify districts with new members 
  group_by(state, Year) %>% 
  # size of the delegation 
  add_count(name = "n_delegation") %>% 
  mutate(
    # new IVs:
    new_senator = ifelse(chamber == "Senate" & new_member == 1, 1, NA), 
    new_proportion = sum(new_member)/n_delegation, 
    new_one = ifelse(new_member == 1, 1, NA)
  ) %>% 
  fill(new_senator, .direction = "updown") %>% 
  fill(new_one, .direction = "updown") %>% 
  mutate(new_senator =   replace_na(new_senator, 0),
         new_one = replace_na(new_one, 0) 
  ) %>% 
  group_by(state, Year, chamber) %>% 
  arrange(year, state) 

  # THEN WE DROP ALL OF THE NEW MEMBERS 
dcounts_spillover %<>%   filter(new_member == 0)  


# # inspect data 
# dcounts_spillover |> select(Year, state, chamber, new_member, new_one, new_senator, new_proportion, perYear) |> ungroup() |>
#   #filter(new_senator ==1) |>  
#   #count(new_senator, new_member) |> 
#   kablebox_long()
#     

```


<!-- NOT WORTH PLOTTING 
### Spillover Coefficient Plots

Figures: `code/figs/negbin-m-spillover-[1:3].png`

1. diff-in-diff, at least one **new Senator** in the delegation effect
2. diff-in-diff, **proportion** of new legislators in the delegation effect **on Senators**
3. diff-in-diff, at least one **new legislator** in the delegation effect **on Senators**
--> 

### Spillover Effect: Total

```{r}
#| layout-ncol: 2
#| fig-height: 4.5
#| fig-cap: "code/figs/negbin-m-spillover-[1:3].png"
#| fig-subcap: 
#|   - "1"
#|   - "2"
#|   - "3"
#| out-width: "100%"
#| label: "negbin-m-spillover"
#| fig-show: "hold"

m_spillover <- fenegbin(perYear ~
  new_senator  | Year_x_Agency + District,
cluster = "District",
data = dcounts_spillover)

# coefplot(m_spillover, horiz = T, drop = "(Intercept)|.theta", sub = "") 

m_spillover_proportion <- fenegbin(perYear ~
  new_proportion  | Year_x_Agency + District,
cluster = "District",
data = dcounts_spillover |> filter(chamber == "Senate"))

# coefplot(m_spillover_proportion, horiz = T, drop = "(Intercept)|.theta", sub = "") 

m_spillover_new_one <- fenegbin(perYear ~
  new_one  | Year_x_Agency + District,
cluster = "District",
data = dcounts_spillover |> filter(chamber == "Senate"))

# coefplot(m_spillover_new_one, horiz = T, drop = "(Intercept)|.theta", sub = "") 

```


- Models: `models/models_spillover_negbin.Rdata`

```{r models_spillover}
models_spillover <- list(
  "(1)" = m_spillover,
  "(2)" = m_spillover_proportion,
  "(3)" = m_spillover_new_one
)


rows <- tibble(
  term = c("Dependent variable", 
           "All districts",
           "Senate only"),
  `(1)` = c("Per year", 
            "X", 
            ""),
  `(2)` =c("Per year", 
            "", 
           "X"),
    `(3)` = c("Per year", 
            "", 
            "X")
)



# Check marks for controls 
attr(rows, 'position') <- c(0)


modelsummary(models_spillover ) 

save(models_spillover, rows, cm, gm,  # beta_cross, beta_did, se_cross, se_did,
     file = here::here("models", "models_spillover_negbin.Rdata"))
```

# Inequality 

```{r}

percentiles <- dcounts_total %>% 
  dplyr::group_by(member_state, chamber) %>% 
  dplyr::summarise(mean = mean(n)) %>% 
  dplyr::ungroup() %>% 
  dplyr::group_by(chamber) %>% 
  dplyr::mutate(Percentile = dplyr::ntile(mean, 100),
         rank = dplyr::dense_rank(-mean)) %>% 
  dplyr::arrange(-Percentile) %>% 
  dplyr::select(member_state, Percentile, mean, chamber, rank) %>% 
  dplyr::distinct() 


avg_effect_house <- m_total_cross_house |> # m_total_did_house |>
  avg_comparisons(
    variables = c("chair")) 

avg_effect_senate <- m_total_cross_senate |> # m_total_did_senate |>
  avg_comparisons(
    variables = c("chair")) 

percentiles_chair <- member_data |>
  ungroup() |> 
  filter(congress == 116) |>
  select(chamber, chair) |> 
  mutate(
    chair = ifelse(chamber=="Senate", # if senate 
                   chair*avg_effect_senate$estimate*n_agency, #senate chair effect
                   chair*avg_effect_house$estimate*n_agency # otherwise, house chair effect 
                   )
  ) |> 
  dplyr::group_by(chamber)  |> 
  dplyr::mutate(Percentile = dplyr::ntile(chair, 100) ) |> 
  dplyr::arrange(-Percentile)  |> 
  dplyr::distinct(Percentile, chamber, chair) 

percentiles_chair

percentiles %<>% left_join(percentiles_chair) %>% 
# hacky fix 
  group_by(member_state) %>% 
  #slice_head(n = 1) %>% 
  ungroup()

tibble(chair = c(0,1))

```


```{r}
#| label: percentiles-chamber-chair
#| fig-height: 3.4
#| fig-width: 3
#| cache: false
#| 
percentiles %>% 
    filter(chamber == "Senate") %>% 
  mutate(Chair = ifelse(chair > 0, "Chair", "") ) %>%
    ggplot() + 
  # observed 
    geom_col(aes(x = Percentile, y = mean), 
             color = "grey", 
             width = .000001,
             fill = "black",
             position = "dodge") + 
  geom_point(aes(x = Percentile, 
                 y = mean), 
             color = "light blue") + 
    # geom_text(aes(x = Percentile, 
    #             y = mean, 
    #             label = ifelse(rank <24 | Percentile < 50,
    #                            member_state, ""
    #                            )
    #             ), 
    #         check_overlap = T, 
    #               size = 3,
    #               hjust = "inward") + 
    # estimated chair effect 
      geom_col(aes(x = Percentile, y = chair, fill = Chair), 
             #width = 1,
                          alpha =.5,
             position = "dodge") + 
      geom_point(aes(x = Percentile, y = chair, color = Chair) ) + 
  geom_text(aes(x = Percentile, 
                y = chair, 
                label = ifelse(Percentile ==100,
                               paste("+", round(chair), "requests"), 
                               ""
                               )
                ), 
            check_overlap = T, 
                  size = 3,
            vjust = -1,
                  hjust = "inward") + 
  theme_minimal() + 
  scale_color_viridis_d(direction = -1) + 
  labs(title = "Observed vs. Explained (Senate)",
       x = "Percentile in the Senate",
       y = "Average requests per year",
       color = "Avg. Effect",
       fill = "Avg. Effect") 


# HOUSE 
percentiles %>% 
  filter(chamber == "House") %>% 
  mutate(Chair = ifelse(chair > 0, "Chair", "") ) %>%
    ggplot() + 
  # observed 
    geom_col(aes(x = Percentile, y = mean), 
             color = "grey", 
             width = .000001,
             fill = "black",
             position = "dodge") + 

  geom_point(aes(x = Percentile, 
                 y = mean), 
             color = "light blue") + 
    # geom_text(aes(x = Percentile, 
    #             y = mean, 
    #             label = ifelse(rank <24 | Percentile < 50,
    #                            member_state, ""
    #                            )
    #             ), 
    #         check_overlap = T, 
    #               size = 3,
    #               hjust = "inward") + 
    # estimated chair effect 
      geom_col(aes(x = Percentile, y = chair, fill = Chair), 
             #width = 1,
             alpha =.1,
             position = "dodge") + 
      geom_point(aes(x = Percentile, y = chair, color = Chair) ) + 
  geom_text(aes(x = Percentile, 
                y = chair, 
                label = ifelse(Percentile ==100,
                               paste("+", round(chair), "requests"), 
                               ""
                               )
                ), 
            check_overlap = T, 
                  size = 3,
            vjust = -1,
                  hjust = "inward") + 
  theme_minimal() + 
  scale_color_viridis_d(direction = -1) + 
  labs(title = "Observed vs. Explained (House)",
       x = "Percentile in the House",
       y = "Average requests per year",
       color = "Avg. Effect",
       fill = "Avg. Effect") 

```






# Paper models 

## Table 1: Overall + House and Senate

"models_total.Rdata"

```{r paper-models, cache=FALSE}
models_total <- list(
  "(1)" = m_total_cross,
  "(2)" = m_total_did,
  "(3)" =  m_total_cross_house,
  "(4)" = m_total_did_house,
   "(5)" =  m_total_cross_senate,
  "(6)" = m_total_did_senate
)

rows <- tibble(
  term = c("Dependent variable", 
           "All legislators", 
           "Only House",
           "Only Senate"),
  `(1)` = c("Count", "X", "", ""),
  `(2)` =c("Count", "X", "", ""),
  `(3)` = c("Count","", "X", ""),
    `(4)` = c("Count", "", "X", ""),
  `(5)` =c("Count", "","","X"),
  `(6)` = c("Count","","", "X")
  )

attr(rows, 'position') <- c(0)

modelsummary(models_total) 

beta_did <- betas(m_total_did)
se_did <- standard_errors(m_total_did)
beta_cross <- betas(m_total_cross)
se_cross <- standard_errors(m_total_cross)

save(models_total, rows, cm, gm,   beta_cross, beta_did, se_cross, se_did,
     file = here::here("models", "models_total.Rdata"))
```

## Table 2: District + Same Party 

"models_district.Rdata"

```{r}
models_district <- list(
  "(1)" = m_district_cross,
  "(2)" = m_district_did,
  "(3)" =  m_district_cross_party,
  "(4)" = m_district_did_party
)

rows <- tibble(
  term = c("Dependent variable"),
  `(1)` = c("Count"),
  `(2)` =c("Count"),
  `(3)` = c("Count"),
  `(4)` =c("Count")
  )

attr(rows, 'position') <- c(0)

modelsummary(models_district)

beta_did <- betas(m_district_did)
se_did <- standard_errors(m_district_did)
beta_cross <- betas(m_district_cross)
se_cross <- standard_errors(m_district_cross)

save(models_district, rows, cm, gm,   beta_cross, beta_did, se_cross, se_did,
     file = here::here("models", "models_district.Rdata"))
```

## Table 3: Electoral motivations 

"models_elect_total.Rdata"

```{r}
models_elect_total <- list(
  "(1)" = m_elect_total_cross,
  "(2)" = m_elect_total_did,
   "(3)" =  m_elect_total_2nd_cross,
   "(4)" = m_elect_total_2nd_did
  #  "(3)" =  m_elect_total_cross_senate,
  # "(4)" = m_elect_total_did_senate
)

rows <- tibble(
  term = c("Dependent variable", "Served At Least 2nd Term"),
  `(1)` = c("Count", ""),
  `(2)` =c("Count", ""),
  `(3)` = c("Count","X"),    
  `(4)` = c("Count", "X")
  # `(5)` =c("Count", "","","X"),
  # `(6)` = c("Count","","", "X")
  )


attr(rows, 'position') <- c(0)


# HTML
modelsummary(models_elect_total,
             notes = list("Robust standard errors in parentheses, clustered by legislator.") ) 

beta_cross <- betas(m_elect_total_cross)
se_cross <- standard_errors(m_total_cross)
beta_did <- betas(m_elect_total_did)
se_did <- standard_errors(m_total_did)


save(models_elect_total, rows, cm, gm,  beta_cross, beta_did, se_cross, se_did,
     file = here::here("models", "models_elect_total.Rdata"))
```


## Table 4: Ideological motivations 

 "models_ideo_total.Rdata"

```{r}
models_ideo_total <- list(
  "(1)" = m_ideo_total_cross,
  "(2)" = m_ideo_total_did
)

rows <- tibble(
  term = c("Dependent variable"),
  `(1)` = c("Count"),
`(2)` = c("Count"))

attr(rows, 'position') <- c(0)

modelsummary(models_ideo_total) 

beta_cross <- betas(m_ideo_total_cross)
se_cross <- standard_errors(m_ideo_total_cross)

save(models_ideo_total, rows, cm, gm,   beta_cross, se_cross,
     file = here::here("models", "models_ideo_total.Rdata"))
```


