# Type = `r type`

Required Packages: 
  
- `tidyverse` and `magrittr`, for data wrangling
- `scales` for plot scales 
- `ggrepel` for plot labels
- `here` for file paths 
- `knitr` for document formatting 
- `tinytable` for table formatting 
- `modelsummary` for regression tables 
- `marginaleffects` for predictions 
- `fixest` --- a statistical package for fixed effects estimation 
- `ineq` to calculate GINI coefficients

```{r functions, cache=FALSE}
here::here("code", "qmd_global_options.R") |> source() 

# plotting functions 
here::here("code", "ggcompetitive.R") |> source() 
here::here("code", "ggchair.R") |> source() 
here::here("code", "ggtenure.R") |> source() 
here::here("code", "ggdistrict.R") |> source() 
here::here("code", "plot_effect.R") |> source() 

# coef map
here::here("code", "cm.R") |> source() 
here::here("code", "modelsummary_formatting.R") |> source()
```

```{r global.options, message=FALSE,warning=FALSE, purl=FALSE, cache=FALSE}
# load r packages and qmd render defaults 
here::here("code", "qmd_global_options.R") |> source() 
testing = F

# directory for figures from this analysis
dir.create(here::here("figs", type))
dir.create(here::here("models", type))
dir.create(here::here("tables", type))

knitr::opts_chunk$set(
  fig.path = paste0("figs/", type, "/")
  )
```

- Figures at `r paste0("figs/", type, "/")`
- Tables at `r paste0("tables/", type, "/")`
- Models at `r paste0("models/", type, "/")`
- Data at `r paste0("data/", type, "/")`

# Data

```{r data, cache=FALSE}
# note these dcounts already have member_data merged in 
load(here::here("data", type, "dcounts.rds")) 
load(here::here("data", type, "dcounts_district.rds"))
load(here::here("data", type, "means.Rdata"))
load(here::here("data", "member_data.Rdata"))

# to confirming that all of the type count data are he same
dim(dcounts)
dcounts |> count(agency)
```

```{r transformations}
data_member <- dcounts |> mutate(type = type)
data_district <- dcounts_district |> mutate(type = type)

rename_vars <- function(data){
  data <- data |> 
  mutate(same_party = as.numeric(same_party),
         # old census variable 
         pop2010m = pop2010/1000000,
         # from new census data 
         population_m = population_total/1000000,
         # note I am transforming these without making "_m" versions 
         workers_federal=workers_federal/1000000 ,
    workers_private_sector=workers_private_sector/1000000 ,
    workers_self_employed=workers_self_employed/1000000 ,
    workers_nonprofit=workers_nonprofit/1000000 ,
    workers_government=workers_government/1000000 ,
    education_bachelor_or_higher=education_bachelor_or_higher/1000000,
    public_assistance_or_snap_households=public_assistance_or_snap_households/1000000,
    # $ 
         PACamount_nonenergy_m = PACamount_m - PACamount_energy_m,
         Legislator = icpsr,
         District = state_dist,
         Year = year,
         first_two = first + second, 
         experience = ifelse(first_two == 1, 0, 1),
         distance = abs(nominate_dim1 - agency_ideo),
    # fixed effects 
    icpsr_agency = paste(agency, icpsr, sep='_'),
    agency_year = paste(agency, year, sep='_'),
    Year_x_Agency = agency_year,
    Legislator_x_Agency = icpsr_agency)
  
  return(data)
}

data_member <- rename_vars(data_member) 
data_district <- rename_vars(data_district)

######## DON'T MODFIY DATA BELOW THIS LINE 

# INSPECT NA COUNT
data_member |>
  group_by(chamber) |> 
  summarise(
    across(where(is.numeric), ~ mean(is.na(.x))),
    .groups = "drop"
  ) |>
  pivot_longer(
    cols = -chamber,
    names_to = "variable",
    values_to = "missing"
  ) |> 
  filter(missing != 1) |> 
  arrange(desc(missing)) |> 
kablebox_long()

# IN VOTEVIEW BUT MISSING FROM LES DATA
# (OFTEN FOR GOOD REASONS - OFTEN BECAUSE THEY SERVED ONLY A PARTIAL TERM), should we drop them too? 
# https://github.com/judgelord/correspondence/issues/248
# They already auto-dropped from most models
data_member |> filter(is.na(lesclassic), congress < 119) |> distinct(congress, chamber, icpsr, bioname, votepct, state_leg, lesclassic) |> kable()

if(F){ # INSPECT CENSUS EMPLOYMENT DATA - DO THEY ADD UP TO 1? WHAT IS THE REMAINDER?
data_member |> group_by(year, icpsr, chamber, agency) |>  mutate(sum = sum( percent_workers_nonprofit, percent_workers_self_employed, percent_workers_private_sector, percent_workers_government, na.rm = T) |> round(1)) |> ungroup() |> count(sum) |> arrange(sum) |> kablebox(
)

data_member |> group_by(year, icpsr, chamber) |>  mutate(sum = sum( percent_workers_nonprofit, percent_workers_self_employed, percent_workers_private_sector, percent_workers_government, na.rm = T) ) |> ungroup() |> filter(sum == 0)
} 


```

# Top member-agency-year counts 


```{r leaderboard}
data_member |> 
  arrange(-perYear) |> 
  kablebox()


data_member |> 
  filter(agency != "DHS_USCIS") |> 
  arrange(-perYear) |> 
  kablebox()

data_member |> 
  filter(agency != "DHHS_CMS") |> 
    filter(agency != "DHS_USCIS") |> 
  arrange(-perYear) |> 
  kablebox()
```

```{r}
#| label: "percentile"
#| fig-cap: "figs/[TYPE]/percentile-[1:2].png"
#| layout-ncol: 2
#| fig-height: 3.5
#| fig-width: 3.5
#| fig-subcap: 
#|   - "1"
#|   - "2"
#| out-width: "100%"
#| fig-show: "hold"

here::here("code", "percentile_plot.R") |> source()

plot_data(d = data_member |> filter(chamber == "Senate"))
plot_data(d = data_member |> filter(chamber == "House"))
```


### Gini coefficients 

```{r gini}
gini <- data_member |> 
  ungroup() |> 
  group_by(year, icpsr) |> 
  summarize(perYear = sum(perYear)) |> 
  ungroup() |> 
group_by(year) |> 
  summarise(gini = round(ineq::Gini(perYear),2)) |>
  arrange(- year) |> 
  filter(year > 2006) 

gini|> 
  kablebox()

gini |> 
  ggplot() +
  aes( x = year, y = gini) + 
  geom_point() + 
  geom_smooth(method = "lm")

gini_min <- min(gini$gini)
gini_max <- max(gini$gini)


gini2 <- data_member |> 
  ungroup() |> 
  group_by(year, chamber, icpsr) |> 
  summarize(perYear = sum(perYear)) |> 
  ungroup() |> 
group_by(year, chamber) |> 
  summarise(gini = round(ineq::Gini(perYear),2)) |>
  arrange(- year) |> 
  filter(year > 2006) 

gini2|> 
  kablebox()

gini2 |> 
  ggplot() +
  aes( x = year,
       y = gini, 
       color = chamber) + 
  geom_point() 
  #geom_smooth(method = "lm")
  

gini %<>% filter(year > 2017)

min(gini$gini)
max(gini$gini)
```




In 2023, Colombia had the highest income inequality Gini coefficient at .54. 

https://ourworldindata.org/what-is-the-gini-coefficient

Top 10 Gini Coefficients in 2023

1. Colombia	0.54
1. Brazil	0.52	
1. Zambia	0.51
1. Angola	0.51				
1. Mozambique	0.50	
1. Zimbabwe	0.50
1. Kosovo	0.49
1. Panama	0.49
1. Honduras	0.47	
1. Costa Rica	0.47

<!--(The Gini coefficient for House campaign spending in 2016 was .29).  --> 



# Correlations 


## oversight (reporting) committee 


```{r}
#| label: cor-oversight

d <- data_member


cor.test(d$perYear, d$oversight)
cor.test(log(d$perYear + 1), d$oversight)
```

## LES correlation 

```{r}
#| label: les

d1 <- group_by(d, member_state, icpsr, year, lesclassic) %>% 
  summarise(
    perYear = sum(perYear)) %>% 
  ungroup()

d1 %<>% 
  group_by(year) %>%
  mutate( corr_decile = ntile(perYear, 10),
          les_decile = ntile(lesclassic, 10)
          ) %>% 
  ungroup()

# LES OF 0 
# d1 |> filter(lesclassic == 0)
```

```{r}
#| label: cor-les-decile 
#| fig-cap: "figs/[TYPE]/cor-les-decile.png"
#| layout-ncol: 2
#| fig-height: 4.5

d1  %>% 
    filter(year >2007, year < 2018) %>% 
  count(les_decile, corr_decile) %>% 
  ggplot() + 
  aes(x = les_decile, 
      y = corr_decile,
      fill = n) + 
  geom_tile(color = "white",
            lwd = 1.5,
            linetype = 1) +
  coord_fixed() + 
  scale_fill_viridis_c() +
  scale_y_continuous( breaks = seq.int(1,10,1)  ) + 
    scale_x_continuous( breaks = seq.int(1,10,1) ) + 
  labs(x = "Legislative Effectiveness Score Decile",
       y = "Interbranch Representation Decile") + 
  theme(panel.grid = element_blank()) 
```


```{r}
#| label: cor-les
#| fig-cap: "figs/[TYPE]/cor-les-[1:4].png"
#| layout-ncol: 2
#| fig-height: 4.5
#| fig-subcap: 
#|   - "1"
#|   - "2"
#|   - "3"
#|   - "4"
#| out-width: "100%"
#| fig-show: "hold"

# per year  
d1 |>
  filter(year >2007, year < 2018) |>
  ggplot() + 
  aes(x = lesclassic, 
      y = perYear,
            color = as.factor(year),
      label = member_state) + 
  geom_point(alpha = .2) + 
  geom_smooth(method = "lm", color = "black") +
  geom_text(check_overlap = T, hjust = "inward", vjust = "inward") + 
  scale_color_viridis_d(direction = -1, option = "E") + 
  labs(color = "",x = "Legislative Effectiveness Score",
       y = "Interbranch Representation (logged)") 

# per year logged 
d1 |>
  filter(year >2007, year < 2018) |>
  ggplot() + 
  aes(x = lesclassic, 
      y = log(perYear),
            color = as.factor(year),
      label = member_state) + 
  geom_point(alpha = .2) + 
  geom_smooth(method = "lm", color = "black") +
  geom_text(check_overlap = T, hjust = "inward", vjust = "inward") + 
  scale_color_viridis_d(direction = -1, option = "E") + 
  labs(color = "",
       x = "Legislative Effectiveness Score",
       y = "Interbranch Representation (logged)") 

# average 
d1 |>
  filter(year >2007, year < 2018) |>
  group_by(member_state) |> 
  summarise(lesclassic = mean(lesclassic),
         perYear = mean(perYear)) |> 
  ggplot() + 
  aes(x = lesclassic, 
      y = perYear,
      label = member_state) + 
  geom_point(alpha = .2) + 
  geom_smooth(method = "lm") +
  geom_text(check_overlap = T, hjust = "inward", vjust = "inward") + 
  scale_color_viridis_c(direction = -1, option = "E") + 
  labs(x = "Average Legislative Effectiveness Score",
       y = "Average Interbranch Representation") 

# average logged
d1 |>
  filter(year >2007, year < 2018) |>
  group_by(member_state) |> 
  summarise(lesclassic = mean(lesclassic),
         perYear = mean(perYear)) |> 
  ggplot() + 
  aes(x = lesclassic, 
      y = log(perYear),
      label = member_state) + 
  geom_point(alpha = .2) + 
  geom_smooth(method = "lm", color = "black") +
  geom_text(check_overlap = T, hjust = "inward", vjust = "inward") + 
  scale_color_viridis_d(direction = -1, option = "E") + 
  labs(color = "",
       x = "Average Legislative Effectiveness Score",
       y = "Average Interbranch Representation (logged)") 
```


```{r les-correlation}
cor.test(d1$perYear, d1$lesclassic)
cor.test(log(d1$perYear + 1), d1$lesclassic)
```



## PAC correlation 

```{r}
#| label: pac

d1 <- group_by(d, member_state, icpsr, year, PACamount_m) %>% 
  summarise(
    perYear = sum(perYear)) %>% 
  ungroup()

d1 %<>% 
  group_by(year) %>%
  mutate( corr_decile = ntile(perYear, 10),
          pac_decile = ntile(PACamount_m, 10)
          ) %>% 
  ungroup()
```

```{r}
#| label: cor-pac-decile 
#| fig-cap: "figs/[TYPE]/cor-pac-decile.png"
#| layout-ncol: 2
#| fig-height: 4.5

d1  %>% 
    filter(year >2007, year < 2018) %>% 
  count(pac_decile, corr_decile) %>% 
  ggplot() + 
  aes(x = pac_decile, 
      y = corr_decile,
      fill = n) + 
  geom_tile(color = "white",
            lwd = 1.5,
            linetype = 1) +
  coord_fixed() + 
  scale_fill_viridis_c() +
  scale_y_continuous( breaks = seq.int(1,10,1)  ) + 
    scale_x_continuous( breaks = seq.int(1,10,1) ) + 
  labs(x = "Corporate Political Action Committee $ Decile",
       y = "Interbranch Representation Decile") + 
  theme(panel.grid = element_blank())
```


```{r}
#| label: cor-pac
#| fig-cap: "figs/[TYPE]/cor-pac-[1:4].png"
#| layout-ncol: 2
#| fig-height: 4.5
#| fig-subcap: 
#|   - "1"
#|   - "2"
#|   - "3"
#|   - "4"
#| out-width: "100%"
#| fig-show: "hold"

# per year  
d1 |>
  filter(year >2007, year < 2018) |>
  ggplot() + 
  aes(x = PACamount_m, 
      y = perYear,
            color = as.factor(year),
      label = member_state) + 
  geom_point(alpha = .2) + 
  geom_smooth(method = "lm", color = "black") +
  geom_text(check_overlap = T, hjust = "inward", vjust = "inward") + 
  scale_color_viridis_d(direction = -1, option = "E") + 
  labs(color = "",
       x = "Corporate Political Action Committee $ (Millions)",
       y = "Interbranch Representation (logged)") 

# per year logged 
d1 |>
  filter(year >2007, year < 2018) |>
  ungroup() |> 
  ggplot() + 
  aes(x = PACamount_m, 
      y = log(perYear),
      color = as.factor(year),
      label = member_state) + 
  geom_point(alpha = .2) + 
  geom_smooth(method = "lm", color = "black") +
  geom_text(check_overlap = T, hjust = "inward", vjust = "inward") + 
  scale_color_viridis_d(direction = -1, option = "E") + 
  labs(color = "",
       x = "Corporate Political Action Committee $ (Millions)",
       y = "Interbranch Representation (logged)") 

# average 
d1 |>
  filter(year >2007, year < 2018) |>
  group_by(member_state) |> 
  summarise(PACamount_m = mean(PACamount_m),
         perYear = mean(perYear)) |> 
  ggplot() + 
  aes(x = PACamount_m, 
      y = perYear,
      label = member_state) + 
  geom_point(alpha = .2) + 
  geom_smooth(method = "lm", color = "black") +
  geom_text(check_overlap = T, hjust = "inward", vjust = "inward") + 
  scale_color_viridis_d(direction = -1, option = "E") + 
  labs(color = "",
       x = "Average Corporate Political Action Committee $ (Millions)",
       y = "Average Interbranch Representation") 

# average logged
d1 |>
  filter(year >2007, year < 2018) |>
  group_by(member_state) |> 
  summarise(PACamount_m = mean(PACamount_m),
         perYear = mean(perYear)) |> 
  ggplot() + 
  aes(x = PACamount_m, 
      y = log(perYear),
      label = member_state) + 
  geom_point(alpha = .2) + 
  geom_smooth(method = "lm", color = "black") +
  geom_text(check_overlap = T, hjust = "inward", vjust = "inward") + 
  scale_color_viridis_c(direction = -1, option = "E") + 
  labs(x = "Corporate Political Action Committee $ (Millions)",
       y = "Average Interbranch Representation (logged)") 
```


```{r pac-correlation}
cor.test(d1$perYear, d1$PACamount_m)
cor.test(log(d1$perYear + 1), d1$PACamount_m)
```


## Values for Predictions

The most frequent legislator agency pair: McCain x VA with 2159 letters!

The average is  `r perYear_mean` letters per legislator per year, `r mean` letters per agency per year.
For predictions, we need an average member-year-agency triad. The first table below shows the members who averaged  `r perYear_mean`, entered Congress between 2007 and 2011, were observed in our data for at least seven years, and most often submitted exactly one letter to an agency (the closest integer  `r perYear_mean` ). For realism, this person would ideally become a chair at some point in our data. 

:::{.callout-warning}
In the figures below, uncertainty intervals around predictions do not include uncertainty in the estimates of the fixed effects. This is because the standard errors returned by marginaleffects::predictions() do not reflect uncertainty in the fixed effect estimation. Since we are just using predictions to illustrate the effects of interest, not make any claims about particular years, legislators, or agencies (the fixed effects), the uncertainty in the fixed effect estimates is not relevant for our use case (illustrating main effects, for which we do have estimates of uncertainty). However, we wish to alert users of these code that they should not use the predictions to make such claims. 

For further discussion, see [this discussion](https://github.com/vincentarelbundock/marginaleffects/issues/1487) that led the authors of the marginaleffects package to [stop](https://marginaleffects.com/bonus/NEWS_r.html#section) allowing users to calculate predictions for fixed effects models (due to their potential misuses and possible differences from uncertianty bounds that do include uncertianty related to the estimation of fixed effects).
:::

<!--
Of the modal legislators, 
John Barrasso and
Phil Roe 
meet this last criterion. However, whereas Barrasso's seat was always held by a Republican, Roe's seat flipped, adding realism to our predictions from models that include whether a legislator is replacing a co-partisan or not. 
Roe entered in 2009 and became a chair in 2017.
The IRS is a fairly modal agency, so predictions are Phil Roe X Treasury IRS X 2015. 
Other legislators, years, and agencies are simply intercept shifts. 
--> 

### Modal agencies

```{r modal-agencies}
 data_member %>% 
 group_by(agency, year) %>% 
  summarise(perAgency = sum(perYear),
            agency_ideo = mean(agency_ideo)) %>% 
  ungroup() %>% 
  mutate(median = median(perAgency),
         diff = abs(perAgency - median)) %>% 
  arrange(diff) %>% 
  drop_na(agency_ideo) %>% 
  kablebox()
```


### Modal legislators

```{r modal-legislators}
modal <- data_member %>% 
  group_by(icpsr) %>% 
  filter(first_year > 2006, first_year < 2013,  max_year > 6) %>% 
  mutate(Chair = sum(chair, na.rm = T) >1) %>% 
  group_by(icpsr, year) %>%
  mutate(perLeg = sum(perYear)) %>% 
  filter(perYear == 1, perLeg == perYear_mean  ) %>% 
  select(perAgency = perYear, 
         congress,
         perLeg, 
         agency, bioname, 
           Legislator_x_Agency,
                        Year_x_Agency,
                        Legislator,
                        Year, first_year, max_year, Chair) %>% 
  distinct() %>% 
  ungroup() %>% 
  left_join(member_data %>% select(bioname, icpsr, congress))


modal %>%
  mutate(average = perLeg) %>% 
  count(average, bioname, first_year, max_year, Chair, sort = T, name = "agency_year_count == 1") %>% 
  distinct() %>%
  arrange(-Chair) %>%
  kablebox()
```

### Modal legislator-agency pairs

```{r values, fig.width=5, fig.height=3}

modal %<>% filter(Chair) %>% distinct()

modal %>%
  kablebox()

data_member %>% 
  group_by(icpsr, year) %>% 
  mutate(perYearleg = sum(perYear)) %>%
  #mutate (perLegislator = sum(perYear)) %>% 
  ungroup() %>% 
  mutate(meanLeg = mean(perYearleg),
         meanYear = mean(perYear)) %>%
  filter( abs(perYearleg - perYear_mean) < 10,   
          perYear < 10 )  %>% 
  drop_na(agency_ideo) %>% 
  ggplot() +
  aes(x = perYear, 
      y = perYearleg) + 
  geom_jitter(alpha = .5) + 
  geom_vline(aes(xintercept = meanYear), color = "blue") + 
  geom_hline(aes(yintercept = meanLeg), color = "blue") + 
  geom_text_repel(
    aes( label = ifelse(icpsr_agency %in% modal$Legislator_x_Agency & agency_year %in% modal$Year_x_Agency , 
                     icpsr_agency, 
                     NA)  ),
    color = "red", 
    box.padding = 0.5, 
    max.overlaps = Inf
    ) + 
  labs(x = "Contacts per Legislator per Agency per year",
       y = "Contacts per Legislator per year") + 
  scale_x_continuous(breaks = seq.int(0, 9, length.out =  10))

modal %>%
  ungroup() %>% 
  distinct(agency, perAgency, bioname, 
           Legislator_x_Agency,
                        Year_x_Agency,
                        Legislator,
                        Year) %>% 
  kablebox()


# modal pair  
n <- 1 

# by chair and President's party
values <- tidyr::expand(data_member,
                        chair = chair, 
                        oversight = 0,
                        distance = data_member$distance |> mean(na.rm = T),
                        ranking_minority	= FALSE, 
                        prestige = TRUE, 
                        competitive = FALSE,
                        competitive_primary = FALSE,
                        experience = 1, 
                        first = FALSE,
                        second = FALSE,
                        third = FALSE,
                        fourth = FALSE,
                        fifth = FALSE, 
                        sixth = FALSE,
                        agency =  modal$agency[n],
                        Legislator_x_Agency = modal$Legislator_x_Agency[n],
                        Year_x_Agency = modal$Year_x_Agency[n],
                        Legislator =  modal$Legislator[n],
                        Year =  modal$year[n],
                        majority = TRUE,
                        presidents_party = presidents_party
                   ) %>% 
  drop_na(majority, chair)

# by year 
values_tenure <- tidyr::expand(data_member,
                        chair = chair, 
                        oversight = 0,
                                                distance = data_member$distance |> mean(na.rm = T),
                        ranking_minority	= FALSE, 
                        prestige = TRUE, 
                        competitive = FALSE,
                        competitive_primary = FALSE,
                        experience = experience, 
                        # first = first,
                        # second = second,
                        # third = third,
                        # fourth = fourth,
                        # fifth = fifth, 
                        # sixth = sixth,
                        agency =  modal$agency[n],
                        Legislator_x_Agency = modal$Legislator_x_Agency[n],
                        Year_x_Agency = modal$Year_x_Agency[n],
                        Legislator =  modal$Legislator[n],
                        Year =  modal$year[n],
                        majority = TRUE,
                        presidents_party = TRUE
                   ) %>% 
  drop_na(chair)
```


# Model Results: Counts per member per year

Clustering standard errors at the legislator level:

["Clustering on the panel variable produces an estimator of the VCE that is robust to cross-sectional heteroskedasticity and within-panel (serial) correlation that is asymptotically equivalent to that proposed by Arellano (1987)"](https://www.stata.com/manuals13/xtxtreg.pdf)

We use `fixest::fenegbin` here and replicated the main models using `xtreg` in Replication.do.
See more about how robust (clustered) standard errors with fixed effects are calculated by `fixest` [here](https://lrberge.github.io/fixest/articles/standard_errors.html) and by  `xtreg` [here](https://www.stata.com/manuals13/xtxtreg.pdf).


---

# Full model 

{{< include code/replication-full.qmd >}}

## Private Sector only (For Types 2 & 4)

{{< include code/replication-full-private.qmd >}}

## + Nonprofit Sector (For Type 3)

{{< include code/replication-full-nonprofit.qmd >}}



## With Majority Status Rather than Committee Chair

{{< include code/replication-full-majority.qmd >}}

# Inequality figures based on full model 

## Demand

### Population

#### population-Senate cross sectional 

Compared to counterfactual of all states having the population of Tennessee (the average) 


```{r}
#| label: "m-population-Senate-effect"
#| fig-cap: "figs/[TYPE]/m-population-Senate-effect"
#| layout-ncol: 2
#| fig-height: 3.5
#| fig-width: 3.5
#| fig-subcap: 
#|   - "1"
#|   - "2"
#| out-width: "100%"
#| fig-show: "hold"

model <- m_full_senate_cross
data = data_member |> filter(chamber=="Senate")  |> filter(year > 2007,  year < 2019)
mean_pop <- data |> group_by(state) |> 
  summarise(pop = mean(population_m)) |> 
  ungroup() |> 
  mutate(mean = mean(pop),
         diff = abs(pop - mean))  |> 
  slice_min(diff)

mean_pop

plot_effect( 
  newdata = mutate(data, population_m = mean_pop$pop),
  effect = "Unequal state population"
  )
```


```{r}
#| label: "m-population-Senate-effect-min"
#| fig-cap: "figs/[TYPE]/m-population-Senate-effect-min"
#| layout-ncol: 2
#| fig-height: 3.5
#| fig-width: 3.5
#| fig-subcap: 
#|   - "1"
#|   - "2"
#| out-width: "100%"
#| fig-show: "hold"

model <- m_full_senate_cross
data = data_member |> filter(chamber=="Senate")  |> filter(year > 2007,  year < 2019)

plot_effect( 
  newdata = mutate(data, population_m = min(data$population_m)),
  effect = "Unequal state population"
  )
```

#### population-Senate diff in diff

Compared to counterfactual of all states having the population of Wyoming 

```{r}
#| label: "m-population-Senate-did-effect-min"
#| fig-cap: "figs/[TYPE]/m-population-Senate-did-effect-min"
#| layout-ncol: 2
#| fig-height: 3.5
#| fig-width: 3.5
#| fig-subcap: 
#|   - "1"
#| out-width: "100%"
#| fig-show: "hold"

model <- m_full_senate_did
data = data_member |> filter(chamber=="Senate")  |> filter(year > 2007,  year < 2019)

plot_effect( 
  newdata = mutate(data, population_m =min(data$population_m)),
  effect = "Unequal state population \n(diff in diff)"
  )
```


### Workers 



#### workers- cross sectional 

```{r}
#| label: "m-workers-effect"
#| fig-cap: "figs/[TYPE]/m-workers-effect"
#| layout-ncol: 2
#| fig-height: 3.5
#| fig-width: 3.5
#| fig-subcap: 
#|   - "1"
#|   - "2"
#| out-width: "100%"
#| fig-show: "hold"

model <- m_full_cross
data = data_member |> filter(year > 2007,  year < 2019)

plot_effect( 
  newdata = mutate(data, percent_workers_government = 0),
  effect = "% Government Employment"
  )
```

#### workers- diff in diff

```{r}
#| label: "m-workers-did-effect"
#| fig-cap: "figs/[TYPE]/m-workers-did-effect"
#| layout-ncol: 2
#| fig-height: 3.5
#| fig-width: 3.5
#| fig-subcap: 
#|   - "1"
#| out-width: "100%"
#| fig-show: "hold"

model <- m_full_did
data = data_member #|> filter(year > 2007,  year < 2019)

plot_effect( 
  newdata = mutate(data, percent_workers_government = 0),
  effect = "% Government Employment\n(diff in diff)"
  )
```



#### workers-nonprofit - cross sectional 

```{r}
#| label: "m-workers-nonprofit-effect"
#| fig-cap: "figs/[TYPE]/m-workers-nonprofit-effect"
#| layout-ncol: 2
#| fig-height: 3.5
#| fig-width: 3.5
#| fig-subcap: 
#|   - "1"
#|   - "2"
#| out-width: "100%"
#| fig-show: "hold"

model <- m_full_nonprofit_cross
data = data_member |> filter(year > 2007,  year < 2019)

plot_effect( 
  newdata = mutate(data, percent_workers_nonprofit = 0),
  effect = "% District Nonprofit Employment"
  )
```

#### workers-nonprofit - diff in diff

```{r}
#| label: "m-workers-nonprofit-did-effect"
#| fig-cap: "figs/[TYPE]/m-workers-nonprofit-did-effect"
#| layout-ncol: 2
#| fig-height: 3.5
#| fig-width: 3.5
#| fig-subcap: 
#|   - "1"
#| out-width: "100%"
#| fig-show: "hold"

model <- m_full_nonprofit_did
data = data_member |> filter(year > 2007,  year < 2019)

plot_effect( 
  newdata = mutate(data, percent_workers_nonprofit = 0),
  effect = "% District Nonprofit Employment\n(diff in diff)"
  )
```




#### workers-private - cross sectional 

```{r}
#| label: "m-workers-private-effect"
#| fig-cap: "figs/[TYPE]/m-workers-private-effect"
#| layout-ncol: 2
#| fig-height: 3.5
#| fig-width: 3.5
#| fig-subcap: 
#|   - "1"
#|   - "2"
#| out-width: "100%"
#| fig-show: "hold"

model <- m_full_private_cross
data = data_member |> filter(year > 2007,  year < 2019)

plot_effect( 
  newdata = mutate(data, percent_workers_private_sector = 0),
  effect = "% Private Sector"
)

plot_effect( 
  newdata = mutate(data, percent_workers_self_employed = 0),
  effect = "% Self Employment"
)
```

#### workers- diff in diff

```{r}
#| label: "m-workers-did-effect-private"
#| fig-cap: "figs/[TYPE]/m-workers-did-effect"
#| layout-ncol: 2
#| fig-height: 3.5
#| fig-width: 3.5
#| fig-subcap: 
#|   - "1"
#| out-width: "100%"
#| fig-show: "hold"

model <- m_full_private_did
data = data_member |> filter(year > 2007,  year < 2019)

plot_effect( 
  newdata = mutate(data, percent_workers_private_sector = 0),
  effect = "% Private Sector\n(diff in diff)"
)

plot_effect( 
  newdata = mutate(data, percent_workers_self_employed = 0),
  effect = "% Self Employment\n(diff in diff)"
)
```



### Education 



#### education - cross sectional 

```{r}
#| label: "m-education-effect"
#| fig-cap: "figs/[TYPE]/m-education-effect"
#| layout-ncol: 2
#| fig-height: 3.5
#| fig-width: 3.5
#| fig-subcap: 
#|   - "1"
#|   - "2"
#| out-width: "100%"
#| fig-show: "hold"

model <- m_full_cross
data = data_member |> filter(year > 2007,  year < 2019)

plot_effect( 
  newdata = mutate(data, percent_education_bachelor_or_higher = 0),
  effect = "% College Grad"
  )
```

#### education - diff in diff

```{r}
#| label: "m-education-did-effect"
#| fig-cap: "figs/[TYPE]/m-education-did-effect"
#| layout-ncol: 2
#| fig-height: 3.5
#| fig-width: 3.5
#| fig-subcap: 
#|   - "1"
#| out-width: "100%"
#| fig-show: "hold"

model <- m_full_did
data = data_member #|> filter(year > 2007,  year < 2019)

plot_effect( 
  newdata = mutate(data, percent_education_bachelor_or_higher = 0),
  effect = "% College Grad\n(diff in diff)"
  )
```

### Need 

#### Need - cross sectional 

```{r}
#| label: "m-need-effect"
#| fig-cap: "figs/[TYPE]/m-need-effect-[n]"
#| layout-ncol: 2
#| fig-height: 3.5
#| fig-width: 3.5
#| fig-subcap: 
#|   - "1"
#|   - "2"
#| out-width: "100%"
#| fig-show: "hold"

model <- m_full_cross
data = data_member |> filter(year > 2007,  year < 2019)

plot_effect( 
  newdata = mutate(data, percent_public_assistance_or_snap_households = 0),
  effect = "% Public Assistance"
  )
```

#### Need - diff in diff

```{r}
#| label: "m-need-did-effect"
#| fig-cap: "figs/[TYPE]/m-need-did-effect"
#| layout-ncol: 2
#| fig-height: 3.5
#| fig-width: 3.5
#| fig-subcap: 
#|   - "1"
#| out-width: "100%"
#| fig-show: "hold"

model <- m_full_did
data = data_member #|> filter(year > 2007,  year < 2019)

plot_effect( 
  newdata = mutate(data, percent_public_assistance_or_snap_households = 0),
  effect = "% Public Assistance\n(diff in diff)"
  )
```

### Total Demand 

#### Total Demand - cross sectional 

m-total-demand-effect

```{r}
#| label: "m-total-demand-effect"
#| fig-cap: "figs/[TYPE]/m-total-demand-effect-[n]"
#| layout-ncol: 2
#| fig-height: 3.5
#| fig-width: 3.5
#| fig-subcap: 
#|   - "1  = House"
#|   - "2 = Senate "
#| out-width: "100%"
#| fig-show: "hold"

model <- m_full_house_cross
data = data_member |> filter(year > 2007,  year < 2019, chamber == "House")  

plot_effect( 
  newdata = mutate(data, 
                   percent_public_assistance_or_snap_households = 0,
                   percent_education_bachelor_or_higher = 0,
                   percent_workers_government = 0,
                   population_m = min(data$population_m)),
  effect = "Total Demand (House)"
  )

model <- m_full_senate_cross
data = data_member |> filter(year > 2007,  year < 2019, chamber == "Senate")  

plot_effect( 
  newdata = mutate(data, 
                   percent_public_assistance_or_snap_households = 0,
                   percent_education_bachelor_or_higher = 0,
                   percent_workers_government = 0,
                   population_m = min(data$population_m)),
  effect = "Total Demand (Senate)"
  )
```

#### Total Demand - diff in diff

```{r}
#| label: "m-total-demand-did-effect"
#| fig-cap: "figs/[TYPE]/m-total-demand-did-effect-[n]"
#| layout-ncol: 2
#| fig-height: 3.5
#| fig-width: 3.5
#| fig-subcap: 
#|   - "1 = House"
#|   - "2 = Senate"
#| out-width: "100%"
#| fig-show: "hold"

model <- m_full_house_did
data = data_member |> filter(year > 2007,  year < 2019, chamber == "House")  

plot_effect( 
  newdata = mutate(data, 
                   percent_public_assistance_or_snap_households = 0,
                   percent_education_bachelor_or_higher = 0,
                   percent_workers_government = 0,
                   population_m = min(data$population_m)),
  effect = "Total Demand (House)\n(diff in diff)"
  )

model <- m_full_senate_did
data = data_member |> filter(year > 2007,  year < 2019, chamber == "Senate")  

plot_effect( 
  newdata = mutate(data, 
                   percent_public_assistance_or_snap_households = 0,
                   percent_education_bachelor_or_higher = 0,
                   percent_workers_government = 0,
                   population_m = min(data$population_m)),
  effect = "Total Demand (Senate)"
  )
```


## Capacity 

m-effect-capacity 

```{r}
#| label: "m-capacity-effect"
#| fig-cap: "figs/[TYPE]/m-capacity-effect"
#| layout-ncol: 4
#| fig-height: 3.5
#| fig-width: 3.5
#| fig-subcap: 
#|   - "1"
#|   - "2"
#|   - "3"
#|   - "4"
#|   - "5"
#|   - "6"
#|   - "7"
#|   - "8"
#| out-width: "100%"
#| fig-show: "hold"

model <- m_full_cross
data = data_member |> filter(year > 2007,  year < 2019)

# 1
plot_effect( 
  newdata = mutate(data, chair = 0),
  effect = "Chair"
  )
#2
plot_effect( 
  newdata = mutate(data, subchr = 0),
  effect = "Subcommittee Chair"
  )

#3
plot_effect( 
  newdata = mutate(data, ranking_minority = 0),
  effect = "Ranking Minority"
  )
# #4
# plot_effect(
#   newdata = mutate(data, prestige = 0),
#   effect = "Prestige Committee"
#   )
#4
plot_effect( 
  newdata = mutate(data, oversight = 0),
  effect = "Oversight Committee"
  )
#5
plot_effect( 
  newdata = mutate(data, experience = 0),
  effect = "3+ years in office"
  )
#6
plot_effect( 
  newdata = mutate(data, majority = 0),
  effect = "Majority"
  )
#7
plot_effect( 
  newdata = mutate(data, presidents_party = 0),
  effect = "President's party"
  )
#8
plot_effect( 
  newdata = mutate(data, 
                   #chamber = "Senate",
                   chair = 0,
                   subchr = 0,
                   ranking_minority = 0,
                   oversight = 0,
                   prestige = 0,
                   experience = 0),
  effect = "Total capacity"
  )

#9 chamber 
plot_effect( 
  newdata = mutate(data, 
                   chamber = "Senate"),
  effect = "Chamber (Senate)"
  )

#10 total, including chamber 
plot_effect( 
  newdata = mutate(data, 
                   chamber = "Senate",
                   chair = 0,
                   subchr = 0,
                   ranking_minority = 0,
                   oversight = 0,
                   prestige = 0,
                   experience = 0),
  effect = "Total capacity"
  )
```


## Environment 

### Elections 

#### electoral - cross sectional 

```{r}
#| label: "m-elect-effect"
#| fig-cap: "figs/[TYPE]/m-elect-effect"
#| layout-ncol: 2
#| fig-height: 3.5
#| fig-width: 3.5
#| fig-subcap: 
#|   - "1 - House - general"
#|   - "2 - House - primary"
#|   - "3 - House - combined"
#|   - "4 - Senate - general"
#| out-width: "100%"
#| fig-show: "hold"

model <- m_full_house_cross
data = data_member |> filter(chamber == "House", 
                             year > 2007,  year < 2019)

plot_effect( 
  newdata = mutate(data, competitive = 0),
  effect = "Competitive general election (House)"
  )


plot_effect( 
  newdata = mutate(data, competitive_primary = 0),
  effect = "Competitive primary election (House)"
  )

plot_effect( 
  newdata = mutate(data, competitive = 0,
                            competitive_primary = 0),
  effect = "Total electoral competition (House)"
  )


# SENATE 
model <- m_full_senate_cross
data = data_member |> filter(chamber == "Senate", 
                             year > 2007,  year < 2019)
plot_effect( 
  newdata = mutate(data, competitive = 0),
  effect = "Competitive general election (Senate)"
  )
```

#### electoral - diff in diff

```{r}
#| label: "m-elect-did-effect"
#| fig-cap: "figs/[TYPE]/m-elect-did-effect"
#| layout-ncol: 2
#| fig-height: 3.5
#| fig-width: 3.5
#| fig-subcap: 
#|   - "1 - House and Senate"
#|   - "2 - House"
#|   - "3 - House"
#| out-width: "100%"
#| fig-show: "hold"

model <- m_full_did
data = data_member |> filter(year > 2007,  year < 2019)

plot_effect( 
  newdata = mutate(data, competitive = 0),
  effect = "Competitive general election\n(diff in diff)"
  )


model <- m_full_house_cross
data = data_member |> filter(chamber == "House", 
                             year > 2007,  year < 2019)
plot_effect( 
  newdata = mutate(data, competitive_primary = 0),
  effect = "Competitive primary election\n(diff in diff)"
  )

plot_effect( 
  newdata = mutate(data, competitive = 0,
                            competitive_primary = 0),
  effect = "Total electoral competition\n(diff in diff)"
  )
```


### Ideology 


m-ideo-effect

```{r}
#| label: "m-ideo-effect"
#| fig-cap: "figs/[TYPE]/m-ideo-effect"
#| layout-ncol: 2
#| fig-height: 3.5
#| fig-width: 3.5
#| fig-subcap: 
#|   - "1"
#|   - "2"
#|   - "3"
#|   - "4"
#| out-width: "100%"
#| fig-show: "hold"

model <- m_full_cross 
data = data_member |> filter(year > 2007,  year < 2019)

plot_effect( 
  newdata = data |>  
    mutate(nominate_dim1 = 0) |>
    mutate(distance = abs(nominate_dim1 - agency_ideo)),
  effect = "Legislator ideology"
  )

plot_effect(
  newdata = data |>  
    mutate(agency_ideo = 0) |>  
    mutate(distance = abs(nominate_dim1 - agency_ideo)),
  effect = "Perceived agency ideology"
  )
```

### Partisanship 

m-partisan- effect 

```{r}
#| label: "m-partisan-effect"
#| fig-cap: "figs/[TYPE]/m-partisan-effect"
#| layout-ncol: 2
#| fig-height: 3.5
#| fig-width: 3.5
#| fig-subcap: 
#|   - "1"
#|   - "2"
#|   - "3"
#|   - "4"
#| out-width: "100%"
#| fig-show: "hold"

model <- m_full_cross 
data = data_member |> filter(year > 2007,  year < 2019)

plot_effect( 
  newdata = data |>  mutate(presidents_party = 0),
  effect = "Co-partisan president"
  )

model <- m_full_majority_cross 

plot_effect(
  newdata = data |> mutate(majority = 0) , 
  effect = "Majority party"
  )


```



# Replicating Ritchie

{{< include code/replication-ritchie.qmd >}}

# Demand

{{< include code/replication-demand.qmd >}}

## Population

{{< include code/replication-population-senate.qmd >}}
{{< include code/replication-population-house.qmd >}}

## District Employment + Population

{{< include code/replication-population-workers-senate.qmd >}}
{{< include code/replication-population-workers-house.qmd >}}
{{< include code/replication-population-workers-nonprofit-senate.qmd >}}
{{< include code/replication-population-workers-nonprofit-house.qmd >}}
{{< include code/replication-population-workers-private-senate.qmd >}}
{{< include code/replication-population-workers-private-house.qmd >}}

## District Employment

<!-- These now include population as well, so the real difference in "workers" models is that they are pooled, whereas the "population-workers" are split house and senate
#TODO rename "workers" as "population-workers" for consistency ---> 

{{< include code/replication-workers.qmd >}}
{{< include code/replication-workers-nonprofit.qmd >}}
{{< include code/replication-workers-private.qmd >}}

# Capacity 

{{< include code/replication-capacity.qmd >}}
{{< include code/replication-capacity-house.qmd >}}
{{< include code/replication-capacity-senate.qmd >}}

## Staff expierence 

see Per District models below

# Strategic Responses to the Political Environment 

## Electoral Context

{{< include code/replication-elect.qmd >}}
{{< include code/replication-elect-basic.qmd >}}
{{< include code/replication-elect-general.qmd >}}
{{< include code/replication-elect-primary.qmd >}}

## Staff Allocation 

{{< include code/replication-staff.qmd >}}
{{< include code/replication-staff-only.qmd >}}

## Style 

{{< include code/replication-style.qmd >}}

## PAC Money 

{{< include code/replication-pac.qmd >}}


<!--

# Ideology

{{< include code/replication-ideology.qmd >}}
--> 


# Per District

## Data

<!--
#TODO deal with chamber switchers ? or maybe we don't need to since everything is calculated grouped at chamber level?
# count(member_data, bioname, icpsr, congress, sort = T) |> filter(n >1)
-->

The main district-level models in the paper focus on estimating the effect of legislator experience by leveraging turnover within districts. We compare the service that a district receives before and after electing a new legislator and in the following years as legislators gain experience in office.

```{r add-crosswalk}
data_district |> 
  count(same_party) |> 
  kablebox()

# data_district |> filter(chamber == "House") |>   select(icpsr, state_dist, year, state_dist_party, lag_p, same_party, new_member)   |> kablebox()

data_district %<>% mutate(same_party = as.numeric(same_party))
```

{{< include code/replication-district.qmd >}}



# Appendix models 



## Demand 

### Default  

```{r save-demand-models}
models_demand <- list(
  "(1)" = m_population_House_cross,
  "(2)" = m_population_Senate_cross,
  # counts are  colinear with population, so just using % 
  "(3)" = m_population_percent_workers_House_cross, 
  "(4)" = m_population_percent_workers_Senate_cross,
  "(5)" = m_workers_cross,
  "(6)" = m_workers_did
)

rows <- tibble(
  term = c("Dependent variable", 
           "All legislators", 
           "Only House",
           "Only Senate"),
  `(1)` = c("Count", "", "X", ""),
  `(2)` =c("Count", "", "", "X"),
  `(3)` = c("Count","", "X", ""),
    `(4)` = c("Count", "", "", "X"),
      `(5)` = c("Count", "X", "", ""),
        `(6)` = c("Count", "X", "", "")

)

# call coefs
attr(rows, 'position') <- c(0)

# HTML
modelsummary(models_demand, 
             title = "", 
             notes = list("Robust standard errors in parentheses, clustered by legislator."))

beta_cross <- betas(m_demand_cross)
se_cross <- standard_errors(m_demand_cross)

save(models_demand, rows, cm, gm, beta_cross, se_cross,
     file = here::here("models", type, "models_demand.Rdata"))
```





### Private  

```{r save-demand-private-models}
models_demand_private <- list(
  "(1)" = m_population_House_cross,
  "(2)" = m_population_Senate_cross,
  # counts are  colinear with population, so just using % 
  "(3)" = m_population_percent_workers_private_House_cross, 
  "(4)" = m_population_percent_workers_private_Senate_cross,
  "(5)" = m_workers_private_cross,
  "(6)" = m_workers_private_did
)

rows <- tibble(
  term = c("Dependent variable", 
           "All legislators", 
           "Only House",
           "Only Senate"),
  `(1)` = c("Count", "", "X", ""),
  `(2)` =c("Count", "", "", "X"),
  `(3)` = c("Count","", "X", ""),
    `(4)` = c("Count", "", "", "X"),
      `(5)` = c("Count", "X", "", ""),
        `(6)` = c("Count", "X", "", "")

)

# call coefs
attr(rows, 'position') <- c(0)

# HTML
modelsummary(models_demand_private, 
             title = "", 
             notes = list("Robust standard errors in parentheses, clustered by legislator."))


save(models_demand_private, rows, cm, gm, beta_cross, se_cross,
     file = here::here("models", type, "models_demand_private.Rdata"))
```

```{r}
#| label: "m-private-cross-effect"
#| fig-cap: "figs/[TYPE]/m-private-cross-effect"
#| layout-ncol: 2
#| fig-height: 3.5
#| fig-width: 3.5
#| fig-subcap: 
#|   - "1"
#| out-width: "100%"
#| fig-show: "hold"

model <- m_workers_private_cross
data = data_member |> filter(year > 2007,  year < 2019)

plot_effect( 
  newdata = mutate(data, percent_workers_private_sector = 0 ),
  effect = "Percent private-sector"
  )
```

### Nonprofit  

```{r save-demand-nonprofit-models}
models_demand_nonprofit <- list(
  "(1)" = m_population_House_cross,
  "(2)" = m_population_Senate_cross,
  # counts are  colinear with population, so just using % 
  "(3)" = m_population_percent_workers_nonprofit_House_cross, 
  "(4)" = m_population_percent_workers_nonprofit_Senate_cross,
  "(5)" = m_workers_nonprofit_cross,
  "(6)" = m_workers_nonprofit_did
)

rows <- tibble(
  term = c("Dependent variable", 
           "All legislators", 
           "Only House",
           "Only Senate"),
  `(1)` = c("Count", "", "X", ""),
  `(2)` =c("Count", "", "", "X"),
  `(3)` = c("Count","", "X", ""),
    `(4)` = c("Count", "", "", "X"),
      `(5)` = c("Count", "X", "", ""),
        `(6)` = c("Count", "X", "", "")

)

# call coefs
attr(rows, 'position') <- c(0)

# HTML
modelsummary(models_demand_nonprofit, 
             title = "", 
             notes = list("Robust standard errors in parentheses, clustered by legislator."))

beta_cross <- betas(m_workers_nonprofit_cross)
se_cross <- standard_errors(m_workers_nonprofit_cross)

save(models_demand_nonprofit, rows, cm, gm, beta_cross, se_cross,
     file = here::here("models", type, "models_demand_nonprofit.Rdata"))
```


## Capacity Table 1: Institutional Position 

"models_capacity.Rdata"

```{r save-capacity-models}
models_capacity <- list(
  "(1)" = m_capacity_cross,
  "(2)" = m_capacity_did,
  "(3)" =  m_capacity_House_cross,
  "(4)" = m_capacity_House_did,
   "(5)" =  m_capacity_Senate_cross,
  "(6)" = m_capacity_Senate_did
)

rows <- tibble(
  term = c("Dependent variable", 
           "All legislators", 
           "Only House",
           "Only Senate"),
  `(1)` = c("Count", "X", "", ""),
  `(2)` =c("Count", "X", "", ""),
  `(3)` = c("Count","", "X", ""),
    `(4)` = c("Count", "", "X", ""),
  `(5)` =c("Count", "","","X"),
  `(6)` = c("Count","","", "X")
  )

attr(rows, 'position') <- c(0)

modelsummary(models_capacity) 

save(models_capacity, rows, cm, gm,   beta_cross, beta_did, se_cross, se_did,
     file = here::here("models", type, "models_capacity.Rdata"))
```



## Capacity Table 2: Staff Quality - District + Same Party 

"models_district.Rdata"

```{r save-district-models}
models_district <- list(
  "(1)" = m_district_cross,
  "(2)" = m_district_did,
  "(3)" =  m_district_party_cross,
  "(4)" = m_district_party_did,
  "(5)" = m_district_full_cross,
  "(6)" = m_district_full_did
)

rows <- tibble(
  term = c("Dependent variable"),
  `(1)` = c("Count"),
  `(2)` =c("Count"),
  `(3)` = c("Count"),
  `(4)` =c("Count"),
  `(5)` = c("Count"),
  `(6)` =c("Count")
  )

attr(rows, 'position') <- c(0)

modelsummary(models_district)

beta_did <- betas(m_district_did)
se_did <- standard_errors(m_district_did)
beta_cross <- betas(m_district_cross)
se_cross <- standard_errors(m_district_cross)

save(models_district, rows, cm, gm,   beta_cross, beta_did, se_cross, se_did,
     file = here::here("models", type, "models_district.Rdata"))
```


## Strategic Environment Table 1: Electoral motivations 

"models_elect.Rdata"

```{r save-elect-models}


models_elect <- list(
    "(1)" = m_elect_basic_cross,
  "(2)" = m_elect_basic_primary_cross,
  "(3)" = m_elect_general_cross,
  "(4)" = m_elect_general_did,
   "(5)" =  m_elect_primary_cross,
   "(6)" = m_elect_primary_did
)

rows <- tibble(
  term = c("Dependent variable", "House Only"),
  `(1)` = c("Count", ""),
  `(2)` =c("Count", "X"),
  `(3)` = c("Count",""),    
  `(4)` = c("Count", ""),
  `(5)` = c("Count","X"),    
  `(6)` = c("Count", "X")
  )


attr(rows, 'position') <- c(0)


# HTML
modelsummary(models_elect,
             notes = list("Robust standard errors in parentheses, clustered by legislator.") ) 

beta_cross <- betas(m_elect_cross)
se_cross <- standard_errors(m_elect_cross)
beta_did <- betas(m_elect_did)
se_did <- standard_errors(m_elect_did)


save(models_elect, rows, cm, gm,  beta_cross, beta_did, se_cross, se_did,
     file = here::here("models", type, "models_elect.Rdata"))
```








## Strategic Environment Table 2: Fundraising motivations 

"models_pac.Rdata"

```{r save-pac-models}
models_pac <- list(
  "(1)" = m_pac_cross,
  "(2)" = m_pac_did,
   "(3)" =  m_pac_full_cross,
   "(4)" = m_pac_full_did
)

rows <- tibble(
  term = c("Dependent variable"),
  `(1)` = c("Count"),
  `(2)` =c("Count"),
  `(3)` = c("Count"),    
  `(4)` = c("Count")
  )


attr(rows, 'position') <- c(0)


# HTML
modelsummary(models_pac,
             notes = list("Robust standard errors in parentheses, clustered by legislator.") ) 

beta_cross <- betas(m_pac_cross)
se_cross <- standard_errors(m_pac_cross)
beta_did <- betas(m_pac_did)
se_did <- standard_errors(m_pac_did)


save(models_pac, rows, cm, gm,  beta_cross, beta_did, se_cross, se_did,
     file = here::here("models", type, "models_pac.Rdata"))
```

"models_pac_energy.Rdata"

```{r save-pac-energy-models}
models_pac_energy <- list(
  "(1)" = m_pac_pooled_cross,
  "(2)" = m_pac_pooled_did,
   "(3)" =  m_pac_pooled_full_cross,
   "(4)" = m_pac_pooled_full_did
)

rows <- tibble(
  term = c("Dependent variable", "Dept. Of Energy Only"),
  `(1)` = c("Count", "X"),
  `(2)` =c("Count", "X"),
  `(3)` = c("Count", "X"),    
  `(4)` = c("Count", "X")
  )


attr(rows, 'position') <- c(0)


# HTML
modelsummary(models_pac_energy,
             notes = list("Robust standard errors in parentheses, clustered by legislator.") ) 

beta_cross <- betas(m_pac_pooled_cross)
se_cross <- standard_errors(m_pac_pooled_cross)
beta_did <- betas(m_pac_pooled_did)
se_did <- standard_errors(m_pac_pooled_did)


save(models_pac_energy, rows, cm, gm,  beta_cross, beta_did, se_cross, se_did,
     file = here::here("models", type, "models_pac_energy.Rdata"))
```


## Stratgy Table 3: Staff Allocation 


"models_staff_spending.Rdata"
"models_staff_only_spending.Rdata"

```{r save-staff-spending-models}
models_staff_spending <- list(
  "(1)" = m_staff_only_spending_cross,
  "(2)" = m_staff_only_spending_did,
  "(3)" =  m_staff_spending_cross,
  "(4)" = m_staff_spending_did
)

rows <- tibble(
  term = c("Dependent variable", "House Only"),
  `(1)` = c("Count", "X"),
  `(2)` =c("Count", "X"),
  `(3)` = c("Count","X"),    
  `(4)` = c("Count", "X")
  )


attr(rows, 'position') <- c(0)

modelsummary(models_staff_spending)

beta_did <- betas(m_staff_only_spending_did)
se_did <- standard_errors(m_staff_only_spending_did)
beta_cross <- betas(m_staff_only_spending_cross)
se_cross <- standard_errors(m_staff_only_spending_cross)

save(models_staff_spending, rows, cm, gm,   beta_cross, beta_did, se_cross, se_did,
     file = here::here("models", type, "models_staff_spending.Rdata"))
```





























## Strategic Environment Table 3: Ideological motivations - NOW COMBINED WITH ABOVE ELECT TABLESS SO NOT PUTTING THIS IN 

 "models_ideo.Rdata"

```{r save-ideo-models, eval=FALSE}
models_ideo <- list(
  "(1)" = m_ideo_cross,
  "(2)" = m_ideo_2nd_cross
)

rows <- tibble(
  term = c("Dependent variable"),
  `(1)` = c("Count"),
  `(2)` = c("Count")
)

attr(rows, 'position') <- c(0)

modelsummary(models_ideo) 

beta_cross <- betas(m_ideo_cross)
se_cross <- standard_errors(m_ideo_cross)

save(models_ideo, rows, cm, gm,   beta_cross, se_cross,
     file = here::here("models", type, "models_ideo.Rdata"))
```



