

## per District

The main results showing that replacing a more experienced legislator with a new legislator yields a substantial decrease in service to the district are robust to interacting all variables with the `same_party` variable. 
Cross-sectional effects get larger but more uncertain when data are subset to district years after turnover (as required for the `same_party` variable). Within-district effects become more uncertain, likely due to the much smaller number of observations where `same_party` can be observed. 


### District-level Coefficient Plots

Figures: `figs/[TYPE]/m-district-[1:4].png`

1. cross-sectional 
2. cross-sectional with same-party variable 
3. diff-in-diff
4. diff-in-diff with same party variable

```{r}
#| layout-ncol: 2
#| fig-height: 4.5
#| fig-cap: "figs/[TYPE]/m-district-[1:4].png"
#| fig-subcap: 
#|   - "1"
#|   - "2"
#|   - "3"
#|   - "4"
#| out-width: "100%"
#| label: "m-district"
#| fig-show: "hold"

# 1
m_district_cross <- fenegbin(perYear ~ chamber + 
                               
  new_member #+ second + third + fourth + fifth + sixth 
  | Year_x_Agency,
cluster = "District",
data = data_district)

if(testing){modelsummary::modelsummary(m_district_cross)}

coefplot(m_district_cross, horiz = T, drop = "(Intercept)|.theta", sub = "Reference = A member serving >6 years") 

# 2 Diff in diff
m_district_did <- fenegbin(perYear ~ #chamber + 
  new_member #+ same_party + second + third + fourth + fifth + sixth | 
  | District + Year_x_Agency,
cluster = "District",
data = data_district )

coefplot(m_district_did, horiz = T, drop = "(Intercept)|.theta", sub = "Reference = A member serving >6 years") 


# 3 wiith party 
m_district_party_cross <- fenegbin(perYear ~ chamber + 
  new_member*same_party #+ second*same_party + third*same_party + fourth*same_party + fifth*same_party + sixth*same_party 
  | Year_x_Agency,
cluster = "District",
data = data_district)

if(testing){modelsummary::modelsummary(m_district_cross)}

coefplot(m_district_party_cross, horiz = T, drop = "(Intercept)|.theta", sub = "Reference = A member serving >6 years") 



# 4 Diff in diff with party
m_district_party_did <- fenegbin(perYear ~ #chamber + 
  new_member*same_party #+ second*same_party + third*same_party + fourth*same_party + fifth*same_party + sixth*same_party 
   | District + Year_x_Agency,
cluster = "District",
data = data_district )

coefplot(m_district_party_did, horiz = T, drop = "(Intercept)|.theta", sub = "Reference = A member serving >6 years") 


# 5 cross full 
m_district_full_cross <- fenegbin(
  perYear ~ #chamber + 
    new_member*same_party + 
    competitive + 
    abs(nominate_dim1) +
    distance*presidents_party +
    party 
  | Year_x_Agency,
  cluster = "District",
  data = data_district )

coefplot(m_district_full_cross, horiz = T, drop = "(Intercept)|.theta", sub = "Reference = A member serving >6 years") 


# 6 Diff in diff
m_district_full_did <- fenegbin(
  perYear ~ #chamber + 
    new_member*same_party + 
    competitive + 
    presidents_party + 
    abs(nominate_dim1) + 
    party + 
    distance*presidents_party
  | District + Year_x_Agency,
cluster = "District",
data = data_district )

coefplot(m_district_full_did, horiz = T, drop = "(Intercept)|.theta", sub = "Reference = A member serving >6 years") 

```

### Per District Tables

- Models: `models/models_district_negbin.Rdata` 


```{r models_district}
models_district <- list(
  "(1)" = m_district_cross,
  "(2)" = m_district_did,
  "(3)" = m_district_full_cross,
  "(4)" = m_district_full_did,
  "(5)" = m_district_party_cross,
  "(6)" = m_district_party_did
)

rows <- tibble(
  term = c("Dependent variable"),
  `(1)` = c("Count"),
  `(2)` =c("Count"),
  `(3)` = c("Count"),
  `(4)` = c("Count"),
  `(5)` =c("Count"),
  `(6)` =c("Count")
)

# Check marks for controls 
attr(rows, 'position') <- c(0)

modelsummary(models_district)
```


\clearpage

# Model Results:  Spillover Effects Robustness Check

This is a robustness check for an observable implication of demand-driven behavior. If variation in constituent demand drives variation in legislator behavior (specifically a preference for more senior members), then we should observe spillover effects on the rest of a delegation when an experienced member is replaced with a new member. That is, if people demand more from experienced members, people should redirect demand to the next most experienced member who represents them.

```{r spillover-data}

# new IVs: new_senator, new_proportion, new_one

dcounts_spillover <- data_district %>% 
  # FIRST, identify districts with new members 
  group_by(state, Year) %>% 
  # size of the delegation 
  add_count(name = "n_delegation") %>% 
  mutate(
    # new IVs:
    new_senator = ifelse(chamber == "Senate" & new_member == 1, 1, NA), 
    new_proportion = sum(new_member)/n_delegation, 
    new_one = ifelse(new_member == 1, 1, NA)
  ) %>% 
  fill(new_senator, .direction = "updown") %>% 
  fill(new_one, .direction = "updown") %>% 
  mutate(new_senator =   replace_na(new_senator, 0),
         new_one = replace_na(new_one, 0) 
  ) %>% 
  group_by(state, Year, chamber) %>% 
  arrange(year, state) 

  # THEN WE DROP ALL OF THE NEW MEMBERS 
dcounts_spillover %<>%   filter(new_member == 0)  


# # inspect data 
# dcounts_spillover |> select(Year, state, chamber, new_member, new_one, new_senator, new_proportion, perYear) |> ungroup() |>
#   #filter(new_senator ==1) |>  
#   #count(new_senator, new_member) |> 
#   kablebox_long()
#     

```


<!-- NOT WORTH PLOTTING 
### Spillover Coefficient Plots

Figures: `figs/[TYPE]/m-spillover-[1:3].png`

1. diff-in-diff, at least one **new Senator** in the delegation effect
2. diff-in-diff, **proportion** of new legislators in the delegation effect **on Senators**

--> 


### Spillover Effect:

```{r}
#| layout-ncol: 2
#| fig-height: 4.5
#| fig-cap: "figs/[TYPE]/m-spillover-[1:3].png"
#| fig-subcap: 
#|   - "1"
#|   - "2"
#|   - "3"
#| out-width: "100%"
#| label: "m-spillover"
#| fig-show: "hold"


m_spillover <- fenegbin(perYear ~
  new_senator  | Year_x_Agency + District,
cluster = "District",
data = dcounts_spillover)

# coefplot(m_spillover, horiz = T, drop = "(Intercept)|.theta", sub = "") 

m_spillover_proportion <- fenegbin(perYear ~
  new_proportion  | Year_x_Agency + District,
cluster = "District",
data = dcounts_spillover |> filter(chamber == "Senate"))

# coefplot(m_spillover_proportion, horiz = T, drop = "(Intercept)|.theta", sub = "") 

m_spillover_new_one <- fenegbin(perYear ~
  new_one  | Year_x_Agency + District,
cluster = "District",
data = dcounts_spillover |> filter(chamber == "Senate"))

# coefplot(m_spillover_new_one, horiz = T, drop = "(Intercept)|.theta", sub = "") 

```


- Models: `models/models_spillover_negbin.Rdata`

```{r models_spillover}
models_spillover <- list(
  "(1)" = m_spillover,
  "(2)" = m_spillover_proportion,
  "(3)" = m_spillover_new_one
)

rows <- tibble(
  term = c("Dependent variable", 
           "All districts",
           "Senate only"),
  `(1)` = c("Count", 
            "X", 
            ""),
  `(2)` =c("Count", 
            "", 
           "X"),
    `(3)` = c("Count", 
            "", 
            "X")
)

# Check marks for controls 
attr(rows, 'position') <- c(0)

modelsummary(models_spillover ) 

save(models_spillover, rows, cm, gm,  # beta_cross, beta_did, se_cross, se_did,
     file = here::here("models", type, "models_spillover.Rdata"))
```

