
## - House staff-only %

- Figures: `figs/[TYPE]/m-staff-only-[1:4].png`

```{r m-staff-only}
#| fig-show: "hold"
#| out-width: "50%"
#| fig-height: 4.5
#| fig-cap: "Per Year"
#| fig-subcap: 
#|   - "Model 1: Cross Sectional"
#|   - "Model 2: Diff in Diff"
#|   - "Model 3: restricted Diff in Diff"
#|   - "Model 4: log Diff in Diff"



# cross-sectional 
m_staff_only_cross <- fenegbin (perYear ~ 
                         prop_legis_spending + prop_pol_spending + prop_comm_spending + prop_off_spending + prop_constit_spending +
                             
                     
                    majority + presidents_party | Year_x_Agency,
                    cluster = "Legislator", 
           data = data_member)

if(testing){modelsummary::modelsummary(m_staff_only_cross, gof_omit = "R.*", coef_omit = coef_omit)}

coefplot(m_staff_only_cross, horiz = T, drop = "(Intercept)") 



# 2
m_staff_only_did <-fenegbin (perYear ~ 
prop_legis_spending + prop_pol_spending + prop_comm_spending + prop_off_spending + prop_constit_spending +
                           
                     
  
                    majority + presidents_party  | Year_x_Agency + Legislator_x_Agency, 
                    cluster = "Legislator",
                    # ALT vcov = hetero ~ ssc(cluster.adj = TRUE),
           data = data_member)

if(testing){modelsummary::modelsummary(m_staff_only_did, gof_omit = "R.*", coef_omit = coef_omit)}

coefplot(m_staff_only_did, horiz = T, drop = ".theta") 


# 3
m_staff_only_2nd_cross <-fenegbin (perYear ~ 
prop_legis_spending + prop_pol_spending + prop_comm_spending + prop_off_spending + prop_constit_spending + 
                           
                    # 
                    majority + presidents_party | Year_x_Agency, 
                    cluster = "Legislator", 
           data = data_member %>% filter(survive == 1))

if(testing){modelsummary::modelsummary(m_staff_only_2nd_cross, gof_omit = "R.*", coef_omit = coef_omit)}
coefplot(m_staff_only_2nd_cross, horiz = T, drop = ".theta") 


# 4
m_staff_only_2nd_did <-fenegbin (perYear ~
   prop_legis_spending + prop_pol_spending + prop_comm_spending + prop_off_spending + prop_constit_spending + 
                            
                    #
                    majority + presidents_party | Year_x_Agency + Legislator_x_Agency,
                    cluster = "Legislator",
           data = data_member %>% filter(survive == 1))

if(testing){modelsummary::modelsummary(m_staff_only_2nd_did, gof_omit = "R.*", coef_omit = coef_omit)}

coefplot(m_staff_only_2nd_did, horiz = T, drop = ".theta")
```


### Table - Staff %

```{r m-staff-only-models}
models_staff_only <- list(
  "(1)" = m_staff_only_cross,
  "(2)" = m_staff_only_did,
  "(3)" =  m_staff_only_2nd_cross,
 "(4)" = m_staff_only_2nd_did
)

rows <- tibble(
  term = c("Dependent Variable", 
           #"Majority",
           #"President's Party",
           "All Representatives", 
           "Served At Least 2nd Term"),
  `(1)` = c("Count", "X", ""),
  `(2)` =c("Count", "X", ""),
  `(3)` = c("Count","", "X"),
  `(4)` = c("Count", "", "X") 
)

# subset
attr(rows, 'position') <- c(0, 20,21,22,23)

# call coefs
attr(rows, 'position') <- c(0)

options(modelsummary_factory_default = 'kableExtra')


# HTML
modelsummary(models_staff_only, 
             title = "The Effect of Experience and District Competitiveness on Legislator Contacts", 
             notes = list("Robust standard errors in parentheses, clustered by legislator."))

beta_cross <- betas(m_staff_only_cross)
se_cross <- standard_errors(m_staff_only_cross)
beta_did <- betas(m_staff_only_did)
se_did <- standard_errors(m_staff_only_did)
```


### Narrative - Staff %

TODO


### Modeled Effects - Staff % - cross sectional 

```{r}
#| label: "m-staff-only-effect"
#| fig-cap: "figs/[TYPE]/m-staff-only-effect"
#| layout-ncol: 2
#| fig-height: 3.5
#| fig-width: 3.5
#| fig-subcap: 
#|   - "1"
#|   - "2"
#| out-width: "100%"
#| fig-show: "hold"

model <- m_staff_only_cross
data = data_member |> filter(year > 2007,  year < 2019)

plot_effect( 
  newdata = mutate(data, prop_constit_spending = 0),
  effect = "%Constit. Serv. Budget"
  )

plot_effect( 
  newdata = mutate(data, prop_comm_spending = 0),
  effect = "%Comms Budget"
  )
```

### Modeled Effects - staff % - diff in diff

```{r}
#| label: "m-staff-only-did-effect"
#| fig-cap: "figs/[TYPE]/m-staff-only-did-effect"
#| layout-ncol: 2
#| fig-height: 3.5
#| fig-width: 3.5
#| fig-subcap: 
#|   - "1"
#| out-width: "100%"
#| fig-show: "hold"

model <- m_staff_only_did
data = data_member #|> filter(year > 2007,  year < 2019)

plot_effect( 
  newdata = mutate(data, prop_constit_spending = 0),
  effect = "%Constit. Serv. Budget\n(diff in diff)"
  )
```


\clearpage

## - House Staff Spending

Spending in Millions 

- Figures: `figs/[TYPE]/m-staff-only_spending-[1:4].png`

```{r m-staff-only_spending}
#| fig-show: "hold"
#| out-width: "50%"
#| fig-height: 4.5
#| fig-cap: "Per Year"
#| fig-subcap: 
#|   - "Model 1: Cross Sectional"
#|   - "Model 2: Diff in Diff"
#|   - "Model 3: restricted Diff in Diff"
#|   - "Model 4: log Diff in Diff"



# cross-sectional 
m_staff_only_spending_cross <- fenegbin (perYear ~ 
                         est_legis_spending + est_pol_spending + est_comm_spending + est_off_spending + est_constit_spending +
                             
                     
                    majority + presidents_party | Year_x_Agency,
                    cluster = "Legislator", 
           data = data_member)

if(testing){modelsummary::modelsummary(m_staff_only_spending_cross, gof_omit = "R.*", coef_omit = coef_omit)}

coefplot(m_staff_only_spending_cross, horiz = T, drop = "(Intercept)") 



# 2
m_staff_only_spending_did <-fenegbin (perYear ~ 
est_legis_spending + est_pol_spending + est_comm_spending + est_off_spending + est_constit_spending +
                           
                     
                    majority + presidents_party | Year_x_Agency + Legislator_x_Agency, 
                    cluster = "Legislator",
                    # ALT vcov = hetero ~ ssc(cluster.adj = TRUE),
           data = data_member)

if(testing){modelsummary::modelsummary(m_staff_only_spending_did, gof_omit = "R.*", coef_omit = coef_omit)}

coefplot(m_staff_only_spending_did, horiz = T, drop = ".theta") 


# 3
m_staff_only_spending_2nd_cross <-fenegbin (perYear ~ 
est_legis_spending + est_pol_spending + est_comm_spending + est_off_spending + est_constit_spending + 
                    majority + presidents_party | Year_x_Agency, 
                    cluster = "Legislator", 
           data = data_member %>% filter(survive == 1))

if(testing){modelsummary::modelsummary(m_staff_only_spending_2nd_cross, gof_omit = "R.*", coef_omit = coef_omit)}
coefplot(m_staff_only_spending_2nd_cross, horiz = T, drop = ".theta") 


# 4
m_staff_only_spending_2nd_did <-fenegbin (perYear ~
                                            est_legis_spending + 
                                            est_pol_spending + 
                                            est_comm_spending + 
                                            est_off_spending + 
                                            est_constit_spending + 
                                            majority + 
                                            presidents_party | 
                                            Year_x_Agency +
                                            Legislator_x_Agency,
                                          cluster = "Legislator",
                                          data = data_member %>% filter(survive == 1))

if(testing){modelsummary::modelsummary(m_staff_only_spending_2nd_did, gof_omit = "R.*", coef_omit = coef_omit)}

coefplot(m_staff_only_spending_2nd_did, horiz = T, drop = ".theta")
```


### Table - staff-only_spending

```{r m-staff-only_spending-models}
models_staff_only_spending <- list(
  "(1)" = m_staff_only_spending_cross,
  "(2)" = m_staff_only_spending_did,
  "(3)" =  m_staff_only_spending_2nd_cross,
 "(4)" = m_staff_only_spending_2nd_did
)

rows <- tibble(
  term = c("Dependent Variable", 
           #"Majority",
           #"President's Party",
           "All Representatives", 
           "Served At Least 2nd Term"),
  `(1)` = c("Count", "X", ""),
  `(2)` =c("Count", "X", ""),
  `(3)` = c("Count","", "X"),
  `(4)` = c("Count", "", "X") 
)

# subset
attr(rows, 'position') <- c(0, 20,21,22,23)

# call coefs
attr(rows, 'position') <- c(0)

options(modelsummary_factory_default = 'kableExtra')


# HTML
modelsummary(models_staff_only_spending, 
             title = "The Effect of Experience and District Competitiveness on Legislator Contacts", 
             notes = list("Robust standard errors in parentheses, clustered by legislator."))

beta_cross <- betas(m_staff_only_spending_cross)
se_cross <- standard_errors(m_staff_only_spending_cross)
beta_did <- betas(m_staff_only_spending_did)
se_did <- standard_errors(m_staff_only_spending_did)


save(models_staff_only_spending, rows, cm, gm,   beta_cross, beta_did, se_cross, se_did,
     file = here::here("models", type, "models_staff_only_spending.Rdata"))
```


### Narrative - staff-only_spending

TODO


### Modeled Effects - staff-only_spending - cross sectional 

```{r}
#| label: "m-staff-only_spending-effect"
#| fig-cap: "figs/[TYPE]/m-staff-only_spending-effect"
#| layout-ncol: 2
#| fig-height: 3.5
#| fig-width: 3.5
#| fig-subcap: 
#|   - "1"
#|   - "2"
#| out-width: "100%"
#| fig-show: "hold"

model <- m_staff_only_spending_cross
data = data_member |> filter(year > 2007,  year < 2019)

plot_effect( 
  newdata = mutate(data, est_constit_spending = 0),
  effect = "Constit. Serv. Budget"
  )

plot_effect( 
  newdata = mutate(data, est_comm_spending = 0),
  effect = "Comms Budget"
  )
```

### Modeled Effects - staff-only_spending - diff in diff

```{r}
#| label: "m-staff-only_spending-did-effect"
#| fig-cap: "figs/[TYPE]/m-staff-only_spending-did-effect"
#| layout-ncol: 2
#| fig-height: 3.5
#| fig-width: 3.5
#| fig-subcap: 
#|   - "1"
#| out-width: "100%"
#| fig-show: "hold"

model <- m_staff_only_spending_did
data = data_member #|> filter(year > 2007,  year < 2019)

plot_effect( 
  newdata = mutate(data, est_constit_spending = 0),
  effect = "Constit. Serv. Budget\n(diff in diff)"
  )
```

\clearpage
