# Type = `r type`

Required Packages: 
  
- `tidyverse` and `magrittr`, for data wrangling
- `scales` for plot scales 
- `ggrepel` for plot labels
- `here` for file paths 
- `knitr` for document formatting 
- `kableExtra` for table formatting 
- `modelsummary` for regression tables 
- `marginaleffects` for predictions 
- `fixest` --- a statistical package for fixed effects estimation 
- `ineq` to calculate GINI coefficients

```{r functions, cache=FALSE}
here::here("code", "qmd_global_options.R") |> source() 

# plotting functions 
here::here("code", "ggcompetitive.R") |> source() 
here::here("code", "ggchair.R") |> source() 
here::here("code", "ggtenure.R") |> source() 
here::here("code", "ggdistrict.R") |> source() 
here::here("code", "plot_effect.R") |> source() 

# coef map
here::here("code", "cm.R") |> source() 
here::here("code", "modelsummary_formatting.R") |> source()
```

```{r global.options, message=FALSE,warning=FALSE, purl=FALSE, cache=FALSE}
# load r packages and qmd render defaults 
here::here("code", "qmd_global_options.R") |> source() 
testing = F

# directory for figures from this analysis
dir.create(here::here("figs", type))
dir.create(here::here("models", type))
dir.create(here::here("tables", type))

knitr::opts_chunk$set(
  fig.path = paste0("figs/", type, "/")
  )
```

Figures at `r paste0("figs/", type, "/")`
Tables at `r paste0("tables/", type, "/")`
Models at `r paste0("models/", type, "/")`
Data at `r paste0("data/", type, "/")`

# Data

```{r data, cache=FALSE}
load(here::here("data", type, "dcounts.rds")) 
load(here::here("data", type, "dcounts_district.rds"))
load(here::here("data", type, "means.Rdata"))
load(here::here("data", "member_data.Rdata"))

# # Drop president and nonvoting members 
# #FIXME this should be done in replication-data.qmd  -- SHOULD BE FIXED NOW 
# dcounts %<>% drop_na(state)
# dcounts_district %<>% drop_na(state)
# member_data %<>% drop_na(state)
# 
# dcounts |> group_by(agency) |>
#   mutate(across(everything(), is.na)) |> 
#   summarise(across(everything(),  sum)) |> 
#   kablebox()
# 
# dcounts %>% group_by(agency) %>% 
#   summarise(total_per_agency = sum(perYear)) 
# 
# # drop uncoded agencies
# dcounts %<>% group_by(agency) %>% 
#   mutate(total_per_agency = sum(perYear)) %>% 
#   filter(total_per_agency > 2)
# 
# # drop uncoded agencies
# dcounts_district %<>% group_by(agency) %>% 
#   mutate(total_per_agency = sum(perYear)) %>% 
#   filter(total_per_agency > 2)
```

```{r transformations, cache=FALSE}
data_member <- dcounts |> mutate(type = type)
data_district <- dcounts_district |> mutate(type = type)

rename_vars <- function(data){
  data <- data |> 
  mutate(same_party = as.numeric(same_party),
         pop2010m = pop2010/1000000,
         Legislator = icpsr,
         District = state_dist,
         Year = year,
         first_two = first + second, 
         experience = ifelse(first_two == 1, 0, 1),
         distance = abs(nominate_dim1 - agency_ideo),
    # fixed effects 
    icpsr_agency = paste(agency, icpsr, sep='_'),
    agency_year = paste(agency, year, sep='_'),
    Year_x_Agency = agency_year,
    Legislator_x_Agency = icpsr_agency)
  
  return(data)
}

data_member <- rename_vars(data_member) 
data_district <- rename_vars(data_district)
```


```{r}
#| label: "percentile"
#| fig-cap: "figs/[TYPE]/percentile-[1:2].png"
#| layout-ncol: 2
#| fig-height: 3.5
#| fig-width: 3.5
#| fig-subcap: 
#|   - "1"
#|   - "2"
#| out-width: "100%"
#| fig-show: "hold"

here::here("code", "percentile_plot.R") |> source()

plot_data(d = data_member |> filter(chamber == "Senate"))
plot_data(d = data_member |> filter(chamber == "House"))
```


### Gini coefficients 

```{r gini}
gini <- data_member |> 
  ungroup() |> 
  group_by(year, icpsr) |> 
  summarize(perYear = sum(perYear)) |> 
  ungroup() |> 
group_by(year) |> 
  summarise(gini = round(ineq::Gini(perYear),2)) |>
  arrange(- year) |> 
  filter(year > 2006) 

gini|> 
  kablebox()

gini |> 
  ggplot() +
  aes( x = year, y = gini) + 
  geom_point() + 
  geom_smooth(method = "lm")

gini_min <- min(gini$gini)
gini_max <- max(gini$gini)


gini2 <- data_member |> 
  ungroup() |> 
  group_by(year, chamber, icpsr) |> 
  summarize(perYear = sum(perYear)) |> 
  ungroup() |> 
group_by(year, chamber) |> 
  summarise(gini = round(ineq::Gini(perYear),2)) |>
  arrange(- year) |> 
  filter(year > 2006) 

gini2|> 
  kablebox()

gini2 |> 
  ggplot() +
  aes( x = year,
       y = gini, 
       color = chamber) + 
  geom_point() 
  #geom_smooth(method = "lm")
  

gini %<>% filter(year > 2017)

min(gini$gini)
max(gini$gini)
```




In 2023, Colombia had the highest income inequality Gini coefficient at .54. 

https://ourworldindata.org/what-is-the-gini-coefficient

Top 10 Gini Coefficients in 2023

1. Colombia	0.54
1. Brazil	0.52	
1. Zambia	0.51
1. Angola	0.51				
1. Mozambique	0.50	
1. Zimbabwe	0.50
1. Kosovo	0.49
1. Panama	0.49
1. Honduras	0.47	
1. Costa Rica	0.47

<!--(The Gini coefficient for House campaign spending in 2016 was .29).  --> 


## Values for Predictions

The most frequent legislator agency pair: McCain x VA with 2159 letters!

The average is  `r perYear_mean` letters per legislator per year, `r mean` letters per agency per year.
For predictions, we need an average member-year-agency triad. The first table below shows the members who averaged  `r perYear_mean`, entered Congress between 2007 and 2011, were observed in our data for at least seven years, and most often submitted exactly one letter to an agency (the closest integer  `r perYear_mean` ). For realism, this person would ideally become a chair at some point in our data. 

:::{.callout-warning}
In the figures below, uncertainty intervals around predictions do not include uncertainty in the estimates of the fixed effects. This is because the standard errors returned by marginaleffects::predictions() do not reflect uncertainty in the fixed effect estimation. Since we are just using predictions to illustrate the effects of interest, not make any claims about particular years, legislators, or agencies (the fixed effects), the uncertainty in the fixed effect estimates is not relevant for our use case (illustrating main effects, for which we do have estimates of uncertainty). However, we wish to alert users of these code that they should not use the predictions to make such claims. 

For further discussion, see [this discussion](https://github.com/vincentarelbundock/marginaleffects/issues/1487) that led the authors of the marginaleffects package to [stop](https://marginaleffects.com/bonus/NEWS_r.html#section) allowing users to calculate predictions for fixed effects models (due to their potential misuses and possible differences from uncertianty bounds that do include uncertianty related to the estimation of fixed effects).
:::

<!--
Of the modal legislators, 
John Barrasso and
Phil Roe 
meet this last criterion. However, whereas Barrasso's seat was always held by a Republican, Roe's seat flipped, adding realism to our predictions from models that include whether a legislator is replacing a co-partisan or not. 
Roe entered in 2009 and became a chair in 2017.
The IRS is a fairly modal agency, so predictions are Phil Roe X Treasury IRS X 2015. 
Other legislators, years, and agencies are simply intercept shifts. 
--> 

### Modal agencies

```{r modal-agencies}
 data_member %>% 
 group_by(agency, year) %>% 
  summarise(perAgency = sum(perYear),
            agency_ideo = mean(agency_ideo)) %>% 
  ungroup() %>% 
  mutate(median = median(perAgency),
         diff = abs(perAgency - median)) %>% 
  arrange(diff) %>% 
  drop_na(agency_ideo) %>% 
  kablebox()
```


### Modal legislators

```{r modal-legislators}
modal <- data_member %>% 
  group_by(icpsr) %>% 
  filter(first_year > 2006, first_year < 2013,  max_year > 6) %>% 
  mutate(Chair = sum(chair, na.rm = T) >1) %>% 
  group_by(icpsr, year) %>%
  mutate(perLeg = sum(perYear)) %>% 
  filter(perYear == 1, perLeg == perYear_mean  ) %>% 
  select(perAgency = perYear, 
         congress,
         perLeg, 
         agency, bioname, 
           Legislator_x_Agency,
                        Year_x_Agency,
                        Legislator,
                        Year, first_year, max_year, Chair) %>% 
  distinct() %>% 
  ungroup() %>% 
  left_join(member_data %>% select(bioname, icpsr, congress))


modal %>%
  mutate(average = perLeg) %>% 
  count(average, bioname, first_year, max_year, Chair, sort = T, name = "agency_year_count == 1") %>% 
  distinct() %>%
  arrange(-Chair) %>%
  kablebox()
```

### Modal legislator-agency pairs

```{r values, fig.width=5, fig.height=3}

modal %<>% filter(Chair) %>% distinct()

modal %>%
  kablebox()

data_member %>% 
  group_by(icpsr, year) %>% 
  mutate(perYearleg = sum(perYear)) %>%
  #mutate (perLegislator = sum(perYear)) %>% 
  ungroup() %>% 
  mutate(meanLeg = mean(perYearleg),
         meanYear = mean(perYear)) %>%
  filter( abs(perYearleg - perYear_mean) < 10,   
          perYear < 10 )  %>% 
  drop_na(agency_ideo) %>% 
  ggplot() +
  aes(x = perYear, 
      y = perYearleg) + 
  geom_jitter(alpha = .5) + 
  geom_vline(aes(xintercept = meanYear), color = "blue") + 
  geom_hline(aes(yintercept = meanLeg), color = "blue") + 
  geom_text_repel(
    aes( label = ifelse(icpsr_agency %in% modal$Legislator_x_Agency & agency_year %in% modal$Year_x_Agency , 
                     icpsr_agency, 
                     NA)  ),
    color = "red", 
    box.padding = 0.5, 
    max.overlaps = Inf
    ) + 
  labs(x = "Contacts per Legislator per Agency per year",
       y = "Contacts per Legislator per year") + 
  scale_x_continuous(breaks = seq.int(0, 9, length.out =  10))

modal %>%
  ungroup() %>% 
  distinct(agency, perAgency, bioname, 
           Legislator_x_Agency,
                        Year_x_Agency,
                        Legislator,
                        Year) %>% 
  kablebox()


# modal pair  
n <- 1 

# by chair and President's party
values <- tidyr::expand(data_member,
                        chair = chair, 
                        oversight = 0,
                        distance = data_member$distance |> mean(na.rm = T),
                        ranking_minority	= FALSE, 
                        prestige = TRUE, 
                        competitive = FALSE,
                        competitive_primary = FALSE,
                        experience = 1, 
                        first = FALSE,
                        second = FALSE,
                        third = FALSE,
                        fourth = FALSE,
                        fifth = FALSE, 
                        sixth = FALSE,
                        agency =  modal$agency[n],
                        Legislator_x_Agency = modal$Legislator_x_Agency[n],
                        Year_x_Agency = modal$Year_x_Agency[n],
                        Legislator =  modal$Legislator[n],
                        Year =  modal$year[n],
                        majority = TRUE,
                        presidents_party = presidents_party
                   ) %>% 
  drop_na(majority, chair)

# by year 
values_tenure <- tidyr::expand(data_member,
                        chair = chair, 
                        oversight = 0,
                                                distance = data_member$distance |> mean(na.rm = T),
                        ranking_minority	= FALSE, 
                        prestige = TRUE, 
                        competitive = FALSE,
                        competitive_primary = FALSE,
                        experience = experience, 
                        # first = first,
                        # second = second,
                        # third = third,
                        # fourth = fourth,
                        # fifth = fifth, 
                        # sixth = sixth,
                        agency =  modal$agency[n],
                        Legislator_x_Agency = modal$Legislator_x_Agency[n],
                        Year_x_Agency = modal$Year_x_Agency[n],
                        Legislator =  modal$Legislator[n],
                        Year =  modal$year[n],
                        majority = TRUE,
                        presidents_party = TRUE
                   ) %>% 
  drop_na(chair)
```


# Model Results: Counts per member per year

Clustering standard errors at the legislator level:

["Clustering on the panel variable produces an estimator of the VCE that is robust to cross-sectional heteroskedasticity and within-panel (serial) correlation that is asymptotically equivalent to that proposed by Arellano (1987)"](https://www.stata.com/manuals13/xtxtreg.pdf)

We use `fixest::fenegbin` here and replicated the main models using `xtreg` in Replication.do.
See more about how robust (clustered) standard errors with fixed effects are calculated by `fixest` [here](https://lrberge.github.io/fixest/articles/standard_errors.html) and by  `xtreg` [here](https://www.stata.com/manuals13/xtxtreg.pdf).


---

## Letters 

### Member-level Coefficient Plots

- Figures: `figs/[TYPE]/m-[1:4].png`

```{r}
#| label: "m"
#| fig-cap: "figs/[TYPE]/m-[1:4].png"
#| layout-ncol: 2
#| fig-height: 4.5
#| fig-subcap: 
#|   - "1"
#|   - "2"
#|   - "3"
#|   - "4"
#| out-width: "100%"
#| fig-show: "hold"


# cross-sectional 
m_cross <-fenegbin (perYear ~ 
                         chair + ranking_minority + prestige + oversight +
                    experience + 
                    majority + presidents_party | Year_x_Agency,
                    cluster = "Legislator", 
           data = data_member)

# data_member |> count(is.na(presidents_party))


if(testing){modelsummary::modelsummary(m_cross)}

coefplot(m_cross, horiz = T, drop = "(Intercept)|.theta") 



# 2
m_did <-fenegbin (perYear ~ 
                       chair + ranking_minority + prestige + oversight +  
                    experience + 
                    majority + presidents_party | Year_x_Agency + Legislator_x_Agency, 
                    cluster = "Legislator",
                    # ALT vcov = hetero ~ ssc(cluster.adj = TRUE),
           data = data_member)

if(testing){modelsummary::modelsummary(m_did)}

coefplot(m_did, horiz = T, drop = ".theta") 


# 3
m_2nd <-fenegbin (perYear ~ 
                       chair + ranking_minority + prestige + oversight +  
                    #experience + 
                    majority + presidents_party | Year_x_Agency, 
                    cluster = "Legislator", 
           data = data_member %>% filter(survive == 1))

if(testing){modelsummary::modelsummary(m_2nd)}
coefplot(m_2nd, horiz = T, drop = ".theta") 

```

###  Table 

- Models: `models/models_negbin.Rdata` 


```{r models}
models <- list(
  "(1)" = m_cross,
  "(2)" = m_did,
  "(3)" =  m_2nd#,
  #"(4)" = m_log_did
)

rows <- tibble(
  term = c("Dependent variable", 
           "Majority",
           "President's party",
           "All legislators", 
           "Served at least 2nd term"),
  `(1)` = c("Count", "X", "X", "X", ""),
  `(2)` =c("Count", "X", "X", "X", ""),
  `(3)` = c("Count", "X","X","", "X")#,
  #`(4)` = c("Log(Count+1)","X","X", "X", "") 
)

rows <- tibble(
  term = c("Dependent variable", 
           #"Majority",
           #"President's party",
           "All legislators", 
           "Served at least 2nd term"),
  `(1)` = c("Count", "X", ""),
  `(2)` =c("Count", "X", ""),
  `(3)` = c("Count","", "X")#,
 # `(4)` = c("Log(Count+1)", "X", "") 
)

attr(rows, 'position') <- c(0, 20,21,22,23)

attr(rows, 'position') <- c(0)


# HTML
modelsummary(models)


if(testing){
rows <- tibble(
  term = c("Dependent variable"),
  `(1)` = c("Count"),
  `(2)` =c("Count"),
  `(3)` = c("Count")#,
  #`(4)` = c("Log(Count+1)") 
)

attr(rows, 'position') <- c(0)


modelsummary::modelsummary(models,  
             add_rows = rows,     
             notes = "") 
}
```


###  Predictions 

- Figures: `figs/[TYPE]/m-predicted-[1:4].png`


```{r}
#| label: "m-predicted"
#| fig-cap: "figs/[TYPE]/m-predicted"
#| layout-ncol: 2
#| fig-height: 3
#| fig-subcap: 
#|   - "1"
#|   - "2"
#|   - "3"
#|   - "4"
#| out-width: "100%"
#| fig-show: "hold"

predicted <- predictions(m_cross,
                         newdata = values)

# Cross-sectional predictions
predicted %>%
    mutate(estimate = estimate*n_agency, 
         conf.high = conf.high*n_agency, conf.low = conf.low*n_agency) %>%  
  ggchair() + 
  labs(title =  "", # "Predicted  per year",        subtitle = "(cross-sectional)",
       x = "",
       y = "Predicted per year",
       fill = "",
       color = "",
       shape = "") 

# by tenure
predicted <- predictions(m_cross,
                         newdata = values_tenure)

predicted %>%
    mutate(estimate = estimate*n_agency, 
         conf.high = conf.high*n_agency, conf.low = conf.low*n_agency) %>% 
ggtenure() +
  labs(title =  "", # "Predicted per year",        subtitle = "(cross-sectional)",
       x = "Years serving in Congress",
       y = "      Predicted letters per year",
       fill = "",
       color = "",
       shape = "") 


# diff in diff 
predicted <- predictions(m_did,
                         newdata = values)


# Predictions by Chair and President's Party
predicted %>%
    mutate(estimate = estimate*n_agency, #predicted*n_agency,
         conf.high = conf.high*n_agency, conf.low = conf.low*n_agency) %>% # std.error = std.error*n_agency)) %>%
  ggchair() + 
  labs(title =  "", # "Predicted per year\nDifference in Differences (Within-Legislator)",
       x = "",
       y = "  Predicted letters per year",
       fill = "",
       color = "",
       shape = "") 

# by tenure
predicted2 <- predictions(m_did,
                         newdata = values_tenure)

predicted2 %>%
    mutate(estimate = estimate*n_agency, #predicted*n_agency,
         conf.high = conf.high*n_agency, conf.low = conf.low*n_agency) %>%  # std.error = std.error*n_agency) %>%
ggtenure() +
    #geom_line(aes(x = as.numeric(year_in_congress %>% str_sub(1,1) %>% str_replace("N", "1")))) + 
  labs(title =  "", # "Predicted per year\nDifference in Differences (Within-Legislator)",
       x = "Years serving in Congress",
       y = "  Predicted letters per year",
       fill = "",
       color = "",
       shape = "") 
```

### Modeled Effects 

```{r}
#| label: "m-effect"
#| fig-cap: "figs/[TYPE]/m-effect"
#| layout-ncol: 2
#| fig-height: 3.5
#| fig-width: 3.5
#| fig-subcap: 
#|   - "1"
#|   - "2"
#|   - "3"
#|   - "4"
#| out-width: "100%"
#| fig-show: "hold"

model <- m_cross
data = data_member |> filter(year > 2007,  year < 2019)

plot_effect( 
  newdata = mutate(data, chair = 0),
  effect = "Chair"
  )

plot_effect( 
  newdata = mutate(data, ranking_minority = 0),
  effect = "Ranking Minority"
  )

plot_effect( 
  newdata = mutate(data, prestige = 0),
  effect = "Prestige Committee"
  )

plot_effect( 
  newdata = mutate(data, oversight = 0),
  effect = "Oversight Committee"
  )

plot_effect( 
  newdata = mutate(data, experience = 0),
  effect = "3+ years in office"
  )

plot_effect( 
  newdata = mutate(data, majority = 0),
  effect = "Majority"
  )

plot_effect( 
  newdata = mutate(data, presidents_party = 0),
  effect = "President's party"
  )

plot_effect( 
  newdata = mutate(data, chair = 0,
                            ranking_minority = 0,
                            # oversight = 0,
                            #prestige = 0,
                            experience = 0),
  effect = "Total capacity"
  )
```


### Modeled Effects - diff in diff

```{r}
#| label: "m-did-effect"
#| fig-cap: "figs/[TYPE]/m-did-effect"
#| layout-ncol: 2
#| fig-height: 3.5
#| fig-width: 3.5
#| fig-subcap: 
#|   - "1"
#|   - "2"
#|   - "3"
#|   - "4"
#| out-width: "100%"
#| fig-show: "hold"

model <- m_did

data = data_member |> filter(year > 2007,  year < 2019)

plot_effect( 
  newdata = mutate(data, chair = 0),
  effect = "Chair (diff in diff)"
  )

plot_effect( 
  newdata = mutate(data, ranking_minority = 0),
  effect = "Ranking minority (diff in diff)"
  )

plot_effect( 
  newdata = mutate(data, prestige = 0),
  effect = "Prestige committee (diff in diff)"
  )

plot_effect( 
  newdata = mutate(data, oversight = 0),
  effect = "Oversight committee (diff in diff)"
  )

plot_effect( 
  newdata = mutate(data, experience = 0),
  effect = "3+ years in office (diff in diff)"
  )

plot_effect( 
  newdata = mutate(data, majority = 0),
  effect = "Majority (diff in diff)"
  )

plot_effect( 
  newdata = mutate(data, presidents_party = 0),
  effect = "President's party (diff in diff)"
  )

plot_effect( 
  newdata = mutate(data, chair = 0,
                            ranking_minority = 0,
                            # oversight = 0,
                            # prestige = 0,
                            experience = 0),
  effect = "Total capacity (diff in diff)"
  )
```


---

## - House

### Member-level Coefficient Plots - House

- Figures: `figs/[TYPE]/m-house-[1:4].png`

```{r}
#| label: "m-house"
#| fig-cap: "figs/[TYPE]/m-house-[1:4].png"
#| layout-ncol: 2
#| fig-height: 4.5
#| fig-subcap: 
#|   - "1"
#|   - "2"
#|   - "3"
#|   - "4"
#| out-width: "100%"
#| fig-show: "hold"

# cross-sectional 
m_cross_house <-fenegbin (perYear ~ 
                         chair + ranking_minority + prestige + oversight +  
                    experience + # first + second + third + fourth + fifth + sixth  + 
                    majority + presidents_party | Year_x_Agency,
                    cluster = "Legislator", 
           data = data_member |> filter(chamber=="House"))

if(testing){modelsummary::modelsummary(m_cross_house)}

coefplot(m_cross_house, horiz = T, drop = "(Intercept)|.theta") 



# Model 2
m_did_house <-fenegbin (perYear ~ 
                       chair + ranking_minority + prestige + oversight +  
                    experience + 
                    majority + presidents_party | Year_x_Agency + Legislator_x_Agency, 
                    cluster = "Legislator",
                    # ALT vcov = hetero ~ ssc(cluster.adj = TRUE),
           data = data_member |> filter(chamber=="House"))

if(testing){modelsummary::modelsummary(m_did_house)}

coefplot(m_did_house, horiz = T, drop = ".theta") 


# 3
m_2nd_house <-fenegbin (perYear ~ 
                       chair + ranking_minority + prestige + oversight +  
                    # experience + 
                    majority + presidents_party | Year_x_Agency , 
                    cluster = "Legislator", 
           data = data_member |> filter(survive == 1)  |> filter(chamber=="House"))

if(testing){modelsummary::modelsummary(m_2nd_house)}
coefplot(m_2nd_house, horiz = T, drop = ".theta") 


# # 4
# m_log_did_house <-fenegbin (log(perYear + 1) ~ 
#                           chair + ranking_minority + prestige + oversight +  
#                     experience + 
#                     majority + presidents_party | Year_x_Agency + Legislator_x_Agency, 
#                     cluster = "Legislator", 
#            data = data_member |> filter(chamber=="House"))
# 
# if(testing){modelsummary::modelsummary(m_log_did_house)}
# 
# coefplot(m_log_did_house, horiz = T, drop = ".theta") 


```


### Modeled Effects - House

```{r}
#| label: "m-house-effect"
#| fig-cap: "figs/[TYPE]/m-house-effect"
#| layout-ncol: 2
#| fig-height: 3.5
#| fig-width: 3.5
#| fig-subcap: 
#|   - "1"
#|   - "2"
#|   - "3"
#|   - "4"
#| out-width: "100%"
#| fig-show: "hold"

model <- m_cross_house
data = data_member |> filter(year > 2007,  year < 2019)

plot_effect( 
  newdata = mutate(data, chair = 0),
  effect = "Chair"
  )

plot_effect( 
  newdata = mutate(data, ranking_minority = 0),
  effect = "Ranking Minority"
  )

plot_effect( 
  newdata = mutate(data, prestige = 0),
  effect = "Prestige Committee"
  )

plot_effect( 
  newdata = mutate(data, oversight = 0),
  effect = "Oversight Committee"
  )

plot_effect( 
  newdata = mutate(data, experience = 0),
  effect = "3+ years in office"
  )

plot_effect( 
  newdata = mutate(data, majority = 0),
  effect = "Majority"
  )

plot_effect( 
  newdata = mutate(data, presidents_party = 0),
  effect = "President's party"
  )

plot_effect( 
  newdata = mutate(data, chair = 0,
                            ranking_minority = 0,
                            # oversight = 0,
                            # prestige = 0,
                            experience = 0),
  effect = "Total capacity"
  )
```


## - Senate

### Member-level Coefficient Plots - Senate

- Figures: `figs/[TYPE]/m-senate-[1:4].png`

```{r}
#| label: "m-senate"
#| fig-cap: "figs/[TYPE]/m-senate-[1:4].png"
#| layout-ncol: 2
#| fig-height: 4.5
#| fig-subcap: 
#|   - "1"
#|   - "2"
#|   - "3"
#|   - "4"
#| out-width: "100%"
#| fig-show: "hold"

# cross-sectional 
m_cross_senate <-fenegbin (perYear ~ pop2010m + 
                         chair + ranking_minority + prestige + oversight +  
                    experience + # first + second + third + fourth + fifth + sixth  + 
                    majority + presidents_party | Year_x_Agency,
                    cluster = "Legislator", 
           data = data_member |> filter(chamber=="Senate"))

if(testing){modelsummary::modelsummary(m_cross_senate)}

coefplot(m_cross_senate, horiz = T, drop = "(Intercept)|.theta") 



# Model 2
m_did_senate <-fenegbin (perYear ~ 
                       chair + ranking_minority + prestige + oversight +  
                    experience + 
                    majority + presidents_party | Year_x_Agency + Legislator_x_Agency, 
                    cluster = "Legislator",
                    # ALT vcov = hetero ~ ssc(cluster.adj = TRUE),
           data = data_member |> filter(chamber=="Senate"))

if(testing){modelsummary::modelsummary(m_did_senate)}

coefplot(m_did_senate, horiz = T, drop = ".theta") 


# 3
m_2nd_senate <-fenegbin (perYear ~
                       chair + ranking_minority + prestige + oversight +  
                    #experience + 
                    majority + presidents_party | Year_x_Agency , 
                    cluster = "Legislator", 
           data = data_member |> filter(survive == 1)  |> filter(chamber=="Senate"))

if(testing){modelsummary::modelsummary(m_2nd_senate)}
coefplot(m_2nd_senate, horiz = T, drop = ".theta") 


# # 4
# m_log_did_senate <-fenegbin (log(perYear + 1) ~ 
#                           chair + ranking_minority + prestige + oversight +  
#                     experience + 
#                     majority + presidents_party | Year_x_Agency + Legislator_x_Agency, 
#                     cluster = "Legislator", 
#            data = data_member |> filter(chamber=="Senate"))
# 
# if(testing){modelsummary::modelsummary(m_log_did_senate)}
# 
# coefplot(m_log_did_senate, horiz = T, drop = ".theta") 


```

### Modeled Effects - Senate 

m-senate

```{r}
#| label: "m-senate-effect"
#| fig-cap: "figs/[TYPE]/m-senate-effect"
#| layout-ncol: 2
#| fig-height: 3.5
#| fig-width: 3.5
#| fig-subcap: 
#|   - "1"
#|   - "2"
#|   - "3"
#|   - "4"
#| out-width: "100%"
#| fig-show: "hold"

data_member %<>% ungroup()

model <- m_cross_senate
data = data_member |> filter(chamber=="Senate") |> filter(year > 2007,  year < 2019)

plot_effect( 
  newdata = mutate(data, pop2010m = min(data_member$pop2010m) ),
  effect = "State population"
  )

plot_effect( 
  newdata = mutate(data, chair = 0),
  effect = "Chair"
  )

plot_effect( 
  newdata = mutate(data, ranking_minority = 0),
  effect = "Ranking minority"
  )

plot_effect( 
  newdata = mutate(data, prestige = 0),
  effect = "Prestige committee"
  )

plot_effect( 
  newdata = mutate(data, oversight = 0),
  effect = "Oversight committee"
  )

plot_effect( 
  newdata = mutate(data, experience = 0),
  effect = "3+ years in office"
  )

plot_effect( 
  newdata = mutate(data, majority = 0),
  effect = "Majority"
  )

plot_effect( 
  newdata = mutate(data, presidents_party = 0),
  effect = "President's party"
  )

plot_effect( 
  newdata = mutate(data, chair = 0,
                            ranking_minority = 0,
                            # oversight = 0,
                            # prestige = 0,
                            experience = 0),
  effect = "Total capacity"
  )
```

{{< include code/replication-demand.qmd >}}

{{< include code/replication-workers.qmd >}}

{{< include code/replication-staff.qmd >}}

{{< include code/replication-staff-only.qmd >}}

{{< include code/replication-elect.qmd >}}

{{< include code/replication-ideology.qmd >}}



# Model Results: Per District

## Data

<!--
#TODO deal with chamber switchers ? or maybe we don't need to since everything is calculated grouped at chamber level?
# count(member_data, bioname, icpsr, congress, sort = T) |> filter(n >1)
-->

The main district-level models in the paper focus on estimating the effect of legislator experience by leveraging turnover within districts. We compare the service that a district receives before and after electing a new legislator and in the following years as legislators gain experience in office.

```{r add-crosswalk}
data_district |> 
  count(same_party) |> 
  kablebox()

# data_district |> filter(chamber == "House") |>   select(icpsr, state_dist, year, state_dist_party, lag_p, same_party, new_member)   |> kablebox()

data_district %<>% mutate(same_party = as.numeric(same_party))
```

{{< include code/replication-district.qmd >}}



# Manuscript models 

## Table 1:  Environment 



## Table 1: Overall + House and Senate

"models.Rdata"

```{r paper-models}
models <- list(
  "(1)" = m_cross,
  "(2)" = m_did,
  "(3)" =  m_cross_house,
  "(4)" = m_did_house,
   "(5)" =  m_cross_senate,
  "(6)" = m_did_senate
)

rows <- tibble(
  term = c("Dependent variable", 
           "All legislators", 
           "Only House",
           "Only Senate"),
  `(1)` = c("Count", "X", "", ""),
  `(2)` =c("Count", "X", "", ""),
  `(3)` = c("Count","", "X", ""),
    `(4)` = c("Count", "", "X", ""),
  `(5)` =c("Count", "","","X"),
  `(6)` = c("Count","","", "X")
  )

attr(rows, 'position') <- c(0)

modelsummary(models) 

beta_did <- betas(m_did)
se_did <- standard_errors(m_did)
beta_cross <- betas(m_cross)
se_cross <- standard_errors(m_cross)

save(models, rows, cm, gm,   beta_cross, beta_did, se_cross, se_did,
     file = here::here("models", type, "models.Rdata"))
```

## Table 2: Staff 


"models_staff_spending.Rdata"
"models_staff_only_spending.Rdata"

```{r}
models_staff <- list(
  "(1)" = m_staff_only_spending_cross,
  "(2)" = m_staff_only_spending_did,
  "(3)" =  m_staff_spending_cross,
  "(4)" = m_staff_spending_did
)

rows <- tibble(
  term = c("Dependent variable"),
  `(1)` = c("Count"),
  `(2)` =c("Count"),
  `(3)` = c("Count"),
  `(4)` =c("Count")
  )

attr(rows, 'position') <- c(0)

modelsummary(models_staff)

beta_did <- betas(m_staff_only_spending_did)
se_did <- standard_errors(m_staff_only_spending_did)
beta_cross <- betas(m_staff_only_spending_cross)
se_cross <- standard_errors(m_staff_only_spending_cross)

save(models_staff, rows, cm, gm,   beta_cross, beta_did, se_cross, se_did,
     file = here::here("models", type, "models_staff.Rdata"))
```


## Table 3: District + Same Party 

"models_district.Rdata"

```{r}
models_district <- list(
  "(1)" = m_district_cross,
  "(2)" = m_district_did,
  "(3)" =  m_district_cross_party,
  "(4)" = m_district_did_party
)

rows <- tibble(
  term = c("Dependent variable"),
  `(1)` = c("Count"),
  `(2)` =c("Count"),
  `(3)` = c("Count"),
  `(4)` =c("Count")
  )

attr(rows, 'position') <- c(0)

modelsummary(models_district)

beta_did <- betas(m_district_did)
se_did <- standard_errors(m_district_did)
beta_cross <- betas(m_district_cross)
se_cross <- standard_errors(m_district_cross)

save(models_district, rows, cm, gm,   beta_cross, beta_did, se_cross, se_did,
     file = here::here("models", type, "models_district.Rdata"))
```

## Table 3: Electoral motivations 

"models_elect.Rdata"

```{r}
models_elect <- list(
  "(1)" = m_elect_cross,
  "(2)" = m_elect_did,
   "(3)" =  m_elect_2nd_cross,
   "(4)" = m_elect_2nd_did
  #  "(3)" =  m_elect_cross_senate,
  # "(4)" = m_elect_did_senate
)

rows <- tibble(
  term = c("Dependent variable", "Served At Least 2nd Term"),
  `(1)` = c("Count", ""),
  `(2)` =c("Count", ""),
  `(3)` = c("Count","X"),    
  `(4)` = c("Count", "X")
  # `(5)` =c("Count", "","","X"),
  # `(6)` = c("Count","","", "X")
  )


attr(rows, 'position') <- c(0)


# HTML
modelsummary(models_elect,
             notes = list("Robust standard errors in parentheses, clustered by legislator.") ) 

beta_cross <- betas(m_elect_cross)
se_cross <- standard_errors(m_cross)
beta_did <- betas(m_elect_did)
se_did <- standard_errors(m_did)


save(models_elect, rows, cm, gm,  beta_cross, beta_did, se_cross, se_did,
     file = here::here("models", type, "models_elect.Rdata"))
```


## Table 4: Ideological motivations 

 "models_ideo.Rdata"

```{r}
models_ideo <- list(
  "(1)" = m_ideo_cross,
  "(2)" = m_ideo_2nd_cross
)

rows <- tibble(
  term = c("Dependent variable"),
  `(1)` = c("Count"),
  `(2)` = c("Count")
)

attr(rows, 'position') <- c(0)

modelsummary(models_ideo) 

beta_cross <- betas(m_ideo_cross)
se_cross <- standard_errors(m_ideo_cross)

save(models_ideo, rows, cm, gm,   beta_cross, se_cross,
     file = here::here("models", type, "models_ideo.Rdata"))
```

