---
title: "wordclouds"
format: html
---

```{r data}
# install.packages(c(
#   "tidyverse", "tidytext", "ggwordcloud", "here", "fs", "scales"
# ))

library(tidyverse)
library(tidytext)
library(ggwordcloud)
library(here)
library(fs)
library(scales)
library(magrittr)

# The minimal count data
here::here("data", "all_contacts.rda") |>
  str_replace("cor-book", "correspondence_data") |> load()

names(all_contacts)


d <- all_contacts |> select(agency, year, SUBJECT, TYPE, party_name) |> filter(agency != "DHS_USCIS")

d
```


Below is a reusable workflow using **tidytext + ggwordcloud**. It will create:
  
  1. One PNG with **one word cloud per year**
  2. One PNG per **agency**, faceted by year  
`figs/wordcloud/by-agency/[agency].png`
3. One PNG per **party**, faceted by year
4. One PNG per **agency-party combination**, faceted by year



## 1. Tokenize and count words

This converts `SUBJECT` into words, removes stop words, and counts words by `agency`, `year`, and `party_name`.

```{r}
custom_stop <- c(
  unique(d$agency) |> str_split("_") |> unlist(), "ferc", "ferc's", "fda's", "cdc", "cdc's", "dhs", "hhs", "cms", #"cder",
  "medicare", "health", "homeland", "security", "support", "america",
  unique(d$agency) |> str_split("_") |> unlist() |> str_to_lower(), 
  state.name,
  state.name |> str_to_lower() |> str_split(" |-") |> unlist(),
  unique(members$last_name) |> str_split(" |-") |> unlist(),
  unique(members$first_name),
  unique(members$last_name) |> str_split(" |-") |> unlist() |> str_to_lower(),
  unique(members$first_name)|> str_to_lower(),
  # Add dataset-specific filler terms here if they dominate too much
  "request", "requests", "requesting", "requested", "forwards", "behalf", "letter", "email", # "question", "constituent", "case", "follow", "up",
  "writes", "write", "writing", "written", "submitted", "comments", "signers", "summary", "subject", "correspondence", "inquiry", "contact", "expressing", "express", "concern", "concerns", "ltr", "concerned", "encourages", "urges", "urging",
  "issue", "issues", "staff", "related", "official", "response", "inquiry", "director", "secretary", "congress", "federal","cosigner","cosigners", "lots", "feels", "cmsy", "info",
  "prep", "sig", "closed", "owner", "recently", "multi", "called", "incoming", "communication", "sending", "letters", "wrote", "responder",
  "department", "national", "u.s.", "u.s","office",  "dept", "americorps",
  "rep", "reps", "sens", "sen", "senator", "senators", "senate", "house", "agency", "position",
  "honorable", "representative", "representatives", 
  "congressman", "congressional", "cong", "committee", "cmte", "staffer", "potus", "secy",
)

subject_words <- d %>%
  select(agency, year, party_name, SUBJECT) %>%
  filter(!is.na(SUBJECT)) %>%
  mutate(
    agency = as.character(agency),
    year = as.integer(year),
    party_name = as.character(party_name),

    # Remove common HTML artifacts before tokenizing
    SUBJECT = str_replace_all(SUBJECT, "<[^>]+>", " "),
    SUBJECT = str_replace_all(SUBJECT, "&nbsp;", " "),
    SUBJECT = str_replace_all(SUBJECT, "&amp;", " and "),
    SUBJECT = str_replace_all(SUBJECT, "&lt;", " "),
    SUBJECT = str_replace_all(SUBJECT, "&gt;", " "),
    SUBJECT = str_squish(SUBJECT)
  ) %>%
  tidytext::unnest_tokens(word, SUBJECT) %>%
  mutate(
    # Extra safety in case any angle brackets survive
    word = str_replace_all(word, "[<>]", ""),
        word = str_replace_all(word, "<|>", "")
  ) %>%
  filter(
    !is.na(word),
    word != "",
    str_detect(word, "[a-z]"),
    !str_detect(word, "^\\d+$"),
    nchar(word) > 3,
    !word %in% custom_stop
  ) %>%
  anti_join(tidytext::stop_words, by = "word") %>%
  count(agency, year, party_name, word, sort = TRUE)

# Optional but recommended so you do not need to retokenize each time
fs::dir_create(here("data", "derived"))
saveRDS(subject_words, here("data", "derived", "subject_word_counts.rds"))
```

Load data   
  ```{r}
subject_words <- readRDS(here("data", "derived", "subject_word_counts.rds"))
```

## 2. Helper functions for word-cloud panels

These functions prepare the top words per panel, scale word sizes within each panel, and save PNGs.

```{r}
safe_filename <- function(x) {
  x %>%
    str_replace_all("[^A-Za-z0-9]+", "_") %>%
    str_replace_all("^_+|_+$", "") %>%
    str_trunc(120, side = "right")
}

clean_wordcloud_label <- function(x) {
  x %>%
    as.character() %>%
    stringr::str_replace_all("<[^>]*>", " ") %>%       # remove HTML-ish tags
    stringr::str_replace_all("&[A-Za-z0-9#]+;", " ") %>% # remove HTML entities
    stringr::str_replace_all("[\\[\\]\\(\\)]", " ") %>%  # remove markdown link chars
    stringr::str_replace_all("[<>]", " ") %>%          # remove any remaining brackets
    stringr::str_replace_all("[\r\n\t]", " ") %>%
    stringr::str_squish()
}

# more agressive clearning 
clean_wordcloud_label <- function(x) {
  x %>%
    as.character() %>%
    stringr::str_replace_all("<[^>]*>", " ") %>%
    stringr::str_replace_all("&[A-Za-z0-9#]+;", " ") %>%
    stringr::str_replace_all("[^A-Za-z0-9'_-]", " ") %>%
    stringr::str_squish()
}

# Then modify prep_cloud_df() so it creates a safe plotting label:
prep_cloud_df <- function(counts, facet_cols = "year", max_words = 75,
                          min_size = 5, max_size = 18) {
  counts %>%
    mutate(
      word = as.character(word),
      word_label = clean_wordcloud_label(word)
    ) %>%
    filter(
      !is.na(word_label),
      word_label != "",
      !is.na(n),
      n > 0
    ) %>%
    group_by(across(all_of(facet_cols))) %>%
    slice_max(order_by = n, n = max_words, with_ties = FALSE) %>%
    mutate(
      .size = if (max(n) == min(n)) {
        mean(c(min_size, max_size))
      } else {
        scales::rescale(n, to = c(min_size, max_size))
      }
    ) %>%
    ungroup()
}

panel_dims <- function(plot_df, facet_cols = "year", ncol = NULL) {
  n_panels <- plot_df %>%
    distinct(across(all_of(facet_cols))) %>%
    nrow()

  if (n_panels == 0) {
    return(list(ncol = 1, width = 4, height = 3))
  }

  if (is.null(ncol)) {
    ncol <- min(n_panels, ceiling(sqrt(n_panels)))
  }

  nrow <- ceiling(n_panels / ncol)

  list(
    ncol = ncol,
    width = max(4, 2.2 * ncol),
    height = max(3, 1.9 * nrow)
  )
}

make_cloud_panel <- function(counts, title = NULL, facet_cols = "year",
                             max_words = 75, ncol = NULL) {
  plot_df <- prep_cloud_df(
    counts = counts,
    facet_cols = facet_cols,
    max_words = max_words
  )

  dims <- panel_dims(plot_df, facet_cols = facet_cols, ncol = ncol)


  ggplot(
    plot_df,
    aes(label = word_label, size = .size, color = log(n))
  ) +
    ggwordcloud::geom_text_wordcloud_area(
      rm_outside = TRUE,
      eccentricity = 1,
      grid_size = 1
    ) +
    facet_wrap(
  vars(!!!rlang::syms(facet_cols)),
  ncol = dims$ncol,
  scales = "free") +
    scale_size_identity() +
    scale_color_viridis_c(option = "B", guide = "none", begin = 0, end = .7) +
    scale_x_continuous(expand = expansion(mult = 0, add = 0)) +
scale_y_continuous(expand = expansion(mult = 0, add = 0)) +
    coord_cartesian(expand = FALSE, clip = "off") + 
    labs(title = title) +
    theme_void(base_size = 12) +
    theme(
      plot.margin = margin(0, 0, 0, 0, unit = "pt"),
      panel.spacing = unit(0, "pt"),
      panel.spacing.x = unit(0, "pt"),
      panel.spacing.y = unit(0, "pt"),

      strip.text = element_text(
        face = "bold",
        size = 10,
        margin = margin(0, 0, 0, 0, unit = "pt")
      ),
      strip.background = element_blank(),

      plot.title = element_text(
        face = "bold",
        hjust = 0.5,
        margin = margin(0, 0, 2, 0, unit = "pt")
      ),

      plot.background = element_rect(fill = "white", color = NA),
      panel.background = element_rect(fill = "white", color = NA)
    )
}

save_cloud_panel <- function(counts, path, title = NULL, facet_cols = "year",
                             max_words = 75, ncol = NULL, dpi = 300,
                             seed = 123) {
  plot_df <- prep_cloud_df(
    counts = counts,
    facet_cols = facet_cols,
    max_words = max_words
  )
  
  if (nrow(plot_df) == 0) {
    message("Skipping empty plot: ", path)
    return(invisible(NULL))
  }
  
  
  
  p <- make_cloud_panel(
    counts = counts,
    title = title,
    facet_cols = facet_cols,
    max_words = max_words,
    ncol = dims$ncol
  )
  
  fs::dir_create(dirname(path))
  
  set.seed(seed)
  
  ggsave(
    filename = path,
    plot = p,
    width = dims$width,
    height = dims$height,
    dpi = dpi,
    bg = "white",
    limitsize = FALSE
  )
  
  invisible(path)
}
```

## 3. Overall word clouds by year

This creates one PNG with one panel per year.

```{r}
overall_year_counts <- subject_words %>%
  group_by(year, word) %>%
  summarize(n = sum(n), .groups = "drop")

save_cloud_panel(
  counts = overall_year_counts,
  path = here("figs", "wordcloud", "overall_by_year.png"),
  #title = "SUBJECT word clouds by year",
  facet_cols = "year",
  max_words = 75
)
```

## 4. One PNG per agency, faceted by year

This saves files like:
  
  ```{r}
figs/wordcloud/by-agency/ABMC.png
```

```{r}
agency_year_counts <- subject_words %>%
  group_by(agency, year, word) %>%
  summarize(n = sum(n), .groups = "drop")

if(F){
agency_year_counts %>%
  filter(
    #agency == "DHHS_ACF",
    str_detect(word, "<|>")
  ) %>%
  arrange(desc(n))

d %>%
  filter(
    #agency == "DHHS_ACF",
    str_detect(SUBJECT, "<a|</a>|<|>")
  ) %>%
  select(agency, year, party_name, SUBJECT) %>%
  head(50)
}

agencies <- agency_year_counts %>%
  distinct(agency) %>%
  arrange(agency) %>%
  pull(agency)

#agencies[agencies != "DHHS_ACF"]
#agencies = "DHHS_ACF"

for (ag in agencies) {
  message("Saving agency plot: ", ag)
  
  dat_ag <- agency_year_counts %>%
    filter(agency == ag) %>%
    select(year, word, n)
  
  save_cloud_panel(
    counts = dat_ag,
    path = here(
      "figs", "wordcloud", "by-agency",
      paste0(safe_filename(ag), ".png")
    ),
    title = paste("SUBJECT word clouds by year:", ag),
    facet_cols = "year",
    max_words = 75
  )
}
```

## 5. One overall series per party

This saves one PNG per party, faceted by year.

```{r}
party_year_counts <- subject_words %>%
  group_by(party_name, year, word) %>%
  summarize(n = sum(n), .groups = "drop")

parties <- party_year_counts %>%
  distinct(party_name) %>%
  filter(!is.na(party_name)) %>%
  arrange(party_name) %>%
  pull(party_name)

for (pt in parties) {
  message("Saving party plot: ", pt)
  
  dat_pt <- party_year_counts %>%
    filter(party_name == pt) %>%
    select(year, word, n)
  
  save_cloud_panel(
    counts = dat_pt,
    path = here(
      "figs", "wordcloud", "by-party",
      paste0(safe_filename(pt), ".png")
    ),
    title = paste("SUBJECT word clouds by year:", pt),
    facet_cols = "year",
    max_words = 75
  )
}
```

## 6. One PNG per agency-party combination, faceted by year

This saves files like:
  
  ```{r}
figs/wordcloud/by-agency-party/ABMC__Republican_Party.png
figs/wordcloud/by-agency-party/ABMC__Democratic_Party.png
```

```{r}
agency_party_year_counts <- subject_words %>%
  group_by(agency, party_name, year, word) %>%
  summarize(n = sum(n), .groups = "drop")

agency_party_combos <- agency_party_year_counts %>%
  distinct(agency, party_name) %>%
  filter(!is.na(agency), !is.na(party_name)) %>%
  arrange(agency, party_name)

for (i in seq_len(nrow(agency_party_combos))) {
  ag <- agency_party_combos$agency[i]
  pt <- agency_party_combos$party_name[i]
  
  message("Saving agency-party plot: ", ag, " / ", pt)
  
  dat_ag_pt <- agency_party_year_counts %>%
    filter(agency == ag, party_name == pt) %>%
    select(year, word, n)
  
  save_cloud_panel(
    counts = dat_ag_pt,
    path = here(
      "figs", "wordcloud", "by-agency-party",
      paste0(safe_filename(ag), "__", safe_filename(pt), ".png")
    ),
    title = paste("SUBJECT word clouds by year:", ag, "-", pt),
    facet_cols = "year",
    max_words = 75
  )
}
```

## Optional: save agency-party plots in folders by agency

If you prefer this structure:
  
  ```{r}
figs/wordcloud/by-agency-party/ABMC/Republican_Party.png
figs/wordcloud/by-agency-party/ABMC/Democratic_Party.png
```

replace the `path = ...` line in the agency-party loop with:
  
  ```{r}
path = here(
  "figs", "wordcloud", "by-agency-party",
  safe_filename(ag),
  paste0(safe_filename(pt), ".png")
)
```

## Useful tuning knobs

The main one is:
  
  ```{r}
max_words = 75
```

Try values like `50`, `100`, or `150`.


Then rerun the tokenization/counting step.
